### 2019-03-18 paper/paper.tex
Repo init

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{subfig}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Replication of ‘A Look at the Dynamics of the JavaScript Package Ecosystem’\\}

\author{\IEEEauthorblockN{ Kevin de Haan, Gregory Neagu, Frederic Sauve-Hoover, Abram Hindle}
\IEEEauthorblockA{\textit{Department of Computing Science} \\
\textit{University of Alberta}\\
Edmonton, Canada\\
Email: \{kdehaan,neagu,rsauveho,abram.hindle\}@ualberta.ca}
}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}

\subsection{Research Questions}
\begin{itemize}
  \item

\end{itemize}

\section{Related Work}

\section{Methodology}

\subsection{Data Collection}

\section{Results and Discussion}

\subsection{Threats to Validity}

\section{Conclusion}

% \begin{thebibliography}{00}

% \end{thebibliography}
\vspace{12pt}

\end{document}

### 2019-04-07 paper/paper.tex
added abstract

@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+    \def\code#1{\texttt{#1}}
 \begin{document}
 
-\title{Replication of ‘A Look at the Dynamics of the JavaScript Package Ecosystem’\\}
+\title{A Second Look at the Dynamics of the JavaScript Package Ecosystem\\}
 
@@
 
+% Footnote should maybe be a full source, or just one link
 \begin{abstract}
-
+In recent years, the tools and packages most commonly involved with JavaScript development have evolved rapidly.
+Newer packages such as Angular and React have experienced a marked increase in popularity among developers, while libraries such as jQuery
+have begun to phase out.\footnote[1]{https://insights.stackoverflow.com/survey/2016\#technology-most-popular-technologies, 
+https://insights.stackoverflow.com/survey/2017\#technology-\_-frameworks-libraries-and-other-technologies, https://insights.stackoverflow.com/survey/2018\#technology-\_-frameworks-libraries-and-tools}
+For this reason, we take a second look at a paper by Wittern, Suter and Rajagopalan \cite{Wittern:2016} based on data up to September 2015 to see what has changed, and if previously observed trends have remained constant.
+In the original paper, the authors use the \emph{node package manager} (\code{npm}) to gain 
+insight into the JavaScript ecosystem as a whole. \code{npm}, a hosting service for JavaScript-based software, has only grown in popularity since
+the original paper, with more than three times as many hosted packages (now over 750,000) and over ten times as many weekly package downloads (now over ten billion per week).
+Additionally, data collected from projects publicly hosted on \code{GitHub} allow us to observe an alternative measure of popularity. 
+Ultimately, this second look aims to discover if recent years have had any significant effects on ecosystem-wide trends, and provide developers with further insight into how packages are used and evolve.
 \end{abstract}
@@
 
-% \begin{thebibliography}{00}
+\begin{thebibliography}{00}
+  \bibitem{Wittern:2016}
+  Erik Wittern, Philippe Suter, and Shriram Rajagopalan.
+  \newblock A look at the dynamics of the javascript package ecosystem.
+  \newblock In {\em Proceedings of the 13th International Conference on Mining
+    Software Repositories}, MSR '16, pages 351--361, New York, NY, USA, 2016.
+    ACM.
 
-% \end{thebibliography}
+\end{thebibliography}
 \vspace{12pt}

### 2019-04-07 paper/paper.tex
added contributions section

@@
 
-\author{\IEEEauthorblockN{ Kevin de Haan, Gregory Neagu, Frederic Sauve-Hoover, Abram Hindle}
+\author{\IEEEauthorblockN{Kevin de Haan, Gregory Neagu, Frederic Sauve-Hoover, Abram Hindle}
 \IEEEauthorblockA{\textit{Department of Computing Science} \\
@@
 In recent years, the tools and packages most commonly involved with JavaScript development have evolved rapidly.
-Newer packages such as Angular and React have experienced a marked increase in popularity among developers, while libraries such as jQuery
+Newer packages such as Angular and React have experienced a marked increase in popularity among developers, while frameworks such as jQuery
 have begun to phase out.\footnote[1]{https://insights.stackoverflow.com/survey/2016\#technology-most-popular-technologies, 
 https://insights.stackoverflow.com/survey/2017\#technology-\_-frameworks-libraries-and-other-technologies, https://insights.stackoverflow.com/survey/2018\#technology-\_-frameworks-libraries-and-tools}
-For this reason, we take a second look at a paper by Wittern, Suter and Rajagopalan \cite{Wittern:2016} based on data up to September 2015 to see what has changed, and if previously observed trends have remained constant.
+For this reason, we take a second look at a 2016 paper by Wittern, Suter and Rajagopalan \cite{Wittern:2016} to see what has changed, and if previously observed trends have remained constant.
 In the original paper, the authors use the \emph{node package manager} (\code{npm}) to gain 
@@
 
-\subsection{Research Questions}
+The core contributions we make are as follows:
 \begin{itemize}
-  \item
-
+  \item We replicate and verify the results found in the original paper for the window of October 1\textsuperscript{st} 2010 to September 1\textsuperscript{st} 2015.
+  \item We extend the analysis to the time period of September 2\textsuperscript{nd} 2015 to April 1\textsuperscript{st} 2019, and evaluate whether patterns and trends noted in the original paper are still observable.
+  \item We investigate whether the continued evolution of the JavaScript package ecosystem has affected the relationships between various measures of package popularity.
+  \item We determine if the ongoing maturation of the JavaScript ecosystem has resulted in tangible changes to version numbering or adoption practices.
 \end{itemize}

### 2019-04-07 paper/paper.tex
rewrote abstract and intro

@@
 Newer packages such as Angular and React have experienced a marked increase in popularity among developers, while frameworks such as jQuery
-have begun to phase out.\footnote[1]{https://insights.stackoverflow.com/survey/2016\#technology-most-popular-technologies, 
+have begun to phase out.\footnote[1]{\label{adoption}https://insights.stackoverflow.com/survey/2016\#technology-most-popular-technologies, 
 https://insights.stackoverflow.com/survey/2017\#technology-\_-frameworks-libraries-and-other-technologies, https://insights.stackoverflow.com/survey/2018\#technology-\_-frameworks-libraries-and-tools}
-For this reason, we take a second look at a 2016 paper by Wittern, Suter and Rajagopalan \cite{Wittern:2016} to see what has changed, and if previously observed trends have remained constant.
-In the original paper, the authors use the \emph{node package manager} (\code{npm}) to gain 
-insight into the JavaScript ecosystem as a whole. \code{npm}, a hosting service for JavaScript-based software, has only grown in popularity since
-the original paper, with more than three times as many hosted packages (now over 750,000) and over ten times as many weekly package downloads (now over ten billion per week).
-Additionally, data collected from projects publicly hosted on \code{GitHub} allow us to observe an alternative measure of popularity. 
+For this reason we take a second look at a 2016 paper by Wittern, Suter and Rajagopalan \cite{Wittern:2016} to see what aspects of the JavaScript package ecosystem have changed, 
+and if previously observed trends have remained constant.
+In the original paper the authors use the \emph{node package manager} (\code{npm}) to gain 
+insight into the JavaScript ecosystem as a whole, and data from projects publicly hosted on \code{GitHub} to observe an alternative measure of popularity.
+We adhere to the same methods of analysis, and extend the data to capture
+more recent information up to April 1\textsuperscript{st} 2019.
 Ultimately, this second look aims to discover if recent years have had any significant effects on ecosystem-wide trends, and provide developers with further insight into how packages are used and evolve.
@@
 \section{Introduction}
-
+This paper is a replication of \emph{A Look at the Dynamics of the JavaScript Package Ecosystem}\cite{Wittern:2016} that performs extensive analysis of 
+the \emph{node package manager} (\code{npm}), a popular distributor of JavaScript-based packages.
+Since the publishing of the original paper, the usage and scale of \code{npm} has only grown.
+With more than three times as many hosted packages (now over 750,000)
+and over ten times as many weekly package downloads (now over ten billion per week), the raw volume of data and the complexity of package dependency graphs has increased significantly. 
+Additionally, the major frameworks used in JavaScript development have undergone a rapid transformation as packages such as Angular and React are adopted\footnotemark[\ref{adoption}].
 The core contributions we make are as follows:
@@
 
-\section{Related Work}
+% \section{Related Work}
 

### 2019-04-08 paper/paper.tex
added subsections mirroring the original paper

@@
 Newer packages such as Angular and React have experienced a marked increase in popularity among developers, while frameworks such as jQuery
-have begun to phase out.\footnote[1]{\label{adoption}https://insights.stackoverflow.com/survey/2016\#technology-most-popular-technologies, 
+have begun to phase out.\footnote{\label{adoption}https://insights.stackoverflow.com/survey/2016\#technology-most-popular-technologies, 
 https://insights.stackoverflow.com/survey/2017\#technology-\_-frameworks-libraries-and-other-technologies, https://insights.stackoverflow.com/survey/2018\#technology-\_-frameworks-libraries-and-tools}
@@
 Since the publishing of the original paper, the usage and scale of \code{npm} has only grown.
-With more than three times as many hosted packages (now over 750,000)
+With more than three times as many hosted packages (over 750,000 as of April 1\textsuperscript{st} 2019)
 and over ten times as many weekly package downloads (now over ten billion per week), the raw volume of data and the complexity of package dependency graphs has increased significantly. 
@@
 
-% \section{Related Work}
+\section{Related Work}
 
 \section{Methodology}
+% CHECK IF THE NUMBERS ARE RIGHT
+The window of data observed within this paper is October 1\textsuperscript{st} 2010 (as in the original paper) to April 1\textsuperscript{st} 2019.
+We collected from three publicly available data sets. Two of these, the \code{npm} registry and the \code{GitHub} repository platform, are from the same source as in the original paper.
+To find repositories relying \code{npm}, we used the Google BigQuery \code{github\_repos} data set, updated weekly\footnote{https://github.com/fhoffa/analyzing\_github/}.
+By using this set we are able to analyze \code{GitHub} data without being constrained to the currently available window provided by the GHTorrent project\cite{ghtorrent}.
+The final data set encompasses 797,940 packages and TODO:FILL applications.
 
@@
 
-\section{Results and Discussion}
+\subsection{Package Metadata}
 
-\subsection{Threats to Validity}
+\subsection{Applications using \code{npm} Packages}
+
+\section{Ecosystem Evolution}
+
+\section{Package Popularity}
+
+\subsection{Relationships between Measures}
+
+\subsection{Distinct Package Types}
+
+\subsection{Popularity Over Time}
+
+\subsubsection{Identifying Top Packages}
+
+\subsubsection{Popular Package Dynamics}
+
+\subsubsection{Comparing Popularities}
+
+\section{Version Numbering and Package Adoption}
+
+\subsection{Attribution of Version Numbers}
+
+\subsection{Adoption by Version Number}
 
@@
 
+  \bibitem{ghtorrent}
+  Georgios Gousios.
+  \newblock The ghtorrent dataset and tool suite.
+  \newblock In {\em Proceedings of the 10th Working Conference on Mining Software
+    Repositories}, MSR '13, pages 233--236, Piscataway, NJ, USA, 2013. IEEE
+    Press.
+
+  \bibitem{Wittern:2016:LDJ:2901739.2901743}
+
 \end{thebibliography}

### 2019-04-08 paper/paper.tex
some updates

@@
 
-\section{Methodology}
+\section{Data Collection}
 % CHECK IF THE NUMBERS ARE RIGHT
-The window of data observed within this paper is October 1\textsuperscript{st} 2010 (as in the original paper) to April 1\textsuperscript{st} 2019.
+The window of data analyzed within this paper is October 1\textsuperscript{st} 2010 (as in the original paper) to April 1\textsuperscript{st} 2019.
 We collected from three publicly available data sets. Two of these, the \code{npm} registry and the \code{GitHub} repository platform, are from the same source as in the original paper.
@@
 By using this set we are able to analyze \code{GitHub} data without being constrained to the currently available window provided by the GHTorrent project\cite{ghtorrent}.
-The final data set encompasses 797,940 packages and TODO:FILL applications.
-
-\subsection{Data Collection}
+The final data set encompasses 797,940 packages and \textbf{\#VALUE} applications.
 
@@
 
+\textbf{this one is probably mostly for @Fred}
+
 \subsection{Applications using \code{npm} Packages}
+
+\textbf{@Greg I'm gonna need you to put something here}
 
@@
 
-  \bibitem{Wittern:2016:LDJ:2901739.2901743}
-
 \end{thebibliography}

### 2019-04-08 paper/paper.tex
added more context to the intro

@@
 \section{Introduction}
+Software ecosystems are environments that form as projects evolve in parallel,
+becoming interconnected as contexts and dependencies span companies and communities \cite{LUNGU2010264}. 
+Research on these systems has increased rapidly in the recent past \cite{Manikas:2017}, investigating
+their characteristics and behaviour as they develop \cite{Manikas:2013}. Understanding how software
+ecosystems form and change is valuable from both a software as well as a business standpoint\cite{Messerschmitt},
+and is important for informing developers how technologies are used over time \cite{Serebrenik:2015}. 
+An understanding of software ecosystems can inform decisions on when to adopt frameworks and how long
+to support them, as well as provide insight into how changes to software propagate throughout the community \cite{Wittern:2016}.
+
 This paper is a replication of \emph{A Look at the Dynamics of the JavaScript Package Ecosystem}\cite{Wittern:2016} that performs extensive analysis of 
@@
 We collected from three publicly available data sets. Two of these, the \code{npm} registry and the \code{GitHub} repository platform, are from the same source as in the original paper.
-To find repositories relying \code{npm}, we used the Google BigQuery \code{github\_repos} data set, updated weekly\footnote{https://github.com/fhoffa/analyzing\_github/}.
-By using this set we are able to analyze \code{GitHub} data without being constrained to the currently available window provided by the GHTorrent project\cite{ghtorrent}.
+To find repositories relying on \code{npm}, we used the Google BigQuery \code{github\_repos} data set, updated weekly\footnote{https://github.com/fhoffa/analyzing\_github/}.
+By using this set we are able to analyze \code{GitHub} data without being constrained to the currently available window provided by the GHTorrent project\cite{Gousi13}.
 The final data set encompasses 797,940 packages and \textbf{\#VALUE} applications.
@@
 \begin{thebibliography}{00}
+
+  \bibitem{Blincoe:2015}
+  Kelly Blincoe, Francis Harrison, and Daniela Damian.
+  \newblock Ecosystems in github and a method for ecosystem identification using
+    reference coupling.
+  \newblock In {\em Proceedings of the 12th Working Conference on Mining Software
+    Repositories}, MSR '15, pages 202--207, Piscataway, NJ, USA, 2015. IEEE
+    Press.
+
+  \bibitem{Gousi13}
+  Georgios Gousios.
+  \newblock The ghtorrent dataset and tool suite.
+  \newblock In {\em Proceedings of the 10th Working Conference on Mining Software
+    Repositories}, MSR '13, pages 233--236, Piscataway, NJ, USA, 2013. IEEE
+    Press.
+
+  \bibitem{LUNGU2010264}
+  Mircea Lungu, Michele Lanza, Tudor Gîrba, and Romain Robbes.
+  \newblock The small project observatory: Visualizing software ecosystems.
+  \newblock {\em Science of Computer Programming}, 75(4):264 -- 275, 2010.
+  \newblock Experimental Software and Toolkits (EST 3): A special issue of the
+    Workshop on Academic Software Development Tools and Techniques (WASDeTT
+    2008).
+
+  \bibitem{Manikas:2013}
+  Konstantinos Manikas and Klaus~Marius Hansen.
+  \newblock Software ecosystems - a systematic literature review.
+  \newblock {\em J. Syst. Softw.}, 86(5):1294--1306, May 2013.
+
+  \bibitem{Messerschmitt}
+  David Messerschmitt and Clemens Szyperski.
+  \newblock {\em Software Ecosystem: Understanding an Indispensable Technology
+    and Industry}.
+  \newblock 01 2003.
+
+  \bibitem{Manikas:2017}
+  M.~{Seppänen}, S.~{Hyrynsalmi}, K.~{Manikas}, and A.~{Suominen}.
+  \newblock Yet another ecosystem literature review: 10+1 research communities.
+  \newblock In {\em 2017 IEEE European Technology and Engineering Management
+    Summit (E-TEMS)}, pages 1--8, Oct 2017.
+
+  \bibitem{Serebrenik:2015}
+  Alexander Serebrenik and Tom Mens.
+  \newblock Challenges in software ecosystems research.
+  \newblock In {\em Proceedings of the 2015 European Conference on Software
+    Architecture Workshops}, ECSAW '15, pages 40:1--40:6, New York, NY, USA,
+    2015. ACM.
+
   \bibitem{Wittern:2016}
@@
 
-  \bibitem{ghtorrent}
-  Georgios Gousios.
-  \newblock The ghtorrent dataset and tool suite.
-  \newblock In {\em Proceedings of the 10th Working Conference on Mining Software
-    Repositories}, MSR '13, pages 233--236, Piscataway, NJ, USA, 2013. IEEE
-    Press.
+  \end{thebibliography}
 
-\end{thebibliography}
 \vspace{12pt}

### 2019-04-08 paper/paper.tex
small phrasing fix

@@
 their characteristics and behaviour as they develop \cite{Manikas:2013}. Understanding how software
-ecosystems form and change is valuable from both a software as well as a business standpoint\cite{Messerschmitt},
-and is important for informing developers how technologies are used over time \cite{Serebrenik:2015}. 
+ecosystems form and change is important from both a software as well as a business standpoint\cite{Messerschmitt},
+and is valuable for informing developers how technologies are used over time \cite{Serebrenik:2015}. 
 An understanding of software ecosystems can inform decisions on when to adopt frameworks and how long

### 2019-04-09 paper/paper.tex
updated bibliography and added sample image
more intro, added keywords

@@
 have begun to phase out.\footnote{\label{adoption}https://insights.stackoverflow.com/survey/2016\#technology-most-popular-technologies, 
-https://insights.stackoverflow.com/survey/2017\#technology-\_-frameworks-libraries-and-other-technologies, https://insights.stackoverflow.com/survey/2018\#technology-\_-frameworks-libraries-and-tools}
-For this reason we take a second look at a 2016 paper by Wittern, Suter and Rajagopalan \cite{Wittern:2016} to see what aspects of the JavaScript package ecosystem have changed, 
-and if previously observed trends have remained constant.
+https://insights.stackoverflow.com/survey/2017\#technology-\_-frameworks-libraries-and-other-technologies, 
+https://insights.stackoverflow.com/survey/2018\#technology-\_-frameworks-libraries-and-tools}
+For this reason we take a second look at a 2016 paper by Wittern, Suter and Rajagopalan \cite{Wittern:2016} 
+to see what aspects of the JavaScript package ecosystem have changed, and if previously observed trends have remained constant.
 In the original paper the authors use the \emph{node package manager} (\code{npm}) to gain 
-insight into the JavaScript ecosystem as a whole, and data from projects publicly hosted on \code{GitHub} to observe an alternative measure of popularity.
-We adhere to the same methods of analysis, and extend the data to capture
-more recent information up to April 1\textsuperscript{st} 2019.
-Ultimately, this second look aims to discover if recent years have had any significant effects on ecosystem-wide trends, and provide developers with further insight into how packages are used and evolve.
+insight into the JavaScript ecosystem as a whole, and data from projects publicly hosted on 
+\code{GitHub} to observe an alternative measure of popularity. We adhere to the same methods of analysis, 
+and extend the data to capture more recent information up to April 1\textsuperscript{st} 2019.
+Ultimately, this second look aims to discover if recent years have had any significant effects on 
+ecosystem-wide trends, and provide developers with further insight into how packages are used and evolve.
 \end{abstract}
+
+\begin{IEEEkeywords}
+JavaScript; software ecosystem analysis; Node.js; replication
+\end{IEEEkeywords}
 
@@
 to support them, as well as provide insight into how changes to software propagate throughout the community \cite{Wittern:2016}.
+Additionally, determining the characteristics of software ecosystems 
+can help clarify why some frameworks flourish while others fail, and guide 
+developers in the creation of new tools\cite{Serebrenik:2015}. Furthermore, 
+because software projects are overwhelmingly a collaborative effort, a complete
+understanding of a single project often requires knowledge of the ecosystem supporting it\cite{Blincoe:2015}.
 
-This paper is a replication of \emph{A Look at the Dynamics of the JavaScript Package Ecosystem}\cite{Wittern:2016} that performs extensive analysis of 
-the \emph{node package manager} (\code{npm}), a popular distributor of JavaScript-based packages.
-Since the publishing of the original paper, the usage and scale of \code{npm} has only grown.
-With more than three times as many hosted packages (over 750,000 as of April 1\textsuperscript{st} 2019)
-and over ten times as many weekly package downloads (now over ten billion per week), the raw volume of data and the complexity of package dependency graphs has increased significantly. 
-Additionally, the major frameworks used in JavaScript development have undergone a rapid transformation as packages such as Angular and React are adopted\footnotemark[\ref{adoption}].
+This paper is a replication of \emph{A Look at the Dynamics of the JavaScript Package Ecosystem}\cite{Wittern:2016} 
+that performs extensive analysis of the \emph{node package manager} (\code{npm}) ecosystem. 
+\code{npm} provides a set of open source tools that allow developers to 
+describe packages for \code{Node.js}, an asynchronous JavaScript runtime environment 
+designed for network applications\footnote{https://nodejs.org/en/about/}.
+The services provided by \code{npm} include a command line interface for maintaining 
+\code{package.json} files, the primary method to describe package metadata such as the name,
+description, version, and dependencies of a given package. \code{npm} also allows 
+developers to publish their packages to a public registry, permitting anyone 
+to download and use their software. Packages hosted on \code{npm} will often depend on other \code{npm}
+packages, forming an elaborate JavaScript package ecosystem.
+Since the publishing of the original paper, the usage and scale of \code{npm} has only grown,
+ and now hosts more than three times as many packages (over 750,000 as of April 1\textsuperscript{st} 2019) 
+and handles over ten times as many weekly package downloads (now over ten billion per week).
+Additionally, the major frameworks used in JavaScript development have undergone a 
+rapid transformation as packages such as Angular and React are adopted\footnotemark[\ref{adoption}].
 The core contributions we make are as follows:
 \begin{itemize}
-  \item We replicate and verify the results found in the original paper for the window of October 1\textsuperscript{st} 2010 to September 1\textsuperscript{st} 2015.
-  \item We extend the analysis to the time period of September 2\textsuperscript{nd} 2015 to April 1\textsuperscript{st} 2019, and evaluate whether patterns and trends noted in the original paper are still observable.
-  \item We investigate whether the continued evolution of the JavaScript package ecosystem has affected the relationships between various measures of package popularity.
-  \item We determine if the ongoing maturation of the JavaScript ecosystem has resulted in tangible changes to version numbering or adoption practices.
+  \item We replicate and verify the results found in the original paper for the 
+  window of October 1\textsuperscript{st} 2010 to September 1\textsuperscript{st} 2015.
+  \item We extend the analysis to the time period of September 2\textsuperscript{nd} 
+  2015 to April 1\textsuperscript{st} 2019, and evaluate whether patterns and trends 
+  noted in the original paper are still observable.
+  \item We investigate whether the continued evolution of the JavaScript package 
+  ecosystem has affected the relationships between various measures of package popularity.
+  \item We determine if the ongoing maturation of the \code{npm} ecosystem has 
+  resulted in tangible changes to version numbering or adoption practices.
 \end{itemize}
-
-\section{Related Work}
 
@@
 \section{Ecosystem Evolution}
+
+\begin{figure*}
+  % \includegraphics[width=.5\textwidth]{figures/highest_ranked_monthly_100.pdf}
+
+  \includegraphics[width=1\textwidth]{figures/highest_ranked_monthly_100.pdf}
+  \caption{Neat you can include PDFs}
+  \label{ranksByYear}
+\end{figure*}
 
@@
 
+\section{Related Work}
+
 \section{Conclusion}
@@
 
+  \bibitem{DBLP:Decan:2018}
+  Alexandre Decan, Tom Mens, and Philippe Grosjean.
+  \newblock An empirical comparison of dependency network evolution in seven
+    software packaging ecosystems.
+  \newblock {\em CoRR}, abs/1710.04936, 2017.
+
   \bibitem{Gousi13}
@@
     Press.
+
+  \bibitem{Kikas:2017}
+  Riivo Kikas, Georgios Gousios, Marlon Dumas, and Dietmar Pfahl.
+  \newblock Structure and evolution of package dependency networks.
+  \newblock In {\em Proceedings of the 14th International Conference on Mining
+    Software Repositories}, MSR '17, pages 102--112, Piscataway, NJ, USA, 2017.
+    IEEE Press.
 
@@
   \newblock 01 2003.
+
+  \bibitem{DBLP:PanoGA16}
+  Amantia Pano, Daniel Graziotin, and Pekka Abrahamsson.
+  \newblock What leads developers towards the choice of a javascript framework?
+  \newblock {\em CoRR}, abs/1605.04303, 2016.
 

### 2019-04-09 paper/paper.tex
some formatting

@@
 \begin{IEEEkeywords}
-JavaScript; software ecosystem analysis; Node.js; replication
+JavaScript; Node.js; node package manager; software ecosystem analysis
 \end{IEEEkeywords}
@@
 \section{Introduction}
-Software ecosystems are environments that form as projects evolve in parallel,
+Software ecosystems are environments that form as projects develop in parallel,
 becoming interconnected as contexts and dependencies span companies and communities \cite{LUNGU2010264}. 
@@
 their characteristics and behaviour as they develop \cite{Manikas:2013}. Understanding how software
-ecosystems form and change is important from both a software as well as a business standpoint\cite{Messerschmitt},
+ecosystems evolve is important from both a software as well as a business standpoint\cite{Messerschmitt},
 and is valuable for informing developers how technologies are used over time \cite{Serebrenik:2015}. 

### 2019-04-09 paper/paper.tex
added info on ecosystem changes

@@
 \section{Ecosystem Evolution}
+
+Created in 2009, \code{npm} has grown
+rapidly in popularity and scope over the last ten years, and 
+as of the original paper showed no signs of slowing down \cite{Wittern:2016}.
+We investigate the state of the \code{npm} ecosystem
+since September 1\textsuperscript{st} 2015, and look for any signs of deterioration in 
+the health of the ecosystem. Periods of stagnating growth would suggest
+that developer interest is waning, while steady activity would 
+indicate that the ecosystem as a whole is healthy and will continue to
+evolve. To search for these potential indicators in the \code{npm} package environment,
+we investigate the number of packages created and updated over time, as well
+as system-wide trends of dependencies within packages. In figure 1 
+[INSERT DATA COMMENTARY HERE]. Figure 2 [MORE DATA COMMENTARY].
+
+To better visualize the status of inter-package dependencies, we constructed
+a directed dependency graph using dependants as out-degrees and
+dependencies as in-degrees. Based on this dependency graph, Figure 3
+displays the percentage of packages with various amounts of dependencies. 
+[MIGHT NEED TO CHANGE BASED ON DATA: While the average number of dependencies 
+of packages continues to increase, the percentage of packages with zero 
+to three dependencies has actually increased since the end of the original paper's
+reporting period \cite{Wittern:2016}. This suggests some changes to developer 
+behaviour, likely either as a deliberate effort by programmers seeking to avoid the perils of 
+complicated dependency trees \cite{Kikas:2017}, or as a natural result of the ever-changing
+ways in which JavaScript is used for project development.
 

### 2019-04-10 paper/paper.tex
added listing for sample package.json

@@
 \usepackage{subfig}
+\usepackage{listings}
+\lstset{numbers=left,stepnumber=1,}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \subsection{Package Metadata}
+
+\begin{lstlisting}[caption={A mock \code{npm} package.json. Some fields omitted for brevity.},captionpos=b,
+  label=samplePkg, frame=single, firstline=1]
+{
+  "name": "Lorem Ipsum",
+  "version": "0.9.3",
+  "maintainers": [
+      {"name": "Dolor Sit",
+      "email": "dolorsit@amet.org"}
+  ],
+  "repository": {
+      "type": "git",
+      "url": "https://github.com/lor/em"
+  },
+  "main" : "loremipsum.js",
+  "keywords": ["Web", "REST"],
+  "dependencies": {
+      "Adipiscing": "~1.7.0",
+      "Elit": "5.1.x"
+  },
+  "devDependencies": {
+      "Sed": "0.9.0",
+      "Do": ">=1.3.5 <4.0.0" 
+  }
+}
+\end{lstlisting}
 

### 2019-04-10 paper/paper.tex

@@
 \usepackage{listings}
-\lstset{numbers=left,stepnumber=1,}
+\lstset{numbers=left,stepnumber=1,basicstyle=\footnotesize\ttfamily}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 a directed dependency graph using dependants as out-degrees and
-dependencies as in-degrees. Based on this dependency graph, Figure 3
+dependencies as in-degrees. Based on this dependency graph, Figure \ref{outDegree}
 displays the percentage of packages with various amounts of dependencies. 
@@
 ways in which JavaScript is used for project development.
+
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{figures/npm_deps_monthly_out_degree.pdf}
+  \caption{\code{npm} packages by their number of dependencies on other packages}
+  \label{outDegree}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{figures/npm_deps_monthly_in_degree.pdf}
+  \caption{\code{npm} packages by the number of other packages depending on them}
+  \label{inDegree}
+\end{figure}
 

### 2019-04-10 paper/paper.tex
updated bib

@@
 complicated dependency trees \cite{Kikas:2017}, or as a natural result of the ever-changing
-ways in which JavaScript is used for project development.
+ways in which JavaScript is used for project development. [ADD EXACT VALUES]
+
+In addition to the number of external dependencies per package, 
+we investigate how packages support dependants. The original paper 
+discovered that the majority of in degrees are concentrated among a core 
+minority of packages, with the majority of packages having no dependants,
+a discovery that has also been observed in other software ecosystems such
+as Linux and MySQL \cite{Myers:2003}. In our updated data, we discover 
+that not only have these aspects held true, but the concentration of 
+dependencies has actually increased. As of April 1\textsuperscript{st} 2019, [NUMBER]\% of packages
+had zero dependants, up from [NUMBER]\% in 2015. Meanwhile, only \%[NUMBER] of packages
+had 6 or more dependants, down from \%[NUMBER] in September 2015. It is again interesting to note
+that the current trend of increasing concentration appears to have begun shortly after the end of window in the original
+paper \cite{Wittern:2016}.
 
@@
 
-\begin{figure*}
-  % \includegraphics[width=.5\textwidth]{figures/highest_ranked_monthly_100.pdf}
-
-  \includegraphics[width=1\textwidth]{figures/highest_ranked_monthly_100.pdf}
-  \caption{Neat you can include PDFs}
-  \label{ranksByYear}
-\end{figure*}
-
 \section{Package Popularity}
@@
 
+\begin{figure*}
+  \includegraphics[width=1\textwidth]{figures/highest_ranked.pdf}
+  \caption{\code{npm} rank (based on PageRank) of five packages with the lowest geometric mean per year}
+  \label{ranksByYear}
+\end{figure*}
+
 \subsubsection{Comparing Popularities}
+
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{figures/select_packages.png}
+  \caption{\code{npm} rank (PageRank) over time of selected utility packages}
+  \label{selectPackages}
+\end{figure}
 
@@
 
+  \bibitem{Myers:2003}
+  Christopher~R. Myers.
+  \newblock Software systems as complex networks: Structure, function, and
+    evolvability of software collaboration graphs.
+  \newblock {\em Phys. Rev. E}, 68:046116, Oct 2003.
+
   \bibitem{DBLP:PanoGA16}
@@
     ACM.
-
   \end{thebibliography}

### 2019-04-10 paper/paper.tex
figure formatting

@@
 a directed dependency graph using dependants as out-degrees and
-dependencies as in-degrees. Based on this dependency graph, Figure \ref{outDegree}
+dependencies as in-degrees. Based on this graph, Figure \ref{outDegree}
 displays the percentage of packages with various amounts of dependencies. 
@@
 
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{figures/geo_mean_highest_pagerank.pdf}
+  \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean}
+  \label{outDegree}
+\end{figure}
+
 \subsubsection{Popular Package Dynamics}
@@
   \includegraphics[width=1\textwidth]{figures/highest_ranked.pdf}
-  \caption{\code{npm} rank (based on PageRank) of five packages with the lowest geometric mean per year}
+  \caption{\code{npm} rank (PageRank) of the five packages each year with the lowest geometric}
   \label{ranksByYear}

### 2019-04-11 paper/paper.tex
added content to ecosystem evolution and added some draft templating

@@
 
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{figures/new_vs_updates_by_month.pdf}
+  \caption{Packages updated and packages created per month. Multiple updates per month are
+  only counted once.}
+  \label{npmGrowth}
+\end{figure}
+
 Created in 2009, \code{npm} has grown
@@
 we investigate the number of packages created and updated over time, as well
-as system-wide trends of dependencies within packages. In figure 1 
-[INSERT DATA COMMENTARY HERE]. Figure 2 [MORE DATA COMMENTARY].
+as system-wide trends of dependencies within packages. In Figure \ref{npmGrowth},
+we can observe that while \code{npm} is still growing, the speed at which new packages
+are created has slowed from an exponential to a linear rate. Some other things of note 
+include an observable spike in package creation and updates around March 2016, the month 
+when developer Azer Koçulu removed his 273 packages (including the popular package 
+\code{left-pad}) from \code{npm} and in doing so affected some packages such as 
+\code{babel} and \code{atom}, and therefore a significant fraction of \emph{all} 
+\code{Node.js} projects\footnote{https://blog.npmjs.org/post/141577284765/kik-left-pad-and-npm}
+There is also a significant spike in package updates observed in the month of January 2019, caused 
+by some source currently unknown to the authors [TRY TO FIGURE THIS ONE OUT].
+[ADD CONCAVITY DATA]. Figure 2 [CURRENTLY MISSING][MORE DATA COMMENTARY].
 
@@
 \subsection{Relationships between Measures}
+[NEEDS MORE DATA]
 
 \subsection{Distinct Package Types}
+[NEEDS MORE DATA]
 
 \subsection{Popularity Over Time}
+[NEEDS MORE DATA]
 
 \subsubsection{Identifying Top Packages}
+[NEEDS MORE DATA]
 
@@
   \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean}
-  \label{outDegree}
+  \label{topFive}
 \end{figure}
@@
 \subsubsection{Popular Package Dynamics}
+[NEEDS MORE DATA]
 
@@
 \subsubsection{Comparing Popularities}
+[NEEDS MORE DATA]
 
@@
 \section{Version Numbering and Package Adoption}
+[NEEDS MORE DATA]
 
 \subsection{Attribution of Version Numbers}
+[NEEDS MORE DATA]
 
 \subsection{Adoption by Version Number}
+[NEEDS MORE DATA]
 
@@
 \section{Conclusion}
+[NEEDS MORE DATA]
 

### 2019-04-11 paper/paper.tex
Wrote First Draft for npm Packages

@@
 
-\textbf{@Greg I'm gonna need you to put something here}
+\textbf{
+To collect our data for this project, we turned to multiple important data repositories.
+We used the GHTorrent public set [ref number], as well as the actual GitHub platform, and the npm repository.
+Using this data, we will further determine the popularity of packages by popularity metrics such as pagerank and download rank.
+
+Firstly, using the public online data set GHTorrent [ref num], we skimmed all projects and pulled those written in JavaScript.
+This resulted in a total of 9,017,221 repositories which were written in Javascript.
+It is important to note though that simply being written in JavaScript is not adequate.
+To find the correct repositories that implemented npm Packages, we looked for repositories that contained a package.json file, as elaborated earlier.
+This criteria is important, as it only holds true for projects utilizing npm packages.
+With this criteria, we then compiled a list of [100,000 for now] project repositories from GitHub, as we felt that this was an appropriate amount of repositories to be representative of the rest of the projects.
+
+    Using the GitHub platform api and the list of valid repository names from before, we cloned the GitHub repository for each project.
+With this, we were then able to determine the date and time of every commit of the project, as well as the list of included npm packages at the time of commit, as listed in every commit version of package.json.
+The results showed that on average a repository had 37.9 commits as well as [STATS HERE]
+
+    While there are a total of 9,017,221 repositories written in JavaScript, it is important to note that not all utilized npm packages, as evident by the lack of a package.json file in some repositories.
+As such, we screened for such repositories that did utilize npm packages.
+FInally, we pulled 100,000 repositories from those repositories as well felt this was representative sample size for the analysis.
+}
 

### 2019-04-11 paper/paper.tex
formatted and edited Greg's github data paragraph

--- 2019-04-11 paper/paper.tex
@@
 
-\textbf{@Greg I'm gonna need you to put something here}
+To collect our data for package usage in public projects, 
+we turned to the Google BigQuery \code{github\_repos} data 
+set\footnote{https://bigquery.cloud.google.com/dataset/bigquery-public-dat:github\_repos}.
+From this data, we skimmed all projects and pulled those 
+written in JavaScript, resulting in an initial total of 9,017,221 
+repositories. Simply being written in JavaScript is not enough to detect
+\code{npm} usage, so to find repositories using \code{npm} packages
+we looked for projects that contained a \code{package.json} 
+file. After confirming that the formatting of the file matched the \code{npm}
+standard, we are able to confidently say that any remaining packages are 
+using \code{npm} packages. With this criteria, we then compiled a list 
+of [100,000 for now] project 
+repositories from GitHub, a volume that we felt is likely to be an 
+appropriate representation of all such public projects.
+Using the \code{GitHub} platform API and the list of valid repository names 
+from before, we cloned the GitHub repository for each project. With
+this, we were then able to determine the date and time of every 
+commit of the project, as well as the list of included \code{npm} packages
+at the time of commit, as listed in every commit version of 
+\code{package.json}. The results showed that on average a repository 
+had 37.9 commits as well as [STATS HERE]. Ultimately, of the 9,017,221 
+public \code{GitHub} projects written in JavaScript and the [NUMBER] of repositories
+using \code{npm} packages, we randomly selected [NUMBER] repositories as
+a representative data set for the analysis.
 

### 2019-04-11 paper/paper.tex
another small edit

@@
 commit of the project, as well as the list of included \code{npm} packages
-at the time of commit, as listed in every commit version of 
-\code{package.json}. The results showed that on average a repository 
+at the time of commit, as listed in every historic version of 
+\code{package.json}, providing us with the \code{npm} packages used by that repository
+at any given time in the project's history. The results showed that on average a repository 
 had 37.9 commits as well as [STATS HERE]. Ultimately, of the 9,017,221 

### 2019-04-11 paper/paper.tex
added table with things

--- 2019-04-11 paper/paper.tex
@@
 
-To collect our data for package usage in public projects, 
-we turned to the Google BigQuery \code{github\_repos} data 
-set\footnote{https://bigquery.cloud.google.com/dataset/bigquery-public-dat:github\_repos}.
-From this data, we skimmed all projects and pulled those 
-written in JavaScript, resulting in an initial total of 9,017,221 
-repositories. Simply being written in JavaScript is not enough to detect
-\code{npm} usage, so to find repositories using \code{npm} packages
-we looked for projects that contained a \code{package.json} 
-file. After confirming that the formatting of the file matched the \code{npm}
-standard, we are able to confidently say that any remaining packages are 
-using \code{npm} packages. With this criteria, we then compiled a list 
-of [100,000 for now] project 
-repositories from GitHub, a volume that we felt is likely to be an 
-appropriate representation of all such public projects.
-Using the \code{GitHub} platform API and the list of valid repository names 
-from before, we cloned the GitHub repository for each project. With
-this, we were then able to determine the date and time of every 
-commit of the project, as well as the list of included \code{npm} packages
-at the time of commit, as listed in every commit version of 
-\code{package.json}. The results showed that on average a repository 
-had 37.9 commits as well as [STATS HERE]. Ultimately, of the 9,017,221 
-public \code{GitHub} projects written in JavaScript and the [NUMBER] of repositories
-using \code{npm} packages, we randomly selected [NUMBER] repositories as
-a representative data set for the analysis.
+\textbf{@Greg I'm gonna need you to put something here}
 
 \section{Ecosystem Evolution}
-
-\begin{figure}
-  \includegraphics[width=0.5\textwidth]{figures/new_vs_updates_by_month.pdf}
-  \caption{Packages updated and packages created per month. Multiple updates per month are
-  only counted once.}
-  \label{npmGrowth}
-\end{figure}
 
@@
 we investigate the number of packages created and updated over time, as well
-as system-wide trends of dependencies within packages. In Figure \ref{npmGrowth},
-we can observe that while \code{npm} is still growing, the speed at which new packages
-are created has slowed from an exponential to a linear rate. Some other things of note 
-include an observable spike in package creation and updates around March 2016, the month 
-when developer Azer Koçulu removed his 273 packages (including the popular package 
-\code{left-pad}) from \code{npm} and in doing so affected some packages such as 
-\code{babel} and \code{atom}, and therefore a significant fraction of \emph{all} 
-\code{Node.js} projects\footnote{https://blog.npmjs.org/post/141577284765/kik-left-pad-and-npm}
-There is also a significant spike in package updates observed in the month of January 2019, caused 
-by some source currently unknown to the authors [TRY TO FIGURE THIS ONE OUT].
-[ADD CONCAVITY DATA]. Figure 2 [CURRENTLY MISSING][MORE DATA COMMENTARY].
+as system-wide trends of dependencies within packages. In figure 1 
+[INSERT DATA COMMENTARY HERE]. Figure 2 [MORE DATA COMMENTARY].
 
@@
 
+% TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
+\begin{tabular}{c|c|c|c}
+  Year & Top 10 & Top 100 & Top 250 \\
+  \hline
+  2010 & 13 & 103 & 253\\
+  2011 & 25 & 297 & 701\\
+  2012 & 6 & 46 & 136\\
+  2013 & 3 & 38 & 114\\
+  2014 & 1 & 40 & 96\\
+  2015 & 4 & 38 & 86\\
+  2016 & 4 & 29 & 62\\
+  2017 & 0 & 12 & 48\\
+  2018 & 0 & 15 & 31\\
+  2019 & 0 & 4 & 12\\
+\end{tabular}
+
 \section{Package Popularity}
@@
 \subsection{Relationships between Measures}
-[NEEDS MORE DATA]
 
 \subsection{Distinct Package Types}
-[NEEDS MORE DATA]
 
 \subsection{Popularity Over Time}
-[NEEDS MORE DATA]
 
 \subsubsection{Identifying Top Packages}
-[NEEDS MORE DATA]
 
@@
   \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean}
-  \label{topFive}
+  \label{geoMean}
 \end{figure}
@@
 \subsubsection{Popular Package Dynamics}
-[NEEDS MORE DATA]
 
@@
 \subsubsection{Comparing Popularities}
-[NEEDS MORE DATA]
 
@@
 \section{Version Numbering and Package Adoption}
-[NEEDS MORE DATA]
 
 \subsection{Attribution of Version Numbers}
-[NEEDS MORE DATA]
 
 \subsection{Adoption by Version Number}
-[NEEDS MORE DATA]
 
@@
 \section{Conclusion}
-[NEEDS MORE DATA]
 

### 2019-04-11 paper/paper.tex
added related works to todo list

--- 2019-04-11 paper/paper.tex
@@
 include an observable spike in package creation and updates around March 2016, the month 
-when developer Azer Koçulu removed his 273 packages (including the popular package 
+when developer Azer Ko\c{c}ulu removed his 273 packages (including the popular package 
 \code{left-pad}) from \code{npm} and in doing so affected some packages such as 
 \code{babel} and \code{atom}, and therefore a significant fraction of \emph{all} 
-\code{Node.js} projects\footnote{https://blog.npmjs.org/post/141577284765/kik-left-pad-and-npm}
+\code{Node.js} projects\footnote{https://blog.npmjs.org/post/141577284765/kik-left-pad-and-npm}.
 There is also a significant spike in package updates observed in the month of January 2019, caused 
@@
 \section{Related Work}
+[IN PROGRESS]
 

### 2019-04-11 paper/paper.tex

--- 2019-04-11 paper/paper.tex
@@
 \usepackage{listings}
+\usepackage{url}
 \lstset{numbers=left,stepnumber=1,basicstyle=\footnotesize\ttfamily}
@@
 
-\author{\IEEEauthorblockN{Kevin de Haan, Gregory Neagu, Frederic Sauve-Hoover, Abram Hindle}
+\author{\IEEEauthorblockN{Kevin de Haan, Frederic Sauve-Hoover, Gregory Neagu, Abram Hindle}
   \IEEEauthorblockA{\textit{Department of Computing Science} \\
@@
 
-\subsection{Package Metadata}
+\subsection{Package Metadata} \label{Package Metadata}
 
@@
   "maintainers": [
-      {"name": "Dolor Sit",
-      "email": "dolorsit@amet.org"}
+      {
+        "name": "Dolor Sit",
+        "email": "dolorsit@amet.org"
+      }
   ],
@@
 
-\textbf{this one is probably mostly for @Fred}
+\begin{lstlisting}[caption={A mock simplified \code{npm} metadata file.},captionpos=b,
+  label=sampleSimpleMetadata, frame=single, firstline=1][t]
+{
+  "name": "Lorem Ipsum",
+  "versions": {
+    "1.0.4": {
+      "dependencies": {
+        "Adipiscing": "~1.7.0",
+        "Elit": "5.1.x"
+      },
+      "devDependencies": {
+        "Sed": "0.9.0",
+        "Do": ">=1.3.5 <4.0.0"
+      }
+    },
+    "1.0.5": {
+      "dependencies": {
+        "Adipiscing": "~1.7.0",
+      },
+      "devDependencies": {
+        "Do": ">=1.3.5 <4.0.0"
+      }
+    },
+    "time": {
+      "1.0.4": "2017-09-25T06:39:20.596Z",
+      "1.0.5": "2018-05-22T08:35:40.227Z",
+      "created": "2015-05-18T03:52:55.192Z"
+    }
+  }
+}
+\end{lstlisting}
+
+  Metadata for every package is available on the \code{npm} registry\footnote{https://registry.npmjs.org/packageName}. 
+  This metadata is a JSON file containing some info on licensing, documentation links, maintainers, and crucially for 
+  our purposes a log of each version of the package since it's creation, labelled using semantic versioning \cite{preston-werner},
+  and a time field containing the timestamp for each version. Each version in the version field contains various bits of 
+  version specific information such as authors, maintainers, license used, bugs, and a list of dependencies for that specific
+  version.\\
+
+  We obtained the list of all \code{npm} package names from the \code{npm} registry skimdb\footnote{\url{https://skimdb.npmjs.com/registry/_all_docs}}, and then %TODO fix this footnote, underscores are cursed
+  downloaded this metadata for all 797,940 packages on the \code{npm} registry, having found the names of all packages using the npm registry skimdb
+  , which we then converted to a somewhat simplified form as in Listing \ref{sampleSimpleMetadata} with just version and dependency information as this is all
+  we care about for this study. There are two kinds of dependencies in the metadata files, a list of runtime dependencies and $devDependencies$ used in testing and development.\\
+
+  We gathered some information on download counts for \code{npm} packages from the npmjs API\footnote{https://api.npmjs.org/downloads/range/2010-01-01:2019-04-01/packageName} 
+  however we found that the npmjs API seems to no longer have any data on download counts before October 1 2017, and so were unable to collect
+  historic download counts for \code{npm} as a whole or any specific packages.\\
 
@@
 
+  \begin{figure}
+    % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
+    \begin{tabular}{c|c|c|c}
+      Year & Top 10 & Top 100 & Top 250 \\
+      \hline
+      2010 & 13 & 103 & 253\\
+      2011 & 25 & 297 & 701\\
+      2012 & 6 & 46 & 136\\
+      2013 & 3 & 38 & 114\\
+      2014 & 1 & 40 & 96\\
+      2015 & 4 & 38 & 86\\
+      2016 & 4 & 29 & 62\\
+      2017 & 0 & 12 & 48\\
+      2018 & 0 & 15 & 31\\
+      2019 & 0 & 4 & 12\\
+    \end{tabular}
+    \caption{Number of packages entering top \code{npm} ranks for the first time}
+    \label{numEnteringTop}
+  \end{figure}
+
   \section{Package Popularity}
+
+  As in the original paper we analyzed popularity of \code{npm} packages using three major measures
+  \begin{enumerate}
+    \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within a dependency graph that we built using the
+      package metadata as described in Section \ref{Package Metadata}. PageRank is calculated for every package using a damping factor of 0.85 
+      and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
+      \code{npm} rank, an relative ranking of packge popularity with 1 being the most popular.
+    \item \textbf{download rank}
+  \end{enumerate}
 
@@
     ACM.
+
+    \bibitem{brin1998anatomy}
+    Sergey Brin and Lawrence Page.
+    \newblock The anatomy of a large-scale hypertextual web search engine.
+    \newblock {\em Computer networks and ISDN systems}, 30(1-7):107--117, 1998.
+
+    \bibitem{preston-werner}
+    Tom Preston-Werner.
+    \newblock Semantic versioning 2.0.0.
+
 \end{thebibliography}

### 2019-04-11 paper/paper.tex

@@
 \usepackage{listings}
-\usepackage{url}
 \lstset{numbers=left,stepnumber=1,basicstyle=\footnotesize\ttfamily}
@@
 
-\author{\IEEEauthorblockN{Kevin de Haan, Frederic Sauve-Hoover, Gregory Neagu, Abram Hindle}
+\author{\IEEEauthorblockN{Kevin de Haan, Gregory Neagu, Frederic Sauve-Hoover, Abram Hindle}
   \IEEEauthorblockA{\textit{Department of Computing Science} \\
@@
 
-\subsection{Package Metadata} \label{Package Metadata}
+\subsection{Package Metadata}
 
@@
   "maintainers": [
-      {
-        "name": "Dolor Sit",
-        "email": "dolorsit@amet.org"
-      }
+      {"name": "Dolor Sit",
+      "email": "dolorsit@amet.org"}
   ],
@@
 
-  We obtained the list of all \code{npm} package names from the \code{npm} registry skimdb\footnote{\url{https://skimdb.npmjs.com/registry/_all_docs}}, and then %TODO fix this footnote, underscores are cursed
+We obtained the list of all \code{npm} package names from the \code{npm} registry skimdb\footnote{https://skimdb.npmjs.com/registry/\_all\_docs}, and then %TODO fix this footnote, underscores are cursed
 downloaded this metadata for all 797,940 packages on the \code{npm} registry, having found the names of all packages using the npm registry skimdb
@@
 include an observable spike in package creation and updates around March 2016, the month 
-  when developer Azer Koçulu removed his 273 packages (including the popular package 
+when developer Azer Ko\c{c}ulu removed his 273 packages (including the popular package 
 \code{left-pad}) from \code{npm} and in doing so affected some packages such as 
 \code{babel} and \code{atom}, and therefore a significant fraction of \emph{all} 
-  \code{Node.js} projects\footnote{https://blog.npmjs.org/post/141577284765/kik-left-pad-and-npm}
+\code{Node.js} projects\footnote{https://blog.npmjs.org/post/141577284765/kik-left-pad-and-npm}.
 There is also a significant spike in package updates observed in the month of January 2019, caused 
@@
 
-  \begin{thebibliography}{00}
+\begin{thebibliography}{10}
 
@@
   Press.
+
+  \bibitem{brin1998anatomy}
+  Sergey Brin and Lawrence Page.
+  \newblock The anatomy of a large-scale hypertextual web search engine.
+  \newblock {\em Computer networks and ISDN systems}, 30(1-7):107--117, 1998.
 
@@
 
+  \bibitem{preston-werner}
+  Tom Preston-Werner.
+  \newblock Semantic versioning 2.0.0.
+
   \bibitem{Manikas:2017}
@@
 
-    \bibitem{brin1998anatomy}
-    Sergey Brin and Lawrence Page.
-    \newblock The anatomy of a large-scale hypertextual web search engine.
-    \newblock {\em Computer networks and ISDN systems}, 30(1-7):107--117, 1998.
-
-    \bibitem{preston-werner}
-    Tom Preston-Werner.
-    \newblock Semantic versioning 2.0.0.
-
 \end{thebibliography}

### 2019-04-12 resources/github-projects/dependency_intervals.py
a refactor of the project directory, added my modified versions of original scripts

@@ -1,0 +1,69 @@
+import json
+import sys
+import dateutil.parser
+
+"""This script takes as an input a package.json history file, and produces, for each dependency, an ordered list of requirement queries with begin and end time."""
+
+HISTORYFILE=sys.argv[1]
+
+with open(HISTORYFILE) as hf:
+    data = json.load(hf)
+
+    file_creation_time = dateutil.parser.parse(data["creation_time"])
+
+    commits_to_time = map(lambda p : (p[0], dateutil.parser.parse(p[1])), list(data["time"].iteritems()))
+    commits_to_time.sort(key=lambda p: p[1], reverse=True)
+
+    # This is the "end of the universe" date for this particular history file.
+    prev_date = file_creation_time
+
+    bounds = {}
+    devBounds = {}
+
+    for (commit,ts) in commits_to_time:
+        pkg_data = data["versions"][commit]
+
+        deps = pkg_data.get("dependencies", {})
+        devDeps = pkg_data.get("devDependencies", {})
+
+        for (dep,query) in deps.iteritems():
+            pair = (dep,query)
+            if not pair in bounds:
+                bounds[pair] = (ts,prev_date)
+            else:
+                before = bounds[pair]
+                bounds[pair] = (ts,before[1])
+
+        for (dep,query) in devDeps.iteritems():
+            pair = (dep,query)
+            if not pair in devBounds:
+                devBounds[pair] = (ts,prev_date)
+            else:
+                before = devBounds[pair]
+                devBounds[pair] = (ts,before[1])
+
+        prev_date = ts
+
+    final_object = {}
+    final_object["_id"] = data["_id"]
+    final_object["creation_time"] = data["creation_time"]
+
+    intervals = {}
+    devIntervals = {}
+
+    for ((d,v),(s,e)) in bounds.iteritems():
+        intervals["%s:%s" % (d,v)] = {
+            "from" : s.isoformat(),
+            "to"   : e.isoformat()
+        }
+
+    for ((d,v),(s,e)) in devBounds.iteritems():
+        devIntervals["%s:%s" % (d,v)] = {
+            "from" : s.isoformat(),
+            "to"   : e.isoformat()
+        }
+
+    final_object["dependencies"] = intervals
+    final_object["devDependencies"] = devIntervals
+
+    print json.dumps(final_object, indent=2)

### 2019-04-12 resources/github-projects/merge-intervals.py

@@ -1,0 +1,16 @@
+import glob
+import json
+import sys
+
+all_files = list(glob.glob("%s/*.json" % sys.argv[1]))
+
+for file_name in all_files:
+    with open(file_name) as fh:
+        data = json.load(fh)
+
+        for k,_ in data["devDependencies"].iteritems():
+            print k.encode('utf-8')
+
+        #for k,_ in data["dependencies"].iteritems():
+        #    print k.encode('utf-8')
+

### 2019-04-12 resources/github-projects/simplify-history.file.py

@@ -1,0 +1,34 @@
+import json
+import sys
+
+with open(sys.argv[1]) as hist_file:
+    data = json.load(hist_file)
+
+    simpler = {}
+
+    simpler["repository"]  = data["repository"]
+    simpler["_id"]         = data["_id"]
+    simpler["json_errors"] = data["json_errors"]
+
+    new_versions = {}
+
+    for k,v in data["versions"].iteritems():
+        new_v = {}
+
+        if "dependencies" in v:
+            new_v["dependencies"] = v["dependencies"]
+
+        if "devDependencies" in v:
+            new_v["devDependencies"] = v["devDependencies"]
+
+        if new_v:
+            new_versions[k] = new_v
+
+    new_time = dict(filter(lambda p: p[0] in new_versions, list(data["time"].iteritems())))
+
+    simpler["versions"] = new_versions
+    simpler["time"] = new_time
+
+    with open(sys.argv[2], 'w') as dest_file:
+        dest_file.write(json.dumps(simpler, indent=2))
+

### 2019-04-12 resources/original_scripts/data/reorder.py

@@ -1,0 +1,13 @@
+import json
+
+names = open("missing_names.json", 'r')
+name_list = json.load(names)
+
+fake_skim = []
+
+for name in name_list['names']:
+    fake_skim.append({"id":name})
+
+f = open("missing_names_skim.json", 'a')
+f.write(json.dumps(fake_skim))
+f.close()

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/github-projects/get-package-json-history.py

@@ -1,112 +1,0 @@
-import datetime
-import dateutil.parser
-import json
-import shutil
-import subprocess
-import sys
-import tempfile
-
-def clone_from_github(group_id, repo_id):
-    clone_dir = tempfile.mkdtemp(prefix="github-clone-%s-%s-" % (group_id, repo_id))
-    github_url = "https://github.com/%s/%s.git" % (group_id, repo_id)
-    subprocess.call([ 'git', 'clone', github_url, clone_dir ])
-    return clone_dir
-
-def commits_for_path(clone_dir, path):
-    # How to get the list of commits where a file is changed:
-    # git -C REPO --no-pager log --pretty=oneline -- PATH | cut -d ' ' -f 1
-    git_log = subprocess.Popen([
-        'git', '-C', clone_dir, '--no-pager', 'log', '--pretty=oneline', '--', path
-    ], stdout=subprocess.PIPE)
-
-    for line in git_log.stdout:
-        # SHA1 hashes are 40 chars
-        commit_hash = line[:40]
-        yield commit_hash
-
-def commit_date(clone_dir, commit):
-    # How to get the commit date:
-    # git -C REPO --no-pager log -1 --pretty=tformat:%ci HASH
-    git_log = subprocess.Popen([
-        'git', '-C', clone_dir, '--no-pager', 'log', '-1', '--pretty=tformat:%ci', commit
-    ], stdout=subprocess.PIPE)
-
-    for line in git_log.stdout:
-        # there should be only one...
-        date = dateutil.parser.parse(line.strip())
-
-    return date
-
-def json_contents_for_commit(clone_dir, path, commit):
-    git_show = subprocess.Popen([
-        'git', '-C', clone_dir, '--no-pager', 'show', "%s:%s" % (commit, path)
-    ], stdout=subprocess.PIPE)
-
-    try:
-        return json.load(git_show.stdout)
-    except:
-        sys.stderr.write("Failed to read JSON contents of file: %s at commit %s.\n" % (path, commit))
-        return None
-
-if __name__ == "__main__":
-    if len(sys.argv) == 2:
-        GIT_USER = "local"
-        GIT_REPO = sys.argv[1]
-        REPO = sys.argv[1]
-        delete_on_exit = False
-    elif len(sys.argv) == 3:
-        GIT_USER = sys.argv[1]
-        GIT_REPO = sys.argv[2]
-        REPO = clone_from_github(GIT_USER, GIT_REPO)
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/github-projects/github-sanity-check.py

@@ -1,39 +1,0 @@
-import sys
-import codecs
-import re
-import requests
-
-REPO_LIST = sys.argv[1]
-
-
-with open(REPO_LIST) as repo_file:
-    with open("404s.txt", "a") as fourofours:
-        with open("200s.txt", "a") as twohundreds:
-            ln = 0
-
-            for line in repo_file:
-                ln = ln + 1
-                m = re.match("""^([^/]*)/([^/]*)$""", line.strip())
-
-                if m is None:
-                    sys.stderr.write("Cannot parse line %d: %s\n" % (ln, line.strip()))
-                else:
-                    gh_user = m.group(1)
-                    gh_repo = m.group(2)
-
-                    print (gh_user, gh_repo)
-
-                    url = "https://raw.githubusercontent.com/%s/%s/master/package.json" % (gh_user, gh_repo)
-
-                    r = requests.get(url)
-
-                    if r.status_code == 200:
-                        twohundreds.write("%s/%s\n" % (gh_user, gh_repo))
-                        of = codecs.open("./package-files/%s--%s--package.json" % (gh_user, gh_repo), "w", "utf-8")
-                        of.write(r.text)
-                        of.close()
-                    elif r.status_code == 404:
-                        fourofours.write("%s/%s\n" % (gh_user, gh_repo))
-                    else:
-                        sys.stderr.write("Unexpected response code: %d.\n" % r.status_code)
-                         

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/github-projects/merge-intervals.py

@@ -1,16 +1,0 @@
-import glob
-import json
-import sys
-
-all_files = list(glob.glob("%s/*.json" % sys.argv[1]))
-
-for file_name in all_files:
-    with open(file_name) as fh:
-        data = json.load(fh)
-
-        for k,_ in data["devDependencies"].iteritems():
-            print k.encode('utf-8')
-
-        #for k,_ in data["dependencies"].iteritems():
-        #    print k.encode('utf-8')
-

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/github-projects/parse-package-json-history-files.py

@@ -1,92 +1,0 @@
-import json
-import glob
-import sys
-import itertools
-
-from collections import Counter
-
-directory = sys.argv[1]
-
-tot_repos = 0
-tot_vers  = 0
-tot_malf  = 0
-
-tot_declared_deps = 0
-tot_declared_dev_deps = 0
-
-tot_errors = 0
-
-dependency_counter = Counter({})
-dev_dependency_counter = Counter({})
-
-for path in glob.glob("%s/*.json" % directory):
-    with open(path) as history_file:
-        tot_repos += 1
-        try:
-            data = json.load(history_file)
-
-            num_versions = len(data["time"])
-            num_errors   = len(data["json_errors"])
-
-            tot_vers += num_versions
-            tot_malf += num_errors
-
-            times = data["time"]
-
-            local_deps = {}
-            local_dev_deps = {}
-
-            package_files = data["versions"].values()
-
-            dependency_blocks = filter(lambda d : isinstance(d, dict),
-                map(lambda p : p.get("dependencies", {}),
-                    package_files))
-
-            dev_dependency_blocks = filter(lambda d : isinstance(d, dict),
-                map(lambda p : p.get("devDependencies", {}),
-                    package_files))
-
-            dependency_lists = map(lambda d : d.keys(), dependency_blocks)
-            dev_dependency_lists = map(lambda d : d.keys(), dev_dependency_blocks)
-
-            all_dependencies = set(itertools.chain.from_iterable(dependency_lists))
-            all_dev_dependencies = set(itertools.chain.from_iterable(dev_dependency_lists))
-
-            dependency_counter += Counter(all_dependencies)
-            dev_dependency_counter += Counter(all_dev_dependencies)
-
-            tot_declared_deps += len(all_dependencies)
-            tot_declared_dev_deps += len(all_dev_dependencies)
-
-        except Exception as e:
-            print e 
-            tot_errors += 1
-
-valid_reps = float(tot_repos - tot_errors)
-
-print "# of repositories    : %d" % tot_repos
-print "Processing errors    : %d" % tot_errors
-print "Avg. # of versions   : %f" % (float(tot_vers) / valid_reps)
-print "Avg. # of json errors: %f" % (float(tot_malf) / valid_reps)
-print "Avg. # deps.         : %f" % (float(tot_declared_deps) / valid_reps)
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/github-projects/process-versions-by-frq.py

@@ -1,32 +1,0 @@
-import re
-import sys
-
-standard = 0
-non_standard = 0
-
-with open(sys.argv[1]) as frq_file:
-    for line in frq_file:
-
-        line = line.strip()
-
-        m = re.match("""^ *(\d)* (.*)$""", line)
-
-        if m is None:
-            print "Can't match: [%s]." % line
-            sys.exit(1)
-
-        count = int(m.group(1))
-
-        vstr = m.group(2)
-
-        m = re.match("""^(\d\d*)\.(\d\d*)\.(\d\d*)$""", vstr)
-
-        if m is None:
-            print vstr
-            non_standard += count
-        else:
-            standard += count
-
-
-print "Simple semver     : %d" % standard
-print "Non-simple semver : %d  (%4f%%)" % (non_standard, 100.0 * float(non_standard) / float(non_standard + standard))

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/data/convert_download_results.py

@@ -1,38 +1,0 @@
-# !/usr/bin/env python
-
-#
-# Small script to convert download results for easier processing with pandas:
-# - Makes package name the index
-# - Creates 2 files, one containing the download rank, the other containing the
-#   absolute download figures
-# 
-# Input example: "npm-downloads-ranking-2010-01-01-to-2015-09-01.csv"
-#
-import sys
-import re
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-
-if __name__=='__main__':
-  if len(sys.argv) < 2:
-    print 'usage: %s <input-data>' % (sys.argv[0])
-    exit(-1)
-  input_file = sys.argv[1]
-  file_name = input_file.split('/')[-1]
-  dates = re.compile(r'(\d+-\d+-\d+)', re.IGNORECASE).findall(file_name)
-  from_date = dates[0]
-  to_date = dates[1]
-  timespan = from_date + '_' + to_date
-
-  df = pd.read_csv(input_file, names=['rank', 'name', 'downloads'], index_col=1)
-  
-  df_rank = df['rank'].to_frame()
-  df_rank.columns = [timespan]
-  df_rank.to_csv('npm_graph_download-ranks_' + from_date + '_' + to_date + '.csv')
-
-  df_downloads = df['downloads'].to_frame()
-  df_downloads.columns = [timespan]
-  df_downloads.to_csv('npm_graph_downloads_' + from_date + '_' + to_date + '.csv')
-
-  # print df_rank

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/data/curate_npm_repos.py

@@ -1,43 +1,0 @@
-# !/usr/bin/env python
-
-#
-# Reads npm-metadata and creates a leaner output, containing only the package name,
-# version times, and dependency history.
-# 
-# Input is "npm_repos-09_22-15.txt" (Who named that file???)
-#
-import json
-import sys
-
-FILE = sys.argv[1]
-
-with open(FILE) as lines:
-  for line in lines:
-    d = json.loads(line)
-
-    nd = {}
-
-    nd["name"] = d["name"]
-
-    if "time" in d:
-      nd["time"] = d["time"]
-
-      # Actually useful
-      # del nd["time"]["created"]
-      del nd["time"]["modified"]
-
-    if "versions" in d:
-      nv = {}
-
-      for v,vd in d["versions"].iteritems():
-        nv[v] = {}
-
-        if "dependencies" in vd:
-          nv[v]["dependencies"] = vd["dependencies"]
-        
-        if "devDependencies" in vd:
-          nv[v]["devDependencies"] = vd["devDependencies"]
-
-      nd["versions"] = nv
-
-    print json.dumps(nd)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/data/extract_ghtorrent_js_repos.js

@@ -1,70 +1,0 @@
-/**
- * Finds JavaScript repositories in GHTorrent data.
- *
- * Input: <path-to-ghtorrent-repo-data>
- */
-
-var fs = require('fs')
-var byline = require('byline')
-
-function extractJSRepos (inputPath, outputPath) {
-  console.log('extract repos from %s', inputPath)
-
-  var repos = []
-
-  var lineCount = 0
-  var repoCount = 0
-  var noLanguage = 0
-
-  var stream = fs.createReadStream(inputPath)
-  stream = byline.createStream(stream, { encoding: 'utf8' })
-
-  stream.on('data', function (line) {
-    lineCount++
-    if (lineCount % 50000 === 0) console.log(' %s repos checked...', lineCount)
-
-    line = line.replace(/"_id" : ObjectId\( "[^"]*" \),/g, '')
-
-    try {
-      var repo = JSON.parse(line)
-      if (repo.full_name === 'request/request' || repo.full_name === 'caolan/async' || repo.full_name === 'facebook/react') {
-        console.log('       %s %s', repo.full_name, repo.language)
-      }
-      if (!repo.language) {
-        noLanguage++
-      } else if (repo.language && repo.language.toLowerCase() === 'javascript') {
-        repoCount++
-        repos.push({
-          full_name: repo.full_name,
-          fork: repo.fork
-        })
-      }
-    } catch (err) {
-      console.log(err)
-    }
-  })
-
-  stream.on('finish', function () {
-    console.log('done processing %s repos - %s JavaScript repos found - %s have no language', lineCount, repoCount, noLanguage)
-    storeRepos(repos, outputPath)
-  })
-}
-
-function storeRepos (repos, outputPath) {
-  fs.writeFile(outputPath, JSON.stringify(repos, null, 2), function (err) {
-    if (err) {
-      console.log(err)
-    } else {
-      console.log('repos saved to %s', outputPath)
-    }
-  })
-}
-
-if (!module.parent) {
-  if (typeof process.argv[2] === 'undefined' ||
-    typeof process.argv[3] === 'undefined') {
-    console.log('usage: node %s <path-to-ghtorrent-repo-data> <output-path>', process.argv[1])
-  } else {
-    extractJSRepos(process.argv[2], process.argv[3])
-  }
-}

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/data/get_npm_metadata.js

@@ -1,98 +1,0 @@
-/**
- * Loads complete set on npm metadata in two steps:
- * 1.) Get npm skim
- * 2.) Get package-specific metadata for every package contained in the skim
- *
- * No further input required.
- */
-
-var fs = require('fs')
-var JSONStream = require('JSONStream')
-var Transform = require('stream').Transform
-var request = require('request')
-var async = require('async')
-var moment = require('moment')
-
-// kick things off:
-loadRepoList()
-
-// config:
-var concurrency = 25
-
-function loadRepoList () {
-  var readCount = 0
-  var repoList = []
-
-  // set up streams:
-  var parser = JSONStream.parse('rows.*')
-  var extractor = new Transform({objectMode: true})
-  extractor._transform = function (dataObj, encoding, done) {
-    readCount++
-    if (readCount % 10000 === 0) console.log('%s repositories assessed...', readCount)
-
-    repoList.push(dataObj.id)
-
-    this.push(dataObj)
-    done()
-  }
-  var stringifyer = JSONStream.stringify('[\n', '\n,\n', '\n]\n', '\t')
-  var outputPath = '../../data/' + moment().format('YYYY-MM-DD') + '_npm_skim.json'
-  var wstream = fs.createWriteStream(outputPath, {encoding: 'utf8'})
-
-  // start streams:
-  request
-    .get('https://skimdb.npmjs.com/registry/_design/scratch/_view/byField')
-    .pipe(parser)
-    .pipe(extractor)
-    .pipe(stringifyer)
-    .pipe(wstream)
-      .on('error', function (err) {
-        console.log('Error: ' + err)
-      })
-      .on('finish', function () {
-        console.log('loaded list of %s repositories; will consider %s in the following', readCount, repoList.length)
-        console.log('written results to "%s"', outputPath)
-        loadData(repoList)
-      })
-}
-
-function loadData (repoList) {
-  var loadCount = 0
-  var successCount = 0
-  var errorCount = 0
-  var outputPath = '../../data/' + moment().format('YYYY-MM-DD') + '_npm_repos.txt'
-
-  async.eachLimit(repoList, concurrency, function (id, callback) {
-    if (loadCount % 1000 === 0) console.log('%s loaded...', loadCount)
-    request({
-      method: 'GET',
-      uri: 'https://registry.npmjs.org/' + id,
-      json: true
-    }, function (err, res, body) {
-      loadCount++
-      if (err || res.statusCode !== 200) {
-        errorCount++
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/data/influx_query.sh

@@ -1,10 +1,0 @@
-#!/bin/bash
-#/opt/influxdb/influx -execute="select sum(value) from downloads where time >= '2015-09-01T00:00:00Z' AND time < '2015-09-02T00:00:00Z' group by package" \
-#	-database=npm -username=user -password=passw0rd -format='csv' >/tmp/a
-/opt/influxdb/influx -execute="select sum(value) from downloads where time < '2015-09-02T00:00:00Z' group by package" \
-	-database=npm -username=user -password=passw0rd -format='csv' >/tmp/a
-
-grep 'downloads' /tmp/a |cut -d '=' -f2|cut -d ',' -f1,3|sort -g -r -t',' -k2 >/tmp/b
-#python add-ranking-to-sortedlist.py /tmp/b >npm-downloads-ranking-2015-08-26-to-2015-09-01.csv
-python add-ranking-to-sortedlist.py /tmp/b >npm-downloads-ranking-2010-01-01-to-2015-09-01.csv
-

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph-versioned/create_gt_graphs_versioned.py

@@ -1,9 +1,0 @@
-#!/usr/bin/env python
-import glob
-import create_graph as g
-
-if __name__=='__main__':
-  fake_graph_list = glob.glob('../../data/json-graphs/*.json')
-  for fake_graph_path in fake_graph_list:
-    print fake_graph_path
-    g.create_graph(fake_graph_path)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph-versioned/create_json_graphs_versioned.js

@@ -1,66 +1,0 @@
-var moment = require('moment')
-require('moment-range')
-var graphSnapshot = require('./graph-snapshot')
-var async = require('async')
-var fs = require('fs')
-
-;(function () {
-  function getDateRange (start, end) {
-    var results = []
-    var startDate = moment(start, 'YYYY-MM-DD')
-    var endDate = moment(end, 'YYYY-MM-DD')
-    // var range = date.range('month')
-    var range = moment.range(startDate, endDate)
-    range.by('months', function (moment) {
-      results.push(moment.format('YYYY-MM-DD'))
-    })
-    return results
-  }
-
-  if (!module.parent) {
-    if (typeof process.argv[2] !== 'undefined' ||
-      typeof process.argv[3] !== 'undefined' ||
-      typeof process.argv[4] !== 'undefined' ||
-      typeof process.argv[5] !== 'undefined') {
-      // get params:
-      var inputPath = process.argv[2]
-      var start = process.argv[3]
-      var end = process.argv[4]
-      var simple = (process.argv[5] === 'true')
-
-      var range = getDateRange(start, end)
-      console.log(range)
-
-      var results = []
-      async.eachSeries(range, function (date, callback) {
-        var outputPath = '../../data/json-graphs-versioned/' + date + '_npm_graph_versioned.json'
-        if (simple) {
-          outputPath = '../../data/json-graphs/' + date + '_npm_graph.json'
-        }
-        graphSnapshot.createSnapshot(inputPath, outputPath, date, simple, function (err, result) {
-          if (err) {
-            callback(err)
-          } else {
-            results.push(result)
-            callback()
-          }
-        })
-      }, function done () {
-        console.log('Finished')
-        var outputFile = '../../data/report_' + start + '_' + end + '_versioned.json'
-        if (simple) {
-          outputFile = '../../data/report_' + start + '_' + end + '.json'
-        }
-        fs.writeFile(outputFile, JSON.stringify(results, null, 2), function (err) {
-          if (err) {
-            console.log(err)
-          } else {
-            console.log('saved results to %s', outputFile)
-          }
-        })
-      })
-    } else {
-      console.log('usage: node %s <input-path> <start-date> <end-date> <simple?>', process.argv[1])
-    }
-  }
-})()

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph-versioned/pageranks.py

@@ -1,57 +1,0 @@
-import json
-import sys
-import pytz
-import re
-import os
-import glob
-import csv
-
-from graph_tool.all import *
-
-def create_pageranks():
-  # obtain list of all graph files (*.gt):
-  graph_file_list = glob.glob('../../data/graphs/*.gt')
-
-  # determine page rank and store results as CSVs:
-  for file_name in graph_file_list:
-    print 'perform page rank for %s' % file_name
-    
-    ranking = []
-
-    g = load_graph(file_name)
-    pr = graph_tool.centrality.pagerank(g)
-    
-    for v in g.vertices():
-      # print '%s (%s) has pagerank: %s' % (graph.vp.name[v], graph.vp.version[v], pr[v])
-      ranking.append({
-        'name_and_version': g.vp.name[v] + '_' + g.vp.version[v],
-        'name': g.vp.name[v],
-        'version': g.vp.version[v],
-        'pr_value': pr[v]
-        })
-
-    # sort results by rank:
-    ranking = sorted(ranking, key=lambda k: k['pr_value'], reverse=True)
-
-    for i in range(0, len(ranking)):
-      ranking[i]['rank'] = i + 1
-
-    # store results under the right date:
-    date = re.search('[0-9][0-9][0-9][0-9]-[0-9][0-9]-[0-9][0-9]', file_name).group(0) # os.path.splitext(file_name)[0]
-    output_file = '../../data/pageranks/%s_pagerank.csv' % (date)
-    
-    keys = ranking[0].keys()
-    with open(output_file, 'wb') as of:
-      dict_writer = csv.DictWriter(of, keys)
-      dict_writer.writeheader()
-      dict_writer.writerows(ranking)
-    print 'written results of %s to %s' % (file_name, output_file)
-
-  # outfile = 'top_%s_results.json' % str(top)
-  # with open(outfile, 'w') as outfile:
-  #   json.dump(overall_results, outfile, sort_keys=True, indent=4)
-  # print 'results written to %s' % outfile
-
-
-if __name__=='__main__':
-  g = create_pageranks()

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph-versioned/pageranks_top.py

@@ -1,62 +1,0 @@
-import json
-import sys
-import pytz
-import re
-import os
-import glob
-
-from graph_tool.all import *
-
-def get_all_graphs(top=25):
-  overall_results = {}
-
-  # obtain list of all graph files (*.gt):
-  graph_file_list = glob.glob('../../data/gt-graphs-versioned/*.gt')
-  
-  for file_name in graph_file_list:
-    print 'perform page rank for %s' % file_name
-    g = load_graph(file_name)
-    pr = graph_tool.centrality.pagerank(g)
-    results = []
-    ranking = []
-    for v in g.vertices():
-      # print '%s (%s) has pagerank: %s' % (graph.vp.name[v], graph.vp.version[v], pr[v])
-      ranking.append({
-        'name': g.vp.name[v],
-        'version': g.vp.version[v],
-        'rank': pr[v]
-        })
-    ranking = sorted(ranking, key=lambda k: k['rank'], reverse=True)
-
-    # don't try to use 'top' results, if there are not enough results:
-    upper_bound = min(len(ranking), top)
-
-    for i in range(0, upper_bound):
-      results.append({
-        'name':     ranking[i]['name'],
-        'version':  ranking[i]['version'],
-        'pagerank': ranking[i]['rank'],
-        'rank':     i
-      })
-
-    # pad missing entries:
-    for i in range(upper_bound, top):
-      results.append({
-        'name':     'NA',
-        'version':  'NA',
-        'pagerank': 0,
-        'rank':     i
-      })
-
-    # store results under the right date:
-    date = re.search('[0-9][0-9][0-9][0-9]-[0-9][0-9]-[0-9][0-9]', file_name).group(0) # os.path.splitext(file_name)[0]
-    overall_results[date] = results
-
-  outfile = '../../data/top_%s_results.json' % str(top)
-  with open(outfile, 'w') as outfile:
-    json.dump(overall_results, outfile, sort_keys=True, indent=4)
-  print 'results written to %s' % outfile
-
-
-if __name__=='__main__':
-  g = get_all_graphs(5)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph-versioned/plot_libraries.py

@@ -1,28 +1,0 @@
-#!/usr/bin/env python
-import pandas as pd
-import numpy as np
-import re
-import matplotlib.pyplot as plt
-
-df = pd.read_csv('../../data/all_pageranks_simple.csv', index_col=0, parse_dates=0)
-
-print df['underscore']
-
-
-#repos = ['express', 'connect', 'async']
-# repos = ['backbone', 'ember', 'backbone.marionette', 'knockout', 'dojo', 'angular', 'polymer']
-repos = ['lodash', 'underscore', 'sugar']
-# repos = ['request', 'superagent', 'restler']
-
-
-ax = df[repos[0]].plot(title='Utility lib wars', logy=True)
-
-for i in range(1, len(repos)):
-  df[repos[i]].plot()
-
-ax.legend(repos, loc='lower center')
-# reverse y-axis:
-plt.gca().invert_yaxis()
-plt.gca().set_ybound(lower=0, upper=None)
-
-plt.show()

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/calc_accumulative_top_packages.py

@@ -1,58 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Calculate the number of new packages entering the top N over time.
-# 
-# Input: 
-# - package ranking data over time, e.g., npm_graph_pr_top_100_weekly_...
-# - N = the number of top packages to consider
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-def calc_accumulative_top(input_file, top_list):
-  frames = []
-
-  df = pd.read_csv(input_file, index_col=0, parse_dates=0)
-
-  # list to store all packages already seen:
-  result = {}
-
-  for top in top_list:
-    seen_list = []
-    # iterate columns:
-    for i in range(len(df.columns)):
-      col = df.ix[:,i]
-
-      print '%s: seen %s packages in the top %s' % (col.name, len(seen_list), top)
-      if col.name not in result:
-        result[col.name] = []
-      result[col.name].append(len(seen_list))
-
-      # iterate entries in column:
-      for index, value in col.iteritems():
-        if not np.isnan(value) and value <= top:
-          if index not in seen_list:
-            seen_list.append(index)
-          # print index + ' ' + str(value)
-
-  df_acc = pd.DataFrame(result).T
-  df_acc.columns = top_list
-
-  axes = df_acc.plot()
-  # axes.set_xlabel('date')
-  # axes.set_ylabel('absolute pagerank changes since one week ago')
-  plt.show()
-
-
-if __name__=='__main__':
-  if len(sys.argv) < 3:
-    print 'usage: %s [input_file, e.g., npm_graph_pr_top_100_weekly_...] [top numbers, e.g., 10 50 100...]' % (sys.argv[0])
-    exit(-1)
-  input_file = sys.argv[1]
-  top_list = map(lambda a : int(a), sys.argv[2:])
-  calc_accumulative_top(input_file, top_list)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/calc_clean_growth.py

@@ -1,112 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Script to calculate package growth over time considering only active packages.
-# 
-# Input: 
-# - "npm_version_dates.json"
-#    (which is an array of JSON objects describing each package in the following way:
-#        {
-#          "name": "...",
-#          "time": {
-#            "created": "2013-05-18T14:04:50.640Z",
-#            "0.0.1": "2013-05-18T14:04:53.742Z",
-#            ...
-#          }
-#        }
-#    )
-# - Number of days in which activity must have occurred for a package to be considered.
-#
-import sys
-import json
-import time
-import datetime
-import pytz
-import pandas as pd
-
-from dateutil import rrule, parser
-
-
-def visualize_growth_clean(input_file, delta_value):
-  # create a date range:
-  dates = get_date_range('10-01-2010', '09-01-2015', 'weekly')
-  # localize:
-  dates = map(lambda x: pytz.UTC.localize(x), dates)
-
-  repos_at_date = {}
-  for date in dates:
-    repos_at_date[str(date)] = 0  
-  count = 0
-
-  delta = datetime.timedelta(days=delta_value)
-
-  with open(input_file) as data_file:    
-    data = json.load(data_file)
-
-  print 'loaded data.'
-
-  for repo in data:
-    count  += 1
-    if count % 200 == 0:
-      print '%s - %s' % (count, repo['name'])
-
-    # iterate dates:
-    if 'time' in repo:
-      for date in dates:
-        date_str = str(date)
-        latest_version_date = pytz.UTC.localize(datetime.datetime(2010, 1, 1))
-        latest_version = None
-
-        for key, version in enumerate(repo['time']):
-          version_date = parser.parse(repo['time'][version])
-          try:
-            if version_date < date and latest_version_date < version_date:
-              latest_version_date = version_date
-              latest_version = version
-          except TypeError:
-            pass
-        if latest_version is not None and (date - latest_version_date) < delta:
-          # print 'Latest version of "%s" (%s) is NEWER than %s at %s' % (repo['name'], latest_version, delta_value, date_str)
-          repos_at_date[date_str] += 1
-        else:
-          # print 'Latest version of "%s" (%s) is OLDER than %s at %s' % (repo['name'], latest_version, delta_value, date_str)
-          pass
-
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/calc_keyword_search_ranks.py

@@ -1,94 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Prints the popularity of all packages for given keyword.
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-files = [
-  {
-    'name': 'GitHub',
-    'path': '../../data/pageranks/apps_graph_bipartite_in-deg_daily_09-01-2015_09-01-2015.csv'
-  }
-  ,
-  {
-    'name': 'npm',
-    'path': '../../data/pageranks/npm_graph_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
-  }
-  ,
-  {
-    'name': 'downloads',
-    'path': '../../data/downloads/npm_graph_download-ranks_2015-08-01_2015-09-01.csv'
-  }
-  ,
-  {
-    'name': 'keywords',
-    'path': '../../data/npm_repos_keywords.csv'
-  }
-]
-
-def calc_popularity(keyword):
-  frames = []
-
-  # get filtered GitHub dependencies:
-  frames.append(get_filtered_github(files[0]['path']))
-
-  # get filtered pageranks:
-  frames.append(get_filtered_pageranks(files[1]['path']))
-
-  # get filtered downloads: (NO processing needed, all have downloads)
-  df_downloads = pd.read_csv(files[2]['path'], index_col=0)
-  df_downloads.columns = ['downloads']
-  frames.append(df_downloads)
-
-  # get keywords:
-  df_keywords = pd.read_csv(files[3]['path'], index_col=0)
-  df_keywords.columns = ['keywords']
-  frames.append(df_keywords)
-
-  # create overall dataframe:
-  df = pd.concat(frames, axis=1).dropna(subset=['keywords'])
-
-  result_df = df[df['keywords'].str.contains(keyword)]
-
-  print result_df.sort_values('GitHub dependencies')
-
-  print result_df.sort_values('npm pagerank')
-
-  print result_df.sort_values('downloads')
-
-
-def get_filtered_pageranks(file_name):
-  df = pd.read_csv(file_name, index_col=0)
-  # filter min values:
-  min_pagerank_value = df.min()[0]
-  df_filtered = df[(df['2015-09-01'] != min_pagerank_value)]
-  
-  # create ranking:
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/calc_newrepos_everymonth.py

@@ -1,108 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Script to generate a lit of new packages introduced into npm, by month
-# 
-# Input: 
-# - "npm_version_dates.json"
-#    (which is an array of JSON objects describing each package in the following way:
-#        {
-#          "name": "...",
-#          "time": {
-#            "created": "2013-05-18T14:04:50.640Z",
-#            "0.0.1": "2013-05-18T14:04:53.742Z",
-#            ...
-#          }
-#        }
-#    )
-#
-import sys
-import json
-import time
-import datetime
-import pytz
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-
-from dateutil import rrule, parser
-
-
-def visualize_newrepos(input_file):
-  # create a date range:
-  dates = get_date_range('10-01-2010', '09-01-2015', 'monthly')
-  # localize:
-  dates = map(lambda x: pytz.UTC.localize(x), dates)
-
-  end_date = dates[-1]
-  dates.pop()
-
-  repos_at_date = {}
-  for date in dates:
-    repos_at_date[date.strftime('%Y-%m-%d')] = 0
-  count = 0
-  errors = 0
-  
-  with open(input_file) as data_file:    
-    data = json.load(data_file)
-
-  print 'loaded data.'
-
-  for repo in data:
-    count  += 1
-    if count % 200 == 0:
-      print '%s - %s' % (count, repo['name'])
-
-    # iterate dates:
-    if 'time' in repo:
-      version_date = parser.parse(repo['time']['created'])
-      try:
-        if version_date < end_date:
-          date_str = version_date.strftime('%Y-%m-01')
-          repos_at_date[date_str] += 1
-      except TypeError:
-        errors += 1
-        pass
-      except KeyError:
-        errors += 1
-        pass
-
-  print 'Had %d errors' % (errors)
-  print 'Total num repos in buckets is %d against total processed %d' % (sum(repos_at_date.values()), count)
-
-  df = pd.DataFrame(repos_at_date, index=[0]).T
-  df.columns = ['newrepos']
-  print df
-  df.to_csv('npm_newpkgs_per_month.csv')
-
-
-
-#
-# Creates a list of dates from the start date to the end date
-# with the given interval
-#
-def get_date_range(start_date, end_date, interval):
-  # create dates:
-  rule = rrule.DAILY
-  if interval == 'daily':
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/calc_rank_differences.py

@@ -1,72 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Calculate the differences in rank of packages in the two given 
-# files and sort results correspondingly.
-# 
-# Input (examples):
-#   npm_graph_pr_top_1800000_weekly_10-01-2010_09-01-2015.csv
-#   npm_graph_downloads-ranks_2015-09-01.csv
-#   
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-def calc_rank_differences(input_file_1, input_file_2):
-  df = get_dfs(input_file_1, input_file_2)
-
-  col1 = df.ix[:,0]
-  name1 = ' '.join(col1.name.split('_')[:4])
-  col2 = df.ix[:,1]
-  name2 = ' '.join(col2.name.split('_')[:4])
-  sub = col1 - col2
-  subname = name1 + ' - ' + name2
-  sub.name = subname
-
-  df = pd.DataFrame(sub).sort_values(subname, ascending=False)
-
-  df = df.dropna()
-
-  print '\nDoing much better in "%s" than in "%s":' % (name1, name2)
-  for index, row in df.tail(10).sort_values(subname).abs().iterrows():
-    print '%30s: difference=%s %30s=%s %30s=%s' % (index, row[subname], name1, col1[index], name2, col2[index])
-  # print df.tail(10).sort_values(subname).abs()
-
-  print '\nDoing much better in "%s" than in "%s":' % (name2, name1)
-  for index, row in df.head(10).iterrows():
-    print '%30s: difference=%s %30s=%s %30s=%s' % (index, row[subname], name1, col1[index], name2, col2[index])
-
-  # print df
-
-
-def get_dfs(input_file_1, input_file_2):
-  frames = []
-
-  print '  read %s...' % (input_file_1)
-  name_1 = input_file_1.split('/')[-1]
-  df_1 = pd.read_csv(input_file_1, index_col=0)
-  df_1.columns = [name_1]
-  frames.append(df_1)
-
-  print '  read %s...' % (input_file_2)
-  name_2 = input_file_2.split('/')[-1]
-  df_2 = pd.read_csv(input_file_2, index_col=0)
-  print df_2
-  df_2.columns = [name_2]
-  frames.append(df_2)
-
-  print '  concatenate...'
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/calc_rank_differences_complex.py

@@ -1,55 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Calculate the differences in rank of packages in multiple given 
-# files and sort results correspondingly.
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-files = [
-  {
-    'name': 'GitHub',
-    'path': '../../data/pageranks/apps_graph_bipartite_pr_top_300000_daily_09-01-2015_09-01-2015.csv'
-  }
-  ,
-  {
-    'name': 'npm',
-    'path': '../../data/pageranks/npm_graph_pr_top_300000_daily_09-01-2015_09-01-2015.csv'
-  }
-  ,
-  {
-    'name': 'downloads',
-    'path': '../../data/downloads/npm_graph_download-ranks_2015-08-01_2015-09-01.csv'
-  }
-]
-
-
-frames = []
-for o in files:
-  df = pd.read_csv(o['path'], index_col=0)
-  df.columns = [o['name']]
-  frames.append(df)
-
-df = pd.concat(frames, axis=1)
-df = df.dropna()
-# df['min'] = pd.DataFrame([df['npm pagerank'], df['Bipartite pagerank']]).min()
-
-df = df.sort_values('downloads', ascending=False)
-
-df['diff'] = df['downloads'] - df['npm']
-
-df = df.sort_values('diff', ascending=False)
-
-print df
-
-# df = ((df + df.shift(-1)) / 300)[::300]
-# print df
-
-axes = df['diff'].plot()
-axes.set_xlabel('packages')
-axes.set_ylabel('difference between GitHub and npm pageranks')
-plt.show()

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/calculate_pr_dynamics.py

@@ -1,43 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Calculates the changes of repository pageranks between pairs of dates
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-def calculate_pr_dynamics(input_file):
-  frames = []
-
-  df = pd.read_csv(input_file, index_col=0, parse_dates=0).T
-
-  # print df
-
-  for i in range(len(df.columns) - 1):
-    col1 = df.ix[:,i]
-    col2 = df.ix[:,i+1]
-    sub = col1 - col2
-    sub.name = col2.name # str(col1.name) + '_' + str(col2.name)
-    frames.append(pd.DataFrame(sub))
-   
-  print len(frames)
-  df = pd.concat(frames)
-  df_change = df.abs().sum()
-
-  axes = df_change.plot(title='Pagerank changes within top 100')
-  axes.set_xlabel('date')
-  axes.set_ylabel('absolute pagerank changes since one week ago')
-
-  plt.show()
-
-
-if __name__=='__main__':
-  if len(sys.argv) < 2:
-    print 'usage: %s [input_file] ' % (sys.argv[0])
-    exit(-1)
-  input_file = sys.argv[1]
-  calculate_pr_dynamics(input_file)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/create-gt-graph.py

@@ -1,127 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Creates a .gt graph (graph-tool) from given JSON graph.
-# The JSON graph is expected to be a JSON object of the following form:
-# 
-# {
-#   "package_a": {
-#     "creationDate": 1359595266159,
-#     "deps": {
-#       "package_b": [
-#         {
-#           "from": 1359595266159,
-#           "to": 1500000000000
-#         },
-#         ...
-#       ]
-#     },
-#     ...
-#   },
-#   ...
-# }
-#
-
-import json
-import sys
-import pytz
-import re
-import os
-
-from graph_tool.all import *
-
-
-def create_graph(input_file, do_bipartite):
-  print '--------------'
-  fake_graph = load_data(input_file)
-  print 'loaded graph with %s nodes' % (len(fake_graph))
-  graph = construct_graph(fake_graph, do_bipartite)
-  print 'created graph with %s nodes and %s edges' % (graph.num_vertices(), graph.num_edges())
-  save_graph(graph, input_file, do_bipartite)
-
-
-# loads the fake graph and returns it as dict:
-def load_data(input_file):
-  print 'read input data at %s...' % (input_file)
-  with open(input_file) as f:    
-    return json.load(f)
-
-
-def save_graph(graph, input_file, do_bipartite):
-  # save the graph:
-  output_file = '../../data/gt-graphs/' + os.path.splitext(input_file)[0].split('/')[-1] + '.gt'
-  if do_bipartite:
-    output_file = '../../data/gt-graphs/' + os.path.splitext(input_file)[0].split('/')[-1] + '_bipartite.gt'
-  graph.save(output_file, fmt='gt')
-  print 'done. graph saved to "%s"' % (output_file)
-
-
-def construct_graph(fake_graph, do_bipartite):
-  print 'start creating graph...'
-  # graph variables:
-  g = Graph()
-  vprop_name = g.new_vertex_property('string')
-  vprop_created = g.new_vertex_property('string')
-  eprop_from = g.new_edge_property('long')
-  eprop_to = g.new_edge_property('long')
-
-  # store properties to graph:
-  g.vertex_properties["name"] = vprop_name
-  g.vertex_properties["created"] = vprop_created
-  g.edge_properties["fromdate"] = eprop_from
-  g.edge_properties["todate"] = eprop_to
-
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/create-json-graph.js

@@ -1,325 +1,0 @@
-
-/**
- * Creates a JSON graph from input data, in which every line
- * is a stringified JSON object describing an npm package,
- * as available at http://registry.npmjs.org/<name>
- */
-
-var fs = require('fs')
-var byline = require('byline')
-var moment = require('moment')
-var semver = require('semver')
-
-;(function () {
-  function createSnapshotFromSingleFile (inputPath, outputPath, callback) {
-    console.log('create FULL snapshot from file %s.', inputPath)
-
-    var graph = {}
-
-    var lineCount = 0
-    var numNodes = 0
-    var numDeps = 0
-    var numLostDeps = 0
-    var numReDeps = 0
-    var start = new Date().getTime()
-
-    console.log('read input data from file...')
-    var stream = fs.createReadStream(inputPath)
-    stream = byline.createStream(stream)
-
-    stream.on('data', function (line) {
-      lineCount++
-      if (lineCount % 10000 === 0) console.log('%s lines...', lineCount)
-      var repo = JSON.parse(line)
-      var formattedVersions = getFormattedVersions(repo, 1500000000000, true)
-      if (formattedVersions) {
-        numNodes++
-        graph[repo.name] = formattedVersions.deps
-        numDeps += formattedVersions.numDeps
-        numLostDeps += formattedVersions.numLostDeps
-        numReDeps += formattedVersions.numReDeps
-      }
-    })
-
-    stream.on('finish', function () {
-      var end = new Date().getTime()
-      var time = (end - start) / 1000
-      console.log('Created graph from %s lines', lineCount)
-      console.log(' - %s nodes', numNodes)
-      console.log(' - %s edges (%s lost deps, %s recreated deps)', numDeps, numLostDeps, numReDeps)
-      console.log(' - %s seconds to create nodes', time)
-      var results = {
-        numNodes: numNodes,
-        numDeps: numDeps,
-        numLostDeps: numLostDeps,
-        numReDeps: numReDeps
-      }
-      storeGraph(graph, outputPath, results, callback)
-    })
-  }
-
-  function createSnapshotFromMultipleFiles (inputPath, outputPath, callback) {
-    console.log('create FULL snapshot from folder %s.', inputPath)
-
-    // remove possibly existing file:
-    try {
-      if (fs.existsSync(outputPath)) {
-        fs.unlinkSync(outputPath)
-        console.log('removed file %s', outputPath)
-      } else {
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/create_diff_dataframe.py

@@ -1,118 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Creates a dataframe containing all packages from npm
-# as well as their ranking regarding different popularity metrics
-# and the differences in rank between these metrics.
-# 
-# The resulting DataFrame will ONLY consider packages that have a valid
-# rank regarding at least one popularity measure!
-# 
-# No further input required.
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-files = [
-  {
-    'name': 'GitHub',
-    'path': '../../data/pageranks/apps_graph_bipartite_in-deg_daily_09-01-2015_09-01-2015.csv'
-  }
-  ,
-  {
-    'name': 'npm',
-    'path': '../../data/pageranks/npm_graph_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
-  }
-  ,
-  {
-    'name': 'downloads',
-    'path': '../../data/downloads/npm_graph_download-ranks_2015-08-01_2015-09-01.csv'
-  }
-  ,
-  {
-    'name': 'keywords',
-    'path': '../../data/npm_repos_keywords.csv'
-  }
-]
-
-def create_popularity_csv():
-  frames = []
-
-  # get filtered GitHub dependencies:
-  frames.append(get_filtered_github(files[0]['path']))
-
-  # get filtered pageranks:
-  frames.append(get_filtered_pageranks(files[1]['path']))
-
-  # get filtered downloads: (NO processing needed, all have downloads)
-  df_downloads = pd.read_csv(files[2]['path'], index_col=0)
-  df_downloads.columns = ['downloads']
-  frames.append(df_downloads)
-
-  df_keywords = pd.read_csv(files[3]['path'], index_col=0, sep=',')
-  df_keywords.columns = [files[3]['name']]
-  frames.append(df_keywords)
-
-  # create overall dataframe:
-  df = pd.concat(frames, axis=1)
-
-  # # create difference dataframes:
-  df_diff_1 = get_diff_df(df, 'npm', 'GitHub')
-
-  df_diff_2 = get_diff_df(df, 'npm', 'downloads')
-
-  df_diff_3 = get_diff_df(df, 'downloads', 'GitHub')
-
-  df = pd.concat([df, df_diff_1, df_diff_2, df_diff_3], axis=1)
-
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/developer_activity.py

@@ -1,113 +1,0 @@
-#!/usr/bin/python
-
-##input: developer_activity.py 2015-11-01_npm_skim.json npm_version_dates.json
-
-import json
-import sys
-import math
-import datetime
-import pytz
-import pandas as pd
-import numpy as np
-from pandas.io.json import json_normalize
-from dateutil import rrule, parser
-
-#
-# Creates a list of dates from the start date to the end date
-# with the given interval
-#
-def get_date_range(start_date, end_date, interval):
-  # create dates:
-  rule = rrule.DAILY
-  if interval == 'daily':
-    rule = rrule.DAILY
-  elif interval == 'weekly':
-    rule = rrule.WEEKLY
-  elif interval == 'monthly':
-    rule = rrule.MONTHLY
-  else:
-    print 'Could not identify interval %s. Try daily, weekly, or monthly' % (interval)
-
-  dates = list(rrule.rrule(rule,
-            interval=1,
-            dtstart=parser.parse(start_date),
-            until=parser.parse(end_date)))
-  return dates
-
-def packages_devs_per_month(skim_file, versions_file):
-    packages = {}
-    versions = {}
-    
-    with open(skim_file) as fp:
-        packages = json.load(fp)
-
-    with open(versions_file) as fp:
-        tempversions = json.load(fp)
-
-    for p in tempversions:
-        try:
-            versions[p['name']] = p['time']
-        except KeyError:
-            pass
-
-    dates = get_date_range('10-01-2010', '09-01-2015', 'monthly')
-    # localize:
-    dates = map(lambda x: pytz.UTC.localize(x), dates)
-
-    start_date = dates[0]
-    end_date = dates[-1]
-    dates.pop()
-
-    p_other = {}
-    repos_at_date = {}
-    all_maintainers = {}
-    total_devs = 0
-    for date in dates:
-        repos_at_date[date.strftime('%Y-%m-%d')] = {"Packages": 0, "Developers" : 0}
-
-    for p in packages:
-      try:
-        name = p['value']['name']
-        vcount = len(versions[name]) - 1
-        created = parser.parse(versions[name]['created'])
-        created_str = created.strftime('%Y-%m-01')
-        license = p['value']['license']
-        for m in p['value']['maintainers']:
-          if m['email'] in all_maintainers:
-            all_maintainers[m['email']]['Packages'] += 1
-          else:
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/new_calc_growth_regression.py

@@ -1,61 +1,0 @@
-import sys
-import math
-import pandas as pd
-import numpy as np
-import math
-import matplotlib.pyplot as plt
-from scipy.optimize import curve_fit
-
-def linear_regression(x, y):
-    A = np.vstack([ x, np.ones(len(x)) ]).T
-    m,c = np.linalg.lstsq(A, y)[0]
-    return m,c
-
-def scale_data(x):
-    """Returns (xs, a, b) such that x = a + xs*b."""
-    m = np.min(x)
-    x0 = x - m
-    M = np.max(x0)
-    x1 = x0 / M
-    return (x1, m, M)
-
-def f(x0, a, b, c):
-    return a * np.exp(b * x0) + c
-
-def fit_exp(x, y):
-    popt, pcov = curve_fit(f, x, y, maxfev=100000000)
-    print popt
-    print pcov
-    return (popt[0], popt[1], popt[2])
-
-def work(input_file):
-    df = pd.read_csv(input_file).T
-
-    df = df.ix[1:]
-
-    df.index = pd.to_datetime(df.index)
-
-    x = df.index.astype(np.int64).astype(np.float64) / 10000000000000.0
-    y = df[4].astype(np.float64).as_matrix()
-
-    (xs, xa, xb) = scale_data(x)
-    (ys, ya, yb) = scale_data(y)
-
-    (a,b,c) = fit_exp(xs, ys)
-
-    ys_approx = f(xs, a, b, c)
-    y_approx  = ya + yb * ys_approx
-
-    plt.plot(x, y, label="Number of packages")
-
-    plt.plot(x, y_approx, label="Approximation")
-
-    plt.show()
-
-if __name__ == "__main__":
-  if len(sys.argv) < 2:
-      sys.stderr.write("Usage: %s <input-data>\n" % sys.argv[0])
-      sys.exit(1)
-
-  input_file = sys.argv[1]
-  work(input_file)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/pageranks.py

@@ -1,309 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Calculates pagerank over given period of time.
-# 
-# Input:
-# - GT Graph file, e.g., "npm_graph.gt"
-# - Start-date (MM-DD-YYYY)
-# - End-date (MM-DD-YYYY)
-# - Interval (daily, weekly, monthly)
-# - Whether to aggregate results in single file (True/False)
-# - The number of top packages to focus on
-#
-
-import json
-import sys
-import pytz
-import re
-import os
-import glob
-import csv
-import time
-import pandas as pd
-
-from graph_tool.all import *
-from dateutil import rrule, parser
-
-
-# where results will be stored to:
-output_path = '../../data/pageranks/'
-# number of results to hold on PER DATE (aggregate may be higher):
-
-def create_pageranks(input_file, start_date, end_date, interval, aggregate_csv, top):
-  print 'Perform %s page rank for %s from %s to %s. Aggregate csv: %s. Keep %s top results.' % (interval, input_file, start_date, end_date, aggregate_csv, top)
-  
-  global output_path
-  output_path = output_path + os.path.splitext(input_file)[0].split('/')[-1]
-
-  dates = get_date_range(start_date, end_date, interval)
-
-  # load graph:
-  g = load_graph(input_file)
-  
-  # array of dataframe for pagerank results:
-  pr_frames = []
-
-  # array of dataframe for pagerank value results:
-  value_frames = []
-
-  # array of dataframe for graph stats:
-  stats_frames = []
-
-  # dataframe for in degree:
-  in_frames = []
-
-  # dataframe for in degree:
-  out_frames = []
-
-  # dataframe for in degree histogram:
-  hist_in_frames = []
-
-  # dataframe for out degree histogram:
-  hist_out_frames = []
-
-  # dataframe for total degree histogram:
-  hist_total_frames = []
-
-  for date in dates:
-    print '----------------'
-    print 'Filter graph for %s...' % (str(date))
-    
-    date_long = long(date.strftime("%s")) * 1000
-    
-    graph_filtered = GraphView(g, 
-      vfilt=lambda v: long(g.vp.created[v]) <= date_long, 
-      efilt=lambda e: long(g.ep.fromdate[e]) <= date_long and long(g.ep.todate[e]) >= date_long)
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_correlation.py

@@ -1,88 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Visualizes the pr (values) of two given results data sets
-# in one plot.
-# 
-# Input: "npm_graph_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv"
-#        "npm_graph_deps_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv"
-#        ...
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-def visualize_correlation(input_file_1, input_file_2, top=sys.maxint):
-  df = get_dfs(input_file_1, input_file_2, top)
-
-  # print some useful information:
-  print df.describe()
-  print 'Spearman correlation: %s' % df[df.columns.values[0]].corr(df[df.columns.values[1]], method='spearman')
-
-  # plot it:
-  axes = df.plot(kind='scatter', x=df.columns.values[0], y=df.columns.values[1], logy=True, logx=True)
-  #plt.scatter(df[name_1], df[name_2])
-  # axes.set_xscale('log')
-  # axes.set_yscale('log')
-  axes.get_xaxis().set_major_formatter(FormatStrFormatter('%.3f'))
-  axes.get_yaxis().set_major_formatter(FormatStrFormatter('%.3f'))
-  # axes.set_xlim(0,10000)
-  axes.set_ylim(0,0.002)
-  # axes.set_xlabel('used by applications')
-  # axes.set_ylabel('number of domains')
-  plt.tight_layout()
-  
-  # save the figure:
-  # fig = axes.get_figure()
-  # fig.savefig('apps_per_domain.pdf')
-
-  plt.show()
-
-
-def get_dfs(input_file_1, input_file_2, top=sys.maxint):
-  print '\ncorrelate %s and %s for the top %s values of the first' % (input_file_1, input_file_2, top)
-
-  frames = []
-  
-  print '  read %s...' % (input_file_1)
-  name_1 = input_file_1.split('/')[-1]
-  df_1 = pd.read_csv(input_file_1, index_col=0)
-  df_1.columns = [name_1]
-  frames.append(df_1)
-
-  print '  read %s...' % (input_file_2)
-  name_2 = input_file_2.split('/')[-1]
-  df_2 = pd.read_csv(input_file_2, index_col=0)
-  df_2.columns = [name_2]
-  frames.append(df_2)
-
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_correlation_table.py

@@ -1,77 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Visualizes a table including all Spearman rank correlation coefficients
-# between the popularity measures provided in the files list.
-# 
-
-import visualize_correlation
-
-top = 1000
-
-# pageranks:
-files = [
-  {
-    'name': 'npm downloads 1 month',
-    'path': '../../data/downloads/npm_graph_downloads_2015-08-01_2015-09-01.csv'
-  }
-  ,
-  {
-    'name': 'Bipartite pagerank values',
-    'path': '../../data/pageranks/apps_graph_bipartite_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
-  }
-  ,
-  # {
-  #   'name': 'Bipartite pagerank values DEPS only',
-  #   'path': '../../data/pageranks/apps_graph_deps_bipartite_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
-  # }
-  # ,
-  # {
-  #   'name': 'Bipartite pagerank values DEV only',
-  #   'path': '../../data/pageranks/apps_graph_dev_bipartite_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
-  # }
-  # ,
-  {
-    'name': 'npm pagerank values',
-    'path': '../../data/pageranks/npm_graph_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
-  }
-  ,
-  # {
-  #   'name': 'npm pagerank values DEPS only',
-  #   'path': '../../data/pageranks/npm_graph_deps_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
-  # }
-  # ,
-  # {
-  #   'name': 'npm pagerank values DEV only',
-  #   'path': '../../data/pageranks/npm_graph_dev_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
-  # }
-  # ,
-  # {
-  #   'name': 'npm downloads overall',
-  #   'path': '../../data/downloads/npm_graph_downloads_2010-01-01_2015-09-01.csv'
-  # }
-  # ,
-  # ,
-  # {
-  #   'name': 'npm downloads 1 week',
-  #   'path': '../../data/downloads/npm_graph_downloads_2015-08-26_2015-09-01.csv'
-  # }
-]
-
-results = []
-for idx in range(0, len(files)):
-  if idx < len(files):
-    for idx2 in range(idx+1, len(files)):
-      f1 = files[idx]['path']
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_deg_histograms.py

@@ -1,50 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Visualizes the histograms of degree values.
-# 
-# No further input required.
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-import glob
-import math
-
-files = [
-  '../../data/pageranks/apps_graph_bipartite_hist_in_daily_09-01-2015_09-01-2015.csv',
-  '../../data/pageranks/apps_graph_deps_bipartite_hist_in_daily_09-01-2015_09-01-2015.csv',
-  '../../data/pageranks/apps_graph_dev_bipartite_hist_in_daily_09-01-2015_09-01-2015.csv',
-  '../../data/pageranks/npm_graph_hist_in_daily_09-01-2015_09-01-2015.csv',
-  '../../data/pageranks/npm_graph_deps_hist_in_daily_09-01-2015_09-01-2015.csv',
-  '../../data/pageranks/npm_graph_dev_hist_in_daily_09-01-2015_09-01-2015.csv'
-]
-
-names = [
-  'apps bipartite',
-  'apps bipartite - deps. only',
-  'apps bipartite - dev deps. only',
-  'npm',
-  'npm - deps. only',
-  'npm - dev deps. only'
-]
-
-frames = []
-
-num_cols = 3
-num_rows = int(math.ceil(len(files) / num_cols))
-fig, axs = plt.subplots(nrows=num_rows, ncols=num_cols)
-
-for i, file_name in enumerate(files):
-  row = int(math.ceil(i / num_cols))
-  col = int(i - row * num_cols)
-  print 'processing %s %s...' % (i, file_name)
-  print 'row: %s, col: %s' % (row, col)
-  frame = pd.read_csv(file_name, index_col=0)
-  frame.columns = [names[i]]
-  frame.loc[0:500].plot(logy=True, ax=axs[row, col])
-
-plt.suptitle("Histograms of in degrees")
-
-plt.show()

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_dependency_dist_evolution.py

@@ -1,65 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Visualize the distribution of dependencies over time.
-# Input: a _hist_ csv, e.g., "npm_graph_hist_in_weekly_10-01-2010_09-01-2015.csv"
-# Outputfile: npm_deps_in_degree.pdf
-
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.pyplot as plt
-from matplotlib.backends.backend_pdf import PdfPages
-from matplotlib import rc
-rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
-rc('text', usetex=True)
-
-def visualize_deps_dist(input_file, pp):
-  
-  agg_min = 6
-
-  df = pd.read_csv(input_file, index_col=0, parse_dates=[0])
-  df.columns = df.columns.to_datetime()
-
-  # replace entries with percent:
-  for colKey in df:
-    df[colKey] = 100 * df[colKey] / df[colKey].sum()
-
-  # merge columns:
-  num_rows = len(df)
-  print num_rows
-  # label = '> %d' % (agg_min - 1)
-  label = '%d or more' % agg_min
-  df.loc[label] = df.ix[agg_min:num_rows,:].sum(axis=0)
-  ##df.drop(df.iloc[[0:num_rows-2],:])
-
-  df = df.ix[:agg_min].append(df.loc[label])
-#  df = df.loc[:,['2015-08-28']]
-  plt.figure()
-  plt.clf()
-  width = 7.0
-  plt.rc("figure", figsize=(width, 3.0*width/4.0))
-
-  # plot as area:
-  axes = df.T.plot(kind='area')
-  axes.set_ylim(0,100)
-  axes.set_ylabel("Percentage of Packages in npm")
-  axes.set_yticks(range(0, 110, 10))
-  
-  # plt.gcf().autofmt_xdate()
-#  plt.show()
-  plt.tight_layout()
-  pp.savefig(plt.gcf())
-
-
-if __name__=='__main__':
-  if len(sys.argv) < 3:
-      print 'usage: %s <input-data> <output-file>' % (sys.argv[0])
-      exit(-1)
-  input_file = sys.argv[1]
-  output_file = sys.argv[2]
-
-  #npm_deps_out_degree.pdf
-  with PdfPages(output_file) as pp:
-    visualize_deps_dist(input_file, pp)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_dependency_graph.py

@@ -1,78 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Visualizes the dependency graph at a certain point in time using graph-tool.
-# 
-# Input:
-# - GT Graph to visualize, e.g., "npm_graph.gt"
-# - Date for when to create the graph visualization, e.g., "01-01-2010"
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-from graph_tool.all import *
-from dateutil import parser
-
-def visualize_dep_graph(input_file, date_str):
-  # load graph:
-  g = load_graph(input_file)
-
-  # parse given date:
-  date = parser.parse(date_str)
-
-  # filter the graph for that date:
-  print 'Filter graph for %s...' % (str(date))  
-  date_long = long(date.strftime("%s")) * 1000
-  
-  graph_filtered = GraphView(g, 
-    vfilt=lambda v: long(g.vp.created[v]) <= date_long, 
-    efilt=lambda e: long(g.ep.fromdate[e]) <= date_long and long(g.ep.todate[e]) >= date_long)
-  print 'Filtered graph:'
-  print ' - Vertices: %s (original=%s)' % (graph_filtered.num_vertices(), g.num_vertices())
-  print ' - Edges: %s (original=%s)' % (graph_filtered.num_edges(), g.num_edges())
-
-  # visualize it:
-  
-  # vertex properties:
-  vprops = {
-    'shape': 'circle', # shape of the vertices
-    'size': 1,
-    'pen_width': 0.1
-  }
-
-  # vertex sizes as function of pagerank value:
-  deg = graph_tool.centrality.pagerank(graph_filtered)
-  deg.a = np.sqrt(deg.a) * 100 + 0.2 # use numpy for square root!!!
-  
-  # vertex positioning:
-  print 'determine vertex positioning...'
-  pos = graph_tool.draw.arf_layout(graph_filtered, max_iter=500)
-
-  # edge properties:
-  eprops = {
-    'color': [0.4, 0.4, 0.4, 0.4], # color in rgbt, the lower the last number, the more transparent
-    'start_marker': 'none',
-    'end_marker': 'arrow',
-    'pen_width': 0.3
-  }
-
-  # draw it using cairo:
-  print 'draw graph...'
-  graph_draw(graph_filtered,
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_devs_per_repo.py

@@ -1,73 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Script to visualize growth of packages vs number of contributors on a
-# month by month basis
-# 
-# Input: 
-# - devs_and_versions_per_repo.csv
-
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-from matplotlib.backends.backend_pdf import PdfPages
-from matplotlib.ticker import FuncFormatter
-
-
-def to_percent(y, position):
-  # Ignore the passed in position. This has the effect of scaling the default
-  # tick locations.
-  s = str(100 * y)
-
-  # The percent symbol needs escaping in latex
-  if matplotlib.rcParams['text.usetex'] is True:
-    return s + r'$\%$'
-  else:
-    return s + '%'
-
-def last_x(x, position):
-  # Ignore the passed in position. This has the effect of scaling the default
-  # tick locations.
-  if (x < 10):
-    s = str(x)
-  else:
-    s = ">=10"
-  return s
-
-def visualize_growth(input_file, pp):
-  df = pd.read_csv(input_file, index_col=0).T
-  
-  plt.figure()
-  plt.clf()
-
-#  axes=df['Developers'].hist(bins=50,normed=1,alpha=0.5,cumulative=True,lw=1.5,histtype='step')
-  axes=df['Developers'].hist(bins=10,range=(1,10), normed=1,alpha=0.5,cumulative=True,lw=1.5,histtype='step')
-  axes.set_ylabel("Percentage of Packages")
-  axes.set_xlabel("Number of Developers")
-  axes.set_ylim(0,1.05)
-  axes.set_xlim(0,11)
-  axes.set_xticks(range(0,11,1))
-
-  # Create the formatter using the function to_percent. This multiplies all the
-  # default labels by 100, making them all percentages
-  yformatter = FuncFormatter(to_percent)
-  ##trimming the bins to that it doesn't obscure patterns in the lower ends of X range
-  xformatter = FuncFormatter(last_x)
-  
-  # Set the formatter
-  plt.gca().yaxis.set_major_formatter(yformatter)
-  plt.gca().xaxis.set_major_formatter(xformatter)
-#  plt.show()
-
-  pp.savefig(plt.gcf())
-
-if __name__=='__main__':
-  if len(sys.argv) < 2:
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_highest_ranked.py

@@ -1,166 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Script to identify and visualize packages whose pagerank 
-# has been the highest over time.
-# 
-# Input: "npm_graph_pr_top_180000_weekly_10-01-2010_09-01-2015.csv"
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.dates as dates
-from scipy.stats import gmean
-from matplotlib import rc
-rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
-rc('text', usetex=True)
-
-def visualize_highest_ranked(input_file):
-  
-  num_packages = 5
-
-  df = pd.read_csv(input_file, index_col=0, parse_dates=0)
-  df.columns = df.columns.to_datetime()
-
-  # reverse rank sum:
-  # visualize_reverse_rank(df, num_packages)
-
-  # Average rank:
-  # visualzie_avg_rank(df, num_packages)
-
-  # Geometric mean rank:
-  # visualize_geo_rank(df, num_packages)
-
-  # Relative rank (from 0 - 1):
-  # visualize_relative_rank(df, num_packages)
-
-  # Select packages:
-  # packages = ['underscore', 'lodash', 'lazy.js', 'sugar', 'valentine', 'wu']
-  # visualize_select_packages(df, packages)
-
-  # Average rank per year:
-  visualize_avg_rank_per_year(df, num_packages)
-
-
-def visualize_reverse_rank(df, num_packages):
-  df['overall_score'] = df.T.apply(lambda x: 180000 - x).sum()
-  df.sort_values('overall_score', ascending=True, inplace=True)
-  df.drop('overall_score', axis=1, inplace=True)
-  ax = df[:num_packages].plot()
-  plt.tight_layout()
-  plt.gca().invert_yaxis()
-  plt.show()
-
-
-def visualize_select_packages(df, packages):
-  df_select = df.ix[packages]
-  df_select.columns = df_select.columns.to_datetime()
-
-  width = 5.0
-  plt.rc("figure", figsize=(width, 3.0*width/4.0))
-
-  axes = df_select.T.plot()
-  plt.tight_layout()
-  axes.set_ylim(-150, 10000)
-  plt.yticks(get_y_ticks(axes.get_ylim()[1], 10))
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_highest_variance.py

@@ -1,84 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Script to identify and visualize packages whose pagerank 
-# has the highest variance over time.
-# 
-# Input: npm_graph_pr_top_180000_weekly_10-01-2010_09-01-2015.csv
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-import math
-
-
-def get_rank_changes(df):
-  results = {}
-  for index, row in df.iterrows():
-    last_rank = 0
-    num_movements = 0
-    for rank in row:
-      if math.isnan(rank):
-        continue
-      difference = abs(last_rank - rank)
-      num_movements += difference
-      last_rank = rank
-    results[index] = num_movements
-  return pd.DataFrame(results, index=['num_movements']).T
-
-
-def visualize_strongest_movers(input_file):
-  
-  num_movers = 5
-
-  df = pd.read_csv(input_file, index_col=0, parse_dates=0)[0:180000]
-
-  movement_df = get_rank_changes(df)
-
-  df = pd.concat([df, movement_df], axis=1)
-
-  df.sort_values('num_movements', ascending=False, inplace=True)
-
-  print df
-
-  df.drop('num_movements', 1, inplace=True)
-
-  axes = df[:num_movers].T.plot()
-  plt.gca().invert_yaxis()
-
-  plt.show()
-
-  # df['variance'] = df.T.var()
-
-  # df.sort_values('variance', ascending=False, inplace=True)
-
-  # print df
-
-  # get indexes of packages with highest variance:
-  # top_mover_indexes = df.var().sort_values(ascending=False)[:num_movers].index
-
-  # print top_mover_indexes
-
-  # print df[top_mover_indexes]
-
-  # create dataframe of packages and fill empty values:
-  # top_movers_df = df[top_mover_indexes].drop(df.index[-1:]).fillna(len(df) + 1)
-
-  # print top_movers_df
-
-  # create plot:
-  # axes = top_movers_df.plot()
-  # # axes.set_ylim(0,100)
-  # for line in axes.lines:
-  #   line.set_linewidth(2)
-  # plt.gca().invert_yaxis()
-  # plt.show()
-
-
-if __name__=='__main__':
-  if len(sys.argv) < 1:
-      print 'usage: %s <input-data>' % (sys.argv[0])
-      exit(-1)
-  input_file = sys.argv[1]
-  visualize_strongest_movers(input_file)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_package_growth.py

@@ -1,58 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Script to visualize growth of the npm ecosystem w.r.t. number
-# of packages and number of dependencies between them.
-# 
-# Input: 
-# - Statistics on package and dependency numbers:
-#     "npm_graph_stats_weekly_10-01-2010_09-01-2015.csv"
-# - Statistics on package and dependency numbers clean (i.e., without inactive packages):
-#     "repos_newer_180_days_at_date.csv"
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib import rc
-rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
-rc('text', usetex=True)
-
-def visualize_growth(input_file, input_clean):
-  df = pd.read_csv(input_file, index_col=0, parse_dates=0).T
-
-  df.rename(columns={'num_vertices': 'Packages', 'num_edges': 'Dependencies'}, inplace=True)
-
-  df_clean = pd.read_csv(input_clean, index_col=0, parse_dates=0)
-  df_clean.columns = ['Packages newer than 180 days']
-
-  df = df[['Packages', 'Dependencies']].join(df_clean)
-
-  df['Dependencies per Package'] = pd.DataFrame(df['Dependencies'] / df['Packages'])
-
-  width = 5.0
-  plt.rc("figure", figsize=(width, 3.0*width/4.0))
-
-  # plot left:
-  ax = df[['Packages', 'Dependencies']].plot(lw=2.0, legend=False)
-  ax.set_ylabel('No. of Packages / Dependencies')
-  ax.xaxis.grid(True)
-
-
-  # plot rights:
-  ax2 = df['Dependencies per Package'].plot(secondary_y=True, lw=2.0, legend=False)
-  ax2.set_ylim(0,10)
-  ax2.set_ylabel('Dependencies per Package')
-
-  plt.tight_layout()
-  plt.grid()
-  plt.show()
-
-
-if __name__=='__main__':
-  if len(sys.argv) < 3:
-      print 'usage: %s <input-data> <input-clean-growth>' % (sys.argv[0])
-      exit(-1)
-  input_file = sys.argv[1]
-  input_clean = sys.argv[2]
-  visualize_growth(input_file, input_clean)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_popularity_relations.py

@@ -1,171 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Visualizes the relationships (differences in ranks) of different popularity measures.
-# Considers only ranks that are NOT random. E.g., filters packages that have all the same
-# minimum pagerank value as they don't have any incoming relations.
-# 
-# It does also re-rank the packages after filtering:
-#   Consider two rankings A and B regarding a set of 150 entries.
-#   A contains 100 valid ranks, 1 - 100.
-#   B contains  50 valid ranks, 1 -  50.
-#   Not having a valid value means that the entry performs indistinguishably BAD.
-#   A comparison of A and B results in 40 comparisons where entries have valid values in A and B.
-#   Theory 1:
-#     Re-rank values regarding A and B from 1 - 40.
-#     This way, one compares the relative rankings between A and B.
-#     Neglects all the packages in either A or B that have no valid value in the other ranking.
-#   Theory 2:
-#     Compare values of A and B without re-ranking, resulting for example in A = 2, B = 125.
-#     This way, one compares the absolute ranks of A and B.
-#     The resulting distribution may be skewed, for example, ranks may be comparatively lower in A.
-#     But doesn't that account for the fact, that there are entries that rank higher in A and comparatively 
-#     low in B (= they don't even have a valid rank)?
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-from matplotlib import rc
-rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
-rc('text', usetex=True)
-
-files = [
-  {
-    'name': 'GitHub',
-    'path': '../../data/pageranks/apps_graph_bipartite_in-deg_daily_09-01-2015_09-01-2015.csv'
-  }
-  ,
-  {
-    'name': 'npm',
-    'path': '../../data/pageranks/npm_graph_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
-  }
-  ,
-  {
-    'name': 'downloads',
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_pr_value_histograms.py

@@ -1,50 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Visualizes the histograms of pagerank values of different datasets
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-import glob
-
-files = [
-  '../../data/pageranks/apps_graph_bipartite_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv',
-  '../../data/pageranks/apps_graph_deps_bipartite_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv',
-  '../../data/pageranks/apps_graph_dev_bipartite_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv',
-  '../../data/pageranks/npm_graph_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv',
-  '../../data/pageranks/npm_graph_deps_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv',
-  '../../data/pageranks/npm_graph_dev_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
-]
-
-names = [
-  'apps bipartite',
-  'apps bipartite - dependencies only',
-  'apps bipartite - dev dependencies only',
-  'npm',
-  'npm - dependencies only',
-  'npm - dev dependencies only'
-]
-
-frames = []
-for i, file_name in enumerate(files):
-  print 'processing %s %s...' % (i, file_name)
-  frame = pd.read_csv(file_name, index_col=0)
-  frame.columns = ['pagerank value ' + names[i]]
-  frames.append(frame)
-
-
-df = pd.concat(frames, axis=1)
-print df
-
-df.hist(bins=100, log=True)\
-
-plt.suptitle("Histograms of pagerank values")
-
-plt.show()
-
-  # print df
-  # axes = df.plot(kind='hist', logy=True, bins=200, title="test")
-  # axes.set_ylim(0,10**7)
-  # plt.show()

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_top_keywords.py

@@ -1,55 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Determine and prints keywords of packages that are comparatively the
-# highest ranking in npm as compared to GitHub and vice versa.
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
-
-
-def get_top_keyword_count_df(df, column_name, top, reverse):
-  df.sort_values(column_name, inplace=True, ascending=(not reverse))
-  keyword_counts = {}
-  for index, row in df[:top].iterrows():
-    keyword_list = str(row['keywords']).split(';')
-    for name in keyword_list:
-      if name not in keyword_counts:
-        keyword_counts[name] = 1
-      else:
-        keyword_counts[name] += 1
-  new_column_name = column_name
-  if reverse:
-    new_column_name = '%s - %s' % (column_name.split(' - ')[1], column_name.split(' - ')[0])
-  new_df = pd.DataFrame(keyword_counts, index=['count_' + new_column_name]).T
-  return new_df.sort_values('count_' + new_column_name, ascending=False)
-
-# read DataFrame with all popularity measures and their rank differences:
-df = pd.read_csv('../../data/popularity_measures.csv', index_col=0)
-
-# count the keywords in the 1000 packages the most better on npm than GitHub:
-print '\n\nKeyword count for packages better on npm than on GitHub:'
-better_npm_df = get_top_keyword_count_df(df, 'npm - GitHub', 1000, False)
-print better_npm_df[:20]
-
-# count the keywords in the 1000 packages the most better on GitHub than npm:
-print '\n\nKeyword count for packages better on GitHub than on npm:'
-better_github_df = get_top_keyword_count_df(df, 'npm - GitHub', 1000, True)
-print better_github_df[:20]
-
-# find keywords with the highest different count between npm- and GitHub-strong packages:
-new_df = pd.concat([better_npm_df, better_github_df], axis=1) 
-new_df['diff'] = new_df['count_npm - GitHub'] - new_df['count_GitHub - npm']
-
-# print keywords that predominantly appear in npm-strong packages:
-print '\n\nKeywords most unilaterally used by npm-strong pacakges:'
-new_df.sort_values('diff', ascending=False, inplace=True)
-print new_df[:15]
-
-# print keywords that predominantly appear in GitHub-strong packages:
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_top_losers.py

@@ -1,102 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Visualizes the top losing packages.
-#
-# Input: "npm_graph_pr_top_180000_weekly_10-01-2010_09-01-2015.csv"
-#
-import sys
-import math
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.stats import gmean
-
-def visualize_highest_lossers(input_file):
-  
-  num_packages = 5
-
-  df = pd.read_csv(input_file, index_col=0, parse_dates=0)
-  df.columns = df.columns.to_datetime()
-
-  visualize_loosers_top_1000(df, num_packages)
-
-def get_max_decline(df):
-  results = {}
-  for index, row in df.iterrows():
-    highest_rank = len(df)
-    lowest_subsequent_rank = 0
-    for rank in row:
-      if math.isnan(rank):
-        continue
-      if rank < highest_rank:
-        highest_rank = rank
-        lowest_subsequent_rank = 0
-      elif rank >= lowest_subsequent_rank and rank < len(df):
-        lowest_subsequent_rank = rank
-      else:
-        continue
-    max_decline = lowest_subsequent_rank - highest_rank
-    # print '%s: highest=%s, lowest=%s, max-decline=%s' % (index, highest_rank, lowest_subsequent_rank, max_decline)
-    results[index] = max_decline
-  return pd.DataFrame(results, index=['num_declines']).T
-
-
-def get_rank_declines(df):
-  results = {}
-  for index, row in df.iterrows():
-    last_rank = 0
-    num_declines = 0
-    for rank in row:
-      if math.isnan(rank):
-        continue
-      if rank < 1000:
-        if last_rank < rank: 
-          num_declines += rank - last_rank
-        last_rank = rank
-    results[index] = num_declines
-  return pd.DataFrame(results, index=['num_declines']).T
-
-
-def visualize_loosers_top_1000(df, num_packages):
-  # sort by geometric mean:
-  def geo_mean(x):
-    return gmean(list(x.dropna()))
-  df['overall_score'] = df.T.apply(geo_mean) # df.T.mean()
-  df.sort_values('overall_score', ascending=True, inplace=True)
-  df.drop('overall_score', axis=1, inplace=True)
-
-  # Consider top 1000 from hereon:
-  df = df[:1000]
-
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_top_newcomers.py

@@ -1,69 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Visualizes the number of packages entering the top N pageranks for the first time
-# over time.
-# 
-# Input: "npm_graph_pr_top_180000_weekly_10-01-2010_09-01-2015.csv"
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from matplotlib import rc
-rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
-rc('text', usetex=True)
-
-
-def visualize_top_newcomers(input_file):
-  # list of top values to consider:
-  top_list = [10, 100, 250]
-
-  # read CSV:
-  df = pd.read_csv(input_file, index_col=0, parse_dates=0)
-  df.columns = df.columns.to_datetime()
-
-  # start at 2011-06-01:
-  df = df.ix[:,35:]
-
-  frames = []
-  for top in top_list:
-    frame = get_newcomers(df, top)
-    frames.append(frame)
-
-  df_results = pd.concat(frames, axis=1)
-
-  # print absolute numbers of packages entering per year:
-  print df_results.resample('A', how='sum')
-
-  width = 6.0
-  plt.rc("figure", figsize=(width, 3.0*width/4.0))
-
-  ax = df_results.resample('1M', how='mean').plot(style=['-', '-', '-'], lw=1.5) # resample('4M', how='mean')
-  ax.set_ylim(0, 10)
-  ax.set_ylabel('No. of Packages')
-  plt.tight_layout()
-  plt.grid()
-  plt.show()
-
-
-def get_newcomers(df, top):
-  seen = []
-  results = {}
-  for column in df:
-    ranks = df[column].sort_values()
-    new_packages = 0
-    for package_name, value in ranks[:top].iteritems():
-      if package_name not in seen:
-        new_packages += 1
-        seen.append(package_name)
-    results[column] = new_packages
-  return pd.DataFrame(results, index=['Entering top %s for the first time' % str(top)]).T
-
-
-if __name__=='__main__':
-  if len(sys.argv) < 1:
-      print 'usage: %s <input-data>' % (sys.argv[0])
-      exit(-1)
-  input_file = sys.argv[1]
-  visualize_top_newcomers(input_file)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/graph/visualize_versions_per_repo.py

@@ -1,72 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Script to visualize growth of packages vs number of contributors on a
-# month by month basis
-# 
-# Input: 
-# - devs_and_versions_per_repo.csv
-
-#
-import sys
-import pandas as pd
-import numpy as np
-import matplotlib
-import matplotlib.pyplot as plt
-from matplotlib.backends.backend_pdf import PdfPages
-from matplotlib.ticker import FuncFormatter
-
-
-def to_percent(y, position):
-  # Ignore the passed in position. This has the effect of scaling the default
-  # tick locations.
-  s = str(100 * y)
-
-  # The percent symbol needs escaping in latex
-  if matplotlib.rcParams['text.usetex'] is True:
-    return s + r'$\%$'
-  else:
-    return s + '%'
-
-def last_x(x, position):
-  # Ignore the passed in position. This has the effect of scaling the default
-  # tick locations.
-  if (x < 100):
-    s = str(x)
-  else:
-    s = ">=100"
-  return s
-
-def visualize_growth(input_file, pp):
-  df = pd.read_csv(input_file, index_col=0).T
-  
-  plt.figure()
-  plt.clf()
-
-  axes=df['Versions'].hist(bins=100,range=(1,100), normed=1,alpha=0.5,cumulative=True,lw=1.5,histtype='step')
-  axes.set_ylabel("Percentage of Packages")
-  axes.set_xlabel("Number of Versions")
-  axes.set_ylim(0,1.05)
-  axes.set_xlim(0,110)
-  axes.set_xticks(range(0,110,10))
-
-  # Create the formatter using the function to_percent. This multiplies all the
-  # default labels by 100, making them all percentages
-  yformatter = FuncFormatter(to_percent)
-  ##trimming the bins to that it doesn't obscure patterns in the lower ends of X range
-  xformatter = FuncFormatter(last_x)
-  
-  # Set the formatter
-  plt.gca().yaxis.set_major_formatter(yformatter)
-  plt.gca().xaxis.set_major_formatter(xformatter)
-#  plt.show()
-
-  pp.savefig(plt.gcf())
-
-if __name__=='__main__':
-  if len(sys.argv) < 2:
-      print 'usage: %s devs_versions_per_repo_hist.csv' % (sys.argv[0])
-      exit(-1)
-  input_file = sys.argv[1]
-  with PdfPages('versions_per_repo_hist.pdf') as pp:
-    visualize_growth(input_file, pp)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/src/version-resolver/version-resolver.js

@@ -1,31 +1,0 @@
-/**
- * Script that reads version queries and candidates in JSON from standard input
- * and produces the best version for the query as output.
- *
- * Input looks like this (one JSON object per line):
- * { "vq" : "~0.8.0", "vs" : [ "0.0.1", "0.1.1", "0.8.0", "0.8.1" ] }
- *
- * Output looks like this (one string per line):
- * 0.8.1
- *
- * Note: requires 'semver' package, as specified in the package.json (use 'npm install')
- */
-var readline = require('readline')
-var semver = require('semver')
-
-var rl = readline.createInterface({
-  input: process.stdin,
-  output: process.stdout,
-  terminal: false
-})
-
-rl.on('line', function (line) {
-  var data = JSON.parse(line)
-  var query = data.vq
-  var candidates = data.vs
-
-  var maxSatisfying = semver.maxSatisfying(candidates, query)
-
-  // console.log('Query=%s, Candidates=%s, maxSatisfying=%s', query, candidates.join(', '), maxSatisfying)
-  console.log(maxSatisfying)
-})

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/data-express-adoption.py

@@ -1,75 +1,0 @@
-import re
-import sys
-import numpy
-
-from db import DB
-
-if __name__ == "__main__":
-    output_file = sys.argv[0].replace(".py", ".dat")
-
-    def semver(v):
-        m = re.match("""([0-9]*)\.([0-9]*)\.([0-9]*)""", v)
-        major = int(m.group(1))
-        minor = int(m.group(2))
-        patch = int(m.group(3))
-        return (major, minor, patch)
-
-    def triple_to_float(major, minor, patch):
-        K = 0.5
-        m = float(major)
-        M = float(minor)
-        p = float(patch)
-
-        M_p = M + 1.0 - (1.0 / (K*p + 1.0))
-        m_M_p = m + 1.0 - (1.0 / (K*M_p + 1.0))
-        
-        # THIS IS SPECIFIC TO EXPRESS
-        return m + M / 22.0 + p / (13.0 * 22.0)
-
-        return m_M_p
-
-    db = DB()
-
-    db.cursor.execute("""
-SELECT
-    `rd`.`version`,
-    `rd`.`released` AS `released`,
-    UNIX_TIMESTAMP(`rd`.`released`) AS `ts`,
-    `rd`.`resolvable_dependents` AS `resolvable`,
-    `ad`.`resolved_dependents` AS `resolved`,
-    `ad`.`resolved_dependents` / `rd`.`resolvable_dependents` AS `fraction`
-FROM
-    `resolvable_dependents` `rd`
-        LEFT OUTER JOIN 
-    `resolved_dependents` `ad`
-        ON
-    `rd`.`version` = `ad`.`version`
-WHERE
-    `rd`.`package_id` = `ad`.`package_id` AND
-    `rd`.`version` = `ad`.`version` AND
-    `rd`.`released` > "2012-10-15"
-ORDER BY
-    `released`
-;
-    """)
-
-    all_triples = []
-    all_major   = []
-    all_minor   = []
-    all_patch   = []
-
-    triple_counts = {}
-
-    print "Writing to %s..." % (output_file)
-    with open(output_file, "w") as fp:
-        fp.write("major,minor,patch,linearized,ts,frac\n")
-
-        for row in db.cursor.fetchall():
-            version = row[0]
-            ts      = row[2]
-            frac    = row[5]
-            triple  = semver(version)
-            (major,minor,patch) = triple
-            linearized = triple_to_float(major, minor, patch)
-
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/data-time-to-version.py

@@ -1,75 +1,0 @@
-import re
-import sys
-
-from db import DB
-
-if __name__ == "__main__":
-    output_file = sys.argv[0].replace(".py", ".dat")
-
-    def semver(v):
-        m = re.match("""([0-9]*)\.([0-9]*)\.([0-9]*)""", v)
-        major = int(m.group(1))
-        minor = int(m.group(2))
-        patch = int(m.group(3))
-        return (major, minor, patch)
-
-    def triple_to_float(major, minor, patch):
-        K = 0.5
-        m = float(major)
-        M = float(minor)
-        p = float(patch)
-
-        M_p = M + 1.0 - (1.0 / (K*p + 1.0))
-        m_M_p = m + 1.0 - (1.0 / (K*M_p + 1.0))
-
-        return m_M_p
-
-    db = DB()
-
-    print "Running query..."
-    db.cursor.execute("""
-        SELECT
-            `version`,
-            COUNT(*) AS `count`,
-            AVG(`time_diff`) AS `avg_time_to_version`,
-            MIN(`time_diff`) AS `min_time_to_version`,
-            MAX(`time_diff`) AS `max_time_to_version`
-        FROM (
-            SELECT
-                `pv`.`package_id`,
-                `pv`.`version`,
-                `pv`.`released`,
-                `sub`.`first_released`,
-                TIMESTAMPDIFF(SECOND, `sub`.`first_released`, `pv`.`released`) AS `time_diff`
-            FROM
-                `package_versions` `pv`
-                INNER JOIN
-                (
-                    SELECT
-                        `package_id`,
-                        MIN(`released`) AS `first_released`
-                    FROM
-                        `package_versions`
-                    GROUP BY
-                        `package_id`
-                ) `sub`
-                ON `pv`.`package_id` = `sub`.`package_id`
-        ) `xxx`
-        WHERE
-            `version` REGEXP "^[0-9]+\\.[0-9]+\\.[0-9]+$"
-        GROUP BY
-            `version`;
-    """)
-
-    print "Writing to %s..." % (output_file)
-    with open(output_file, "w") as fp:
-        fp.write("major,minor,patch,linearized,count,avg_time,min_time,max_time\n")
-
-        for row in db.cursor.fetchall():
-            (version, count, avg_time, min_time, max_time) = row
-            (major,minor,patch) = semver(version)
-            linearized = triple_to_float(major,minor,patch)
-
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/data-version-stairway.py

@@ -1,76 +1,0 @@
-import itertools
-import re
-import sys
-
-from db import DB
-
-if __name__ == "__main__":
-    try:
-        package = sys.argv[1]
-    except:
-        print "You need to provide a package name."
-        sys.exit(1)
-
-    output_file = sys.argv[0].replace(".py", "-%s.dat" % package)
-
-    def semver(v):
-        m = re.match("""([0-9]*)\.([0-9]*)\.([0-9]*)""", v)
-        major = int(m.group(1))
-        minor = int(m.group(2))
-        patch = int(m.group(3))
-        return (major, minor, patch)
-
-    def triple_to_float(major, minor, patch):
-        K = 0.5
-        m = float(major)
-        M = float(minor)
-        p = float(patch)
-
-        M_p = M + 1.0 - (1.0 / (K*p + 1.0))
-        m_M_p = m + 1.0 - (1.0 / (K*M_p + 1.0))
-
-        return m_M_p
-
-    db = DB()
-
-    print "Running query..."
-    db.cursor.execute("""
-        SELECT
-            `packages`.`name` AS `package_name`,
-            `package_versions`.`version` AS `version`,
-            UNIX_TIMESTAMP(`package_versions`.`released`) AS `released`
-        FROM
-            `packages` JOIN `package_versions` ON `packages`.`id` = `package_versions`.`package_id`
-        WHERE
-            `packages`.`name`=%s AND
-            `version` REGEXP "^[0-9]+\\.[0-9]+\\.[0-9]+$" AND
-            `released` >= "2010-10-01" AND `released` < "2015-09-01"
-        ORDER BY
-            `released` ASC
-    """, package)
-
-    all_rows = []
-    current_max = -1;
-    for row in db.cursor.fetchall():
-        (_, version, released) = row
-        (major,minor,patch) = semver(version)
-        linearized = triple_to_float(major,minor,patch)
-
-        if linearized <= current_max:
-            continue
-
-        current_max = linearized
-
-        all_rows.append((major,minor,patch,linearized,released))
-
-    max_rows = []
-    for (ts, rows) in itertools.groupby(all_rows, lambda t: t[4]):
-        rows = sorted(list(rows), key=lambda t: -t[3])
-        max_rows.append(rows[0]) 
-
-    print "Writing to %s..." % (output_file)
-    with open(output_file, "w") as fp:
-        fp.write("major,minor,patch,linearized,released\n")
-        for row in max_rows:
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/data-versions-distribution.py

@@ -1,66 +1,0 @@
-import re
-import sys
-import numpy
-
-from db import DB
-
-if __name__ == "__main__":
-    output_file = sys.argv[0].replace(".py", ".dat")
-
-    def semver(v):
-        m = re.match("""([0-9]*)\.([0-9]*)\.([0-9]*)""", v)
-        major = int(m.group(1))
-        minor = int(m.group(2))
-        patch = int(m.group(3))
-        return (major, minor, patch)
-
-    def triple_to_float(major, minor, patch):
-        K = 0.5
-        m = float(major)
-        M = float(minor)
-        p = float(patch)
-
-        M_p = M + 1.0 - (1.0 / (K*p + 1.0))
-        m_M_p = m + 1.0 - (1.0 / (K*M_p + 1.0))
-
-        return m_M_p
-
-    db = DB()
-
-    all_semver = db.cursor.execute("""
-        SELECT
-            `version`, COUNT(*) AS `how_many` 
-        FROM
-            `package_versions`
-        WHERE
-            `version` REGEXP "^[0-9]+\\.[0-9]+\\.[0-9]+$"
-        GROUP BY
-            `version`
-        ORDER BY
-            `how_many` DESC
-        ;
-    """)
-
-    all_triples = []
-    all_major   = []
-    all_minor   = []
-    all_patch   = []
-
-    triple_counts = {}
-
-    for row in db.cursor.fetchall():
-        version = row[0]
-        count   = int(row[1])
-
-        triple = semver(version)
-
-        before = triple_counts.get(triple, 0)
-        triple_counts[triple] = before + count
-
-    print "Writing to %s..." % (output_file)
-    with open(output_file, "w") as fp:
-        fp.write("major,minor,patch,linearized,count\n")
-        for triple,count in triple_counts.iteritems():
-            (major, minor, patch) = triple
-            linearized = triple_to_float(major, minor, patch)
-            fp.write("%d, %d, %d, %f, %d\n" % (major, minor, patch, linearized, count))

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/datasources.py

@@ -1,17 +1,0 @@
-class DataSources:
-    # The expected format is a JSON array, where each entry is a record
-    # with at least the following field: r["value"]["name"].
-    #
-    # Expected size is ~300M
-    npm_packages = "../data/2015-09-22_npm_skim.json"
-
-    # The expected format is a text file where each line contains a JSON object.
-    # Each object is expected to have the following fields:
-    #   - obj["name"]
-    #   - obj["time"]
-    # Expected size is ~2G if full of ~300M if "curated"
-    # npm_full = "../data/just_express.txt"
-    npm_full = "../data/2015-09-22_npm_repos_curated.txt"
-
-    # The expected format is a directory containing many JSON files.
-    project_history_dir = "../github-projects/histories"

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/db.py

@@ -1,10 +1,0 @@
-import sys
-import MySQLdb
-
-class DB:
-    def __init__(self):
-        self.db = MySQLdb.connect(host="localhost", user="npmversions", passwd="password", db="npmversions")
-        self.cursor = self.db.cursor()
-
-    def commit(self):
-        self.db.commit()

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/dbstats.py

@@ -1,24 +1,0 @@
-#!/usr/bin/env python
-from db import DB
-
-if __name__ == "__main__":
-    db = DB()
-
-    query = """
-        SELECT 
-            `table_name`,
-            ROUND(((data_length + index_length) / 1024 / 1024), 2)
-            FROM information_schema.TABLES where `table_schema`="npmversions"
-            ORDER BY (data_length + index_length) DESC;
-     """
-
-    db.cursor.execute(query)
-    print "%-40s %10s" % ("Table name", "Size")
-    print "%-40s-%10s" % ("-" * 40, "-" * 10)
-    for row in db.cursor.fetchall():
-        if row[1] is None:
-            size = "%10s" % "----"
-        else:
-            size = "%7.2f MB" % row[1]
-
-        print "%-40s %10s" % (row[0], size)

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/githubhistory.py

@@ -1,77 +1,0 @@
-import json
-import re
-import dateutil.parser
-
-class GitHubHistory:
-    def __init__(self, json_file):
-        with open(json_file) as fp:
-            self.data = json.load(fp)
-
-        m = re.match("""^github:([^:]+):([^:]+)$""", self.data["_id"])
-
-        self.user = m.group(1)
-        self.repo = m.group(2)
-
-    def get_intervals(self):
-        file_creation_time = dateutil.parser.parse(self.data["creation_time"])
-
-        commits_to_time = map(lambda p : (p[0], dateutil.parser.parse(p[1])), list(self.data["time"].iteritems()))
-        commits_to_time.sort(key=lambda p: p[1], reverse=True)
-
-        # This is the "end of the universe" date for this particular history file.
-        prev_date = file_creation_time
-
-        bounds = {}
-        devBounds = {}
-
-        for (commit,ts) in commits_to_time:
-            pkg_data = self.data["versions"][commit]
-
-            deps = pkg_data.get("dependencies", {})
-            devDeps = pkg_data.get("devDependencies", {})
-
-            for (dep,query) in deps.iteritems():
-                pair = (dep,query)
-                if not pair in bounds:
-                    bounds[pair] = (ts,prev_date)
-                else:
-                    before = bounds[pair]
-                    bounds[pair] = (ts,before[1])
-
-            for (dep,query) in devDeps.iteritems():
-                pair = (dep,query)
-                if not pair in devBounds:
-                    devBounds[pair] = (ts,prev_date)
-                else:
-                    before = devBounds[pair]
-                    devBounds[pair] = (ts,before[1])
-
-            prev_date = ts
-
-        final_object = {}
-        # final_object["_id"] = self.data["_id"]
-        # final_object["creation_time"] = self.data["creation_time"]
-
-        intervals = []
-        devIntervals = []
-
-        for ((d,v),(s,e)) in bounds.iteritems():
-            intervals.append({
-                "package" : d,
-                "version" : v,
-                "from"    : s.isoformat(),
-                "to"      : e.isoformat()
-            })
-
-        for ((d,v),(s,e)) in devBounds.iteritems():
-            devIntervals.append({
-                "package" : d,
-                "version" : v,
-                "from"    : s.isoformat(),
-                "to"      : e.isoformat()
-            })
-
-        final_object["dependencies"] = intervals
-        final_object["devDependencies"] = devIntervals
-
-        return final_object

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/loader.py

@@ -1,125 +1,0 @@
-from datetime import datetime
-from datetime import tzinfo
-import dateutil.parser
-import glob
-import json
-import pytz
-import re
-
-from db import DB
-from datasources import DataSources
-
-class Loader:
-    @classmethod
-    def dt2ts(cls, dt):
-        if dt.tzinfo is not None:
-            return long((dt - datetime(1970, 1, 1, tzinfo=pytz.utc)).total_seconds())
-        else:
-            return long((dt - datetime(1970, 1, 1)).total_seconds())
-        
-    @classmethod
-    def string2ts(cls, d):
-        dt = dateutil.parser.parse(d)
-        return cls.dt2ts(dt)
-
-    @classmethod
-    def load_package_names(cls, db):
-        print "Loading package names..."
-        print "  - loading JSON representation"
-        with open(DataSources.npm_packages) as fp:
-            data = json.load(fp)
-
-        print "  - computing unique set"
-        all_names = set([])
-        for obj in data:
-            name = obj.get("value", {}).get("name", None)
-            if isinstance(name, basestring):
-                all_names.add(name)
-
-        print "  - inserting into database"
-        for name in all_names:
-            db.cursor.execute("INSERT INTO `packages` (`name`) VALUES(%s)", name)
-        db.commit()
-
-    @classmethod
-    def load_package_versions(cls, db):
-        print "Loading package versions..."
-        print "  - inserting from JSON lines to DB"
-        with open(DataSources.npm_full) as fp:
-            for line in fp:
-                data = json.loads(line)
-                name = data.get("name", None)
-                if not isinstance(name, basestring):
-                    continue
-
-                try:
-                    versions = data.get("time", {})
-                    if not isinstance(versions, dict):
-                        continue
-
-                    for v,d in versions.iteritems():
-                        try:
-                            ts = cls.utc2ts(d)
-                        except:
-                            print "  - couldn't parse/convert date value for %s-%s: %s" % (name, v, d)
-                            continue
-
-                        db.cursor.execute("INSERT INTO `package_versions` (`package_id`, `version`, `released`) SELECT `id`, %s, FROM_UNIXTIME(%s) FROM `packages` WHERE `packages`.`name`=%s", (v, ts, name))
-
-                    db.commit()
-                except Exception, e:
-                    print "  - error when processing %s: %s" % (name, str(e))
-
-        print "  - cleanup"
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/multiresolver-import.py

@@ -1,33 +1,0 @@
-import json
-import fileinput
-
-from db import DB
-
-def store_row(db, row):
-    package_name   = row["p"]
-    version_query  = row["vq"]
-    result_version = row["vr"]
-    started        = row["from"]
-    ended          = row["to"]
-
-    db.cursor.execute("""
-        INSERT INTO `version_query_resolutions`
-            (`package_id`, `version_query`, `result_version`, `started`, `ended`)
-        SELECT
-            `packages`.`id`, %s, `pv`.`id`, FROM_UNIXTIME(%s), FROM_UNIXTIME(%s)
-        FROM
-            `packages`, `package_versions` AS `pv`
-        WHERE
-            `packages`.`name`=%s AND
-            `packages`.`id`=`pv`.`package_id` AND
-            `pv`.`version`=%s;
-    """, (version_query, started, ended, package_name, result_version))
-
-if __name__ == "__main__":
-    db = DB()
-
-    for line in fileinput.input():
-        data = json.loads(line)
-        store_row(db, data)
-
-    db.commit()

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/multiresolver-post.py

@@ -1,50 +1,0 @@
-import json
-import subprocess
-
-import fileinput
-from loader import Loader
-
-def emit_range(package_name, query_string, result, from_ts, to_ts):
-    print json.dumps({
-        "p"    : package_name,
-        "vq"   : query_string,
-        "vr"   : result,
-        "from" : from_ts,
-        "to"   : to_ts
-    })
-
-if __name__ == "__main__":
-    prev_package = None
-    prev_query   = None
-    prev_result  = None
-    start_ts     = -1
-    end_ts       = -1
-
-    emitted = 0
-
-    for line in fileinput.input():
-        data = json.loads(line)
-
-        package = data["p"]
-        query   = data["vq"]
-        result  = data["vr"]
-        ts      = data["at"]
-
-        if package == prev_package and query == prev_query and result == prev_result:
-            # When all it the same, we just skip over, but we widen the range.
-            end_ts = ts
-            continue
-
-        if prev_package is not None and prev_result is not None:
-            emit_range(prev_package, prev_query, prev_result, start_ts, end_ts)
-            if prev_package != package:
-                emitted += 1
-                pass
-
-        prev_package = package
-        prev_query   = query
-        prev_result  = result
-        start_ts     = ts
-        end_ts       = ts
-
-        

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/multiresolver-pre.py

@@ -1,141 +1,0 @@
-import json
-import subprocess
-
-from loader import Loader
-
-# This script is designed to feed into version-resolver.js, then into *-post.py.
-class MultiResolverPre:
-    @classmethod
-    def resolve_all_queries(cls, db, package_name):
-        (intervals, latest_ts) = cls.query_intervals(db, package_name)
-
-        if latest_ts is None:
-            return
-
-        releases = cls.versions_earlier_than(db, package_name, latest_ts)
-
-        if releases:
-            (versions, release_dates) = zip(*releases)
-
-            for (qs, start_ts, end_ts) in intervals:
-                cls.resolve(package_name, qs, start_ts, end_ts, versions, release_dates)
-
-    @classmethod
-    def versions_earlier_than(cls, db, package_name, ts):
-        versions = []
-
-        db.cursor.execute("""
-            SELECT
-                `version`, `released`
-            FROM
-                `packages`,
-                `package_versions`
-            WHERE
-                `packages`.`id`=`package_versions`.`package_id` AND
-                `packages`.`name`=%s
-            ORDER BY
-                `released` ASC;""", package_name)
-
-        for (version, released) in db.cursor.fetchall():
-            versions.append((version, Loader.dt2ts(released)))
-
-        return versions
-
-    @classmethod
-    def query_intervals(cls, db, package_name):
-        
-        # This will get you all the query strings ever used for that package,
-        # together with first-seen and last-seen dates.
-        db.cursor.execute("""
-            SELECT
-                `packages`.`id` AS `package_id`,
-                `packages`.`name` AS `package_name`,
-                `deps`.`version_query`,
-                MIN(`deps`.`started`) AS `first_started`,
-                MAX(`deps`.`ended`) AS `last_ended`
-            FROM
-                `packages`,
-                `project_explicit_dependencies` AS `deps`
-            WHERE
-                `packages`.`id`=`deps`.`package_id` AND
-                `packages`.`name`=%s
-            GROUP BY
-                `packages`.`id`,
-                `deps`.`version_query`;""", package_name)
-
-        stored_rows = []
-        latest_ts = -1
-
-        # Each row is a specific query string
-        for row in db.cursor.fetchall():
-            (pkg_id, pkg_name, qs, first_started, last_ended) = row
-            first_ts = Loader.dt2ts(first_started)
-            last_ts  = Loader.dt2ts(last_ended)
[…]

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/plot-number-frequencies.py

@@ -1,45 +1,0 @@
-import os
-import sys
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-
-if __name__ == "__main__":
-    input_file = sys.argv[0].replace("plot-", "data-").replace(".py", ".dat")
-
-    frame = pd.read_csv(input_file)
-
-    print frame
-
-    width = 5.0
-    
-    bar_width = 0.31
-
-    plt.rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
-    plt.rc("text", usetex=True)
-    plt.rc("figure", figsize=(width, 3.0*width/4.0))
-    plt.rc("axes", linewidth=0.5)
-
-    plt.bar(frame["number"] - 1.5 * bar_width, frame["major"], bar_width, color="blue")
-    plt.bar(frame["number"] - 0.5 * bar_width, frame["minor"], bar_width, color="red")
-    plt.bar(frame["number"] + 0.5 * bar_width, frame["patch"], bar_width, color="green")
-
-    axes = plt.gca()
-    axes.set_xlabel("Number")
-    axes.set_xlim([ -2 * bar_width, 9 + 2 * bar_width ])
-    plt.xticks(range(0,10), range(0,10))
-    # axes.set_ylim([ 0.5, 5.5 ])
-
-    axes.set_ylabel("Frequency")
-    axes.set_yscale('log')
-
-    axes.yaxis.grid(True, which='major')
-
-    # plt.xticks(range(0,11))
-
-    plt.tight_layout()
-
-    # plt.show()
-
-    plot_file = sys.argv[0].replace("plot-", "").replace(".py", ".pdf") 
-    plt.savefig(plot_file, format="pdf")

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/plot-time-to-version.py

@@ -1,55 +1,0 @@
-import os
-import sys
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-
-def color_from_mp(mp):
-    (m,p) = mp
-    m = int(m)
-    p = int(p)
-    if m == 0 and p == 0:
-        return "blue"
-    elif p == 0:
-        return "red"
-    else:
-        return "green"
-
-if __name__ == "__main__":
-    input_file = sys.argv[0].replace("plot-", "data-").replace(".py", ".dat")
-
-    frame = pd.read_csv(input_file)
-
-    width = 5.0
-
-    plt.rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
-    plt.rc("text", usetex=True)
-    plt.rc("figure", figsize=(width, 3.5*width/4.0))
-    plt.rc("axes", linewidth=0.5)
-
-    versions = frame["linearized"]
-    months   = frame["avg_time"] / 60 / 60 / 24 / 30.5
-
-    color_in = zip(list(frame["minor"]), list(frame["patch"]))
-    colors = map(color_from_mp, color_in)
-
-    plt.scatter(versions, months, marker='+', c=colors)
-
-    axes = plt.gca()
-
-    axes.set_xlabel("Version number")
-    axes.set_xlim([ 0, 7 ])
-    plt.xticks(range(0,8), map(lambda n: "%d.0.0" % n, range(0,8)), rotation=45, ha='right')
-
-    axes.set_ylabel("Months")
-    axes.set_ylim([ 0, 13 ])
-    axes.xaxis.grid(True, which='major')
-
-    # plt.xticks(range(0,11))
-
-    plt.tight_layout()
-
-    # plt.show()
-
-    plot_file = sys.argv[0].replace("plot-", "").replace(".py", ".pdf") 
-    plt.savefig(plot_file, format="pdf")

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/plot-version-stairway.py

@@ -1,60 +1,0 @@
-import os
-import sys
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-
-if __name__ == "__main__":
-    def triple_to_float(major, minor, patch):
-        K = 0.5
-        m = float(major)
-        M = float(minor)
-        p = float(patch)
-
-        M_p = M + 1.0 - (1.0 / (K*p + 1.0))
-        m_M_p = m + 1.0 - (1.0 / (K*M_p + 1.0))
-
-        return m_M_p
-
-    try:
-        package = sys.argv[1]
-    except:
-        print "You need to provide a package name."
-        sys.exit(1)
-
-    input_file = sys.argv[0].replace("plot-", "data-").replace(".py", "-%s.dat" % package)
-
-    frame = pd.read_csv(input_file)
-
-    width = 5.0
-
-    plt.rc("text", usetex=True)
-    plt.rc("figure", figsize=(width, 3.0*width/4.0))
-    plt.rc("axes", linewidth=0.5)
-
-    versions = frame["linearized"]
-    dates    = frame["released"] / 60 / 60 / 24 / 30.5
-
-    plt.scatter(dates, versions, marker='+')
-
-    axes = plt.gca()
-    # axes.set_xlim([ 0, 7 ])
-    axes.set_ylim([ 0.5, 5.5 ])
-
-    # Preparing the ticks.
-    ytick_pos = []
-    ytick_labels = []
-    for major in range(0, 5):
-        for minor in [ 2, 4, 6, 8, 10 ]:
-            ytick_pos.append(triple_to_float(major, minor, 0))
-            ytick_labels.append("%d.%d.0" % (major, minor))
-    plt.yticks(ytick_pos, ytick_labels)
-
-    axes.yaxis.grid(True, which='major')
-
-    # plt.xticks(range(0,11))
-
-    plt.show()
-
-    # plot_file = sys.argv[0].replace("plot-", "").replace(".py", ".pdf") 
-    # plt.savefig(plot_file, format="pdf")

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/plot-versions-distribution.py

@@ -1,55 +1,0 @@
-import os
-import sys
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-
-def color_from_mp(mp):
-    (m,p) = mp
-    m = int(m)
-    p = int(p)
-    if m == 0 and p == 0:
-        return "blue"
-    elif p == 0:
-        return "red"
-    else:
-        return "green"
-
-if __name__ == "__main__":
-    input_file = sys.argv[0].replace("plot-", "data-").replace(".py", ".dat")
-
-    frame = pd.read_csv(input_file)
-
-    width = 5.0
-
-    plt.rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
-    plt.rc("text", usetex=True)
-    plt.rc("figure", figsize=(width, 3.5*width/4.0))
-    plt.rc("axes", linewidth=0.5)
-
-    color_in = zip(list(frame["minor"]), list(frame["patch"]))
-    colors = map(color_from_mp, color_in)
-
-    axes = plt.gca()
-
-    axes.xaxis.grid(True, which='major')
-    axes.yaxis.grid(True, which='major')
-
-    axes.set_xlabel("Version number")
-    axes.set_xlim([ 0, 10])
-    plt.xticks(range(0,11), map(lambda n: "%d.0.0" % n, range(0,11)), rotation=45, ha='right')
-
-    axes.set_ylabel("Frequency")
-    axes.set_ylim([ 1, 100000 ])
-    axes.set_yscale('log')
-
-    plt.scatter(frame["linearized"], frame["count"], marker='+') #, c=colors)
-
-
-
-    plt.tight_layout()
-
-    # plt.show()
-
-    plot_file = sys.argv[0].replace("plot-", "").replace(".py", ".pdf") 
-    plt.savefig(plot_file, format="pdf")

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/schema.py

@@ -1,28 +1,0 @@
-#!/usr/bin/env python
-import sys
-
-from db import DB
-
-if __name__ == "__main__":
-    if len(sys.argv) < 3 or (sys.argv[2] != "up" and sys.argv[2] != "down"):
-        print("Usage: %s id {up,down}" % sys.argv[0])
-        sys.exit(1)
-
-    which = sys.argv[1]
-
-    if sys.argv[2] == "down":
-        src = "./sql/%s-down.sql" % which
-    else:
-        src = "./sql/%s-up.sql" % which
-
-    print "Executing script: %s" % src
-
-    with open(src) as fp:
-        contents = fp.read()
-
-    print ""
-    print contents
-
-    db = DB()
-    db.cursor.execute(contents)
-

### 2019-04-12 resources/original_scripts/npm-analysis-source-code/version-histories/version-resolver.js

@@ -1,40 +1,0 @@
-var readline = require('readline')
-var semver = require('semver')
-
-var rl = readline.createInterface({
-  input: process.stdin,
-  output: process.stdout,
-  terminal: false
-})
-
-var processed = 0
-
-rl.on('line', function (line) {
-    var data = JSON.parse(line);
-    var query = data.vq;
-    var candidates = data.vs;
-
-    if (query == "latest") {
-        query = "*";
-    }
-
-    try {
-        var validCandidates = candidates.filter(function (c) {
-            return semver.valid(c) != null;
-        });
-
-        var maxSatisfying = semver.maxSatisfying(validCandidates, query);
-        data["vr"] = maxSatisfying;
-    } catch (e) {
-        data["vr"] = null;
-    }
-
-    delete data.vs;
-
-    console.log(JSON.stringify(data));
-
-    processed += 1;
-    if(processed % 1000 == 0) {
-        process.stderr.write(".");
-    }
-})

### 2019-04-12 resources/original_scripts/src/data/get_npm_download_stats.py

@@ -1,0 +1,41 @@
+#!/usr/bin/python3.4
+import asyncio  
+import aiohttp
+import json
+import sys
+
+
+base_url = 'https://api.npmjs.org/downloads/point/last-month/'
+downloads = {}
+failed=0
+max_tasks = 50
+
+def fetch_count(package_list, start, end, session):
+    for i in range(start, end):
+        package = package_list[i]
+        response = yield from session.get(base_url+package)
+        if response.status == 200:
+            downloads[package] = yield from response.json()
+        else:
+            failed += 1
+
+def main(npm_packages):
+    tasks = []
+    jobs_per_task = int(len(npm_packages) / max_tasks)
+    for start in range(0, len(npm_packages), jobs_per_task):
+        conn = aiohttp.TCPConnector(verify_ssl=False)
+        session = aiohttp.ClientSession(connector=conn)
+        end = start + jobs_per_task
+        if end > len(npm_packages):
+            end = len(npm_packages)
+        tasks.append(asyncio.Task(fetch_count(npm_packages, start, end, session)))
+    yield from asyncio.gather(*tasks)
+
+if __name__ == '__main__':
+    kv = json.load(open('npm_stripped.json'))
+    npm_packages = list(kv.keys())
+    loop = asyncio.get_event_loop()
+    loop.run_until_complete(main(npm_packages))
+    with open('npm_downloads_last_month.json','w') as outfile:
+        json.dump(downloads, outfile)
+    print(failed,'requests failed')

### 2019-04-12 resources/original_scripts/src/data/get_npm_downloads.js

@@ -1,0 +1,98 @@
+/**
+ * Loads npm download data per package in two steps:
+ * 1.) Get npm skim
+ * 2.) Get, per package found in the skim, the package download metadata
+ *
+ * No further input required.
+ */
+
+var fs = require('fs')
+var JSONStream = require('JSONStream')
+var Transform = require('stream').Transform
+var request = require('request')
+var async = require('async')
+var moment = require('moment')
+
+// kick things off:
+loadRepoList()
+
+// config:
+var concurrency = 40
+
+function loadRepoList () {
+  var readCount = 0
+  var repoList = []
+
+  // set up streams:
+  var parser = JSONStream.parse('rows.*')
+  var extractor = new Transform({objectMode: true})
+  extractor._transform = function (dataObj, encoding, done) {
+    readCount++
+    if (readCount % 10000 === 0) console.log('%s repositories assessed...', readCount)
+
+    repoList.push(dataObj.id)
+
+    this.push(dataObj)
+    done()
+  }
+  var stringifyer = JSONStream.stringify('[\n', '\n,\n', '\n]\n', '\t')
+  var outputPath = '../../data/' + moment().format('YYYY-MM-DD') + '_npm_skim.json'
+  var wstream = fs.createWriteStream(outputPath, {encoding: 'utf8'})
+
+  // start streams:
+  request
+    .get('https://skimdb.npmjs.com/registry/_design/scratch/_view/byField')
+    .pipe(parser)
+    .pipe(extractor)
+    .pipe(stringifyer)
+    .pipe(wstream)
+      .on('error', function (err) {
+        console.log('Error: ' + err)
+      })
+      .on('finish', function () {
+        console.log('loaded list of %s repositories; will consider %s in the following', readCount, repoList.length)
+        console.log('written results to "%s"', outputPath)
+        loadData(repoList)
+      })
+}
+
+function loadData (repoList) {
+  var loadCount = 0
+  var successCount = 0
+  var errorCount = 0
+  var outputPath = '../../data/' + moment().format('YYYY-MM-DD') + '_npm_downloads-2010_01_01-2019_04_01.txt'
+
+  async.eachLimit(repoList, concurrency, function (id, callback) {
+    if (loadCount % 1000 === 0) console.log('%s loaded...', loadCount)
+    request({
+      method: 'GET',
+      uri: 'https://api.npmjs.org/downloads/range/2010-01-01:2019-04-01/' + id,
+      json: true
+    }, function (err, res, body) {
+      loadCount++
[…]

### 2019-04-12 resources/original_scripts/src/data/get_npm_metadata.js

@@ -1,0 +1,105 @@
+/**
+ * Loads complete set on npm metadata in two steps:
+ * 1.) Get npm skim
+ * 2.) Get package-specific metadata for every package contained in the skim
+ *
+ * No further input required.
+ */
+
+var fs = require('fs')
+var JSONStream = require('JSONStream')
+var Transform = require('stream').Transform
+var request = require('request')
+var async = require('async')
+var moment = require('moment')
+
+// kick things off:
+//loadRepoList()
+
+fs.readFile('../../data/missing_names_skim.json', 'utf8', function(err, data) {
+  if (err) throw err; // we'll not consider error handling for now
+  var missingRepoList = JSON.parse(data)
+  loadData(missingRepoList)
+});
+
+
+// config:
+var concurrency = 25
+
+function loadRepoList () {
+  var readCount = 0
+  var repoList = []
+
+  // set up streams:
+  var parser = JSONStream.parse('rows.*')
+  var extractor = new Transform({objectMode: true})
+  extractor._transform = function (dataObj, encoding, done) {
+    readCount++
+    if (readCount % 10000 === 0) console.log('%s repositories assessed...', readCount)
+
+    repoList.push(dataObj.id)
+
+    this.push(dataObj)
+    done()
+  }
+  var stringifyer = JSONStream.stringify('[\n', '\n,\n', '\n]\n', '\t')
+  var outputPath = '../../data/' + moment().format('YYYY-MM-DD') + '_npm_skim.json'
+  var wstream = fs.createWriteStream(outputPath, {encoding: 'utf8'})
+
+  // start streams:
+  request
+    .get('https://skimdb.npmjs.com/registry/_design/scratch/_view/byField')
+    .pipe(parser)
+    .pipe(extractor)
+    .pipe(stringifyer)
+    .pipe(wstream)
+    .on('error', function (err) {
+      console.log('Error: ' + err)
+    })
+    .on('finish', function () {
+      console.log('loaded list of %s repositories; will consider %s in the following', readCount, repoList.length)
+      console.log('written results to "%s"', outputPath)
+      loadData(repoList)
+    })
+}
+
+function loadData (repoList) {
+  var loadCount = 0
+  var successCount = 0
+  var errorCount = 0
+  var outputPath = '../../data/' + moment().format('YYYY-MM-DD') + '_npm_repos.txt'
+
+  async.eachLimit(repoList, concurrency, function (id, callback) {
+    if (loadCount % 1000 === 0) console.log('%s loaded...', loadCount)
[…]

### 2019-04-12 resources/original_scripts/src/graph-versioned/create_gt_graphs_versioned.py

@@ -1,0 +1,9 @@
+#!/usr/bin/env python
+import glob
+import create_graph as g
+
+if __name__=='__main__':
+  fake_graph_list = glob.glob('../../data/json-graphs/*.json')
+  for fake_graph_path in fake_graph_list:
+    print fake_graph_path
+    g.create_graph(fake_graph_path)

### 2019-04-12 resources/original_scripts/src/graph-versioned/create_json_graph_versioned.js

@@ -1,0 +1,356 @@
+var fs = require('fs')
+var byline = require('byline')
+var moment = require('moment')
+var semver = require('semver')
+
+var inputData
+
+;(function () {
+  function createSnapshot (inputPath, outputPath, dateString, simple, callback) {
+    console.log('create snapshot from %s at date %s. simple: %s', inputPath, dateString, simple)
+
+    var date = moment(dateString, 'YYYY-MM-DD')
+    var graph = {}
+
+    var lineCount = 0
+    var nodeCount = 0
+    var start = new Date().getTime()
+
+    if (!inputData) {
+      console.log('read input data from file...')
+      var stream = fs.createReadStream(inputPath)
+      stream = byline.createStream(stream)
+      inputData = []
+
+      stream.on('data', function (line) {
+        lineCount++
+        if (lineCount % 10000 === 0) console.log('%s lines...', lineCount)
+        try {
+          inputData.push(line)
+          var repo = JSON.parse(line)
+          var oldVersions
+          if (simple) {
+            oldVersions = getOldVersionsSimple(repo, date)
+          } else {
+            oldVersions = getOldVersions(repo, date)
+          }
+          if (oldVersions) {
+            nodeCount++
+            graph[repo.name] = oldVersions
+          }
+        } catch (err) {
+          console.log(err)
+        }
+      })
+
+      stream.on('finish', function () {
+        var end = new Date().getTime()
+        var time = (end - start) / 1000
+        console.log('created %s nodes from %s lines', nodeCount, lineCount)
+        console.log(' - %s seconds to create nodes', time)
+        concretizeDependencies(graph, outputPath, date, simple, callback)
+      })
+    } else {
+      console.log('use input data from memory...')
+      for (var i = inputData.length - 1; i >= 0; i--) {
+        lineCount++
+        if (lineCount % 10000 === 0) console.log('%s lines...', lineCount)
+        var repo = JSON.parse(inputData[i])
+        var oldVersions
+        if (simple) {
+          oldVersions = getOldVersionsSimple(repo, date)
+        } else {
+          oldVersions = getOldVersions(repo, date)
+        }
+        if (oldVersions) {
+          nodeCount++
+          graph[repo.name] = oldVersions
+        }
+      }
+      var end = new Date().getTime()
+      var time = (end - start) / 1000
+      console.log('created %s nodes from %s lines', nodeCount, lineCount)
+      console.log(' - %s seconds to create nodes', time)
[…]

### 2019-04-12 resources/original_scripts/src/graph-versioned/create_json_graphs_versioned.js

@@ -1,0 +1,67 @@
+var moment = require('moment')
+require('moment-range')
+//var graphSnapshot = require('./graph-snapshot')
+var graphSnapshot = require('./create_json_graph_versioned')
+var async = require('async')
+var fs = require('fs')
+
+;(function () {
+  function getDateRange (start, end) {
+    var results = []
+    var startDate = moment(start, 'YYYY-MM-DD')
+    var endDate = moment(end, 'YYYY-MM-DD')
+    // var range = date.range('month')
+    var range = moment.range(startDate, endDate)
+    range.by('months', function (moment) {
+      results.push(moment.format('YYYY-MM-DD'))
+    })
+    return results
+  }
+
+  if (!module.parent) {
+    if (typeof process.argv[2] !== 'undefined' ||
+      typeof process.argv[3] !== 'undefined' ||
+      typeof process.argv[4] !== 'undefined' ||
+      typeof process.argv[5] !== 'undefined') {
+      // get params:
+      var inputPath = process.argv[2]
+      var start = process.argv[3]
+      var end = process.argv[4]
+      var simple = (process.argv[5] === 'true')
+
+      var range = getDateRange(start, end)
+      console.log(range)
+
+      var results = []
+      async.eachSeries(range, function (date, callback) {
+        var outputPath = '../../data/json-graphs-versioned/' + date + '_npm_graph_versioned.json'
+        if (simple) {
+          outputPath = '../../data/json-graphs/' + date + '_npm_graph.json'
+        }
+        graphSnapshot.createSnapshot(inputPath, outputPath, date, simple, function (err, result) {
+          if (err) {
+            callback(err)
+          } else {
+            results.push(result)
+            callback()
+          }
+        })
+      }, function done () {
+        console.log('Finished')
+        var outputFile = '../../data/report_' + start + '_' + end + '_versioned.json'
+        if (simple) {
+          outputFile = '../../data/report_' + start + '_' + end + '.json'
+        }
+        fs.writeFile(outputFile, JSON.stringify(results, null, 2), function (err) {
+          if (err) {
+            console.log(err)
+          } else {
+            console.log('saved results to %s', outputFile)
+          }
+        })
+      })
+    } else {
+      console.log('usage: node %s <input-path> <start-date> <end-date> <simple?>', process.argv[1])
+    }
+  }
+})()

### 2019-04-12 resources/original_scripts/src/graph-versioned/pageranks.py

@@ -1,0 +1,57 @@
+import json
+import sys
+import pytz
+import re
+import os
+import glob
+import csv
+
+from graph_tool.all import *
+
+def create_pageranks():
+  # obtain list of all graph files (*.gt):
+  graph_file_list = glob.glob('../../data/graphs/*.gt')
+
+  # determine page rank and store results as CSVs:
+  for file_name in graph_file_list:
+    print 'perform page rank for %s' % file_name
+    
+    ranking = []
+
+    g = load_graph(file_name)
+    pr = graph_tool.centrality.pagerank(g)
+    
+    for v in g.vertices():
+      # print '%s (%s) has pagerank: %s' % (graph.vp.name[v], graph.vp.version[v], pr[v])
+      ranking.append({
+        'name_and_version': g.vp.name[v] + '_' + g.vp.version[v],
+        'name': g.vp.name[v],
+        'version': g.vp.version[v],
+        'pr_value': pr[v]
+        })
+
+    # sort results by rank:
+    ranking = sorted(ranking, key=lambda k: k['pr_value'], reverse=True)
+
+    for i in range(0, len(ranking)):
+      ranking[i]['rank'] = i + 1
+
+    # store results under the right date:
+    date = re.search('[0-9][0-9][0-9][0-9]-[0-9][0-9]-[0-9][0-9]', file_name).group(0) # os.path.splitext(file_name)[0]
+    output_file = '../../data/pageranks/%s_pagerank.csv' % (date)
+    
+    keys = ranking[0].keys()
+    with open(output_file, 'wb') as of:
+      dict_writer = csv.DictWriter(of, keys)
+      dict_writer.writeheader()
+      dict_writer.writerows(ranking)
+    print 'written results of %s to %s' % (file_name, output_file)
+
+  # outfile = 'top_%s_results.json' % str(top)
+  # with open(outfile, 'w') as outfile:
+  #   json.dump(overall_results, outfile, sort_keys=True, indent=4)
+  # print 'results written to %s' % outfile
+
+
+if __name__=='__main__':
+  g = create_pageranks()

### 2019-04-12 resources/original_scripts/src/graph-versioned/plot_libraries.py

@@ -1,0 +1,28 @@
+#!/usr/bin/env python
+import pandas as pd
+import numpy as np
+import re
+import matplotlib.pyplot as plt
+
+df = pd.read_csv('../../data/all_pageranks_simple.csv', index_col=0, parse_dates=0)
+
+print df['underscore']
+
+
+#repos = ['express', 'connect', 'async']
+# repos = ['backbone', 'ember', 'backbone.marionette', 'knockout', 'dojo', 'angular', 'polymer']
+repos = ['lodash', 'underscore', 'sugar']
+# repos = ['request', 'superagent', 'restler']
+
+
+ax = df[repos[0]].plot(title='Utility lib wars', logy=True)
+
+for i in range(1, len(repos)):
+  df[repos[i]].plot()
+
+ax.legend(repos, loc='lower center')
+# reverse y-axis:
+plt.gca().invert_yaxis()
+plt.gca().set_ybound(lower=0, upper=None)
+
+plt.show()

### 2019-04-12 resources/original_scripts/src/graph/calc_accumulative_top_packages.py

@@ -1,0 +1,58 @@
+#!/usr/bin/env python
+
+#
+# Calculate the number of new packages entering the top N over time.
+# 
+# Input: 
+# - package ranking data over time, e.g., npm_graph_pr_top_100_weekly_...
+# - N = the number of top packages to consider
+#
+import sys
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+def calc_accumulative_top(input_file, top_list):
+  frames = []
+
+  df = pd.read_csv(input_file, index_col=0, parse_dates=False)
+
+  # list to store all packages already seen:
+  result = {}
+
+  for top in top_list:
+    seen_list = []
+    # iterate columns:
+    for i in range(len(df.columns)):
+      col = df.ix[:,i]
+
+      print '%s: seen %s packages in the top %s' % (col.name, len(seen_list), top)
+      if col.name not in result:
+        result[col.name] = []
+      result[col.name].append(len(seen_list))
+
+      # iterate entries in column:
+      for index, value in col.iteritems():
+        if not np.isnan(value) and value <= top:
+          if index not in seen_list:
+            seen_list.append(index)
+          # print index + ' ' + str(value)
+
+  df_acc = pd.DataFrame(result).T
+  df_acc.columns = top_list
+
+  axes = df_acc.plot()
+  # axes.set_xlabel('date')
+  # axes.set_ylabel('absolute pagerank changes since one week ago')
+  plt.show()
+
+
+if __name__=='__main__':
+  if len(sys.argv) < 3:
+    print 'usage: %s [input_file, e.g., npm_graph_pr_top_100_weekly_...] [top numbers, e.g., 10 50 100...]' % (sys.argv[0])
+    exit(-1)
+  input_file = sys.argv[1]
+  top_list = map(lambda a : int(a), sys.argv[2:])
+  calc_accumulative_top(input_file, top_list)

### 2019-04-12 resources/original_scripts/src/graph/calc_clean_growth.py

@@ -1,0 +1,112 @@
+#!/usr/bin/env python
+
+#
+# Script to calculate package growth over time considering only active packages.
+# 
+# Input: 
+# - "npm_version_dates.json"
+#    (which is an array of JSON objects describing each package in the following way:
+#        {
+#          "name": "...",
+#          "time": {
+#            "created": "2013-05-18T14:04:50.640Z",
+#            "0.0.1": "2013-05-18T14:04:53.742Z",
+#            ...
+#          }
+#        }
+#    )
+# - Number of days in which activity must have occurred for a package to be considered.
+#
+import sys
+import json
+import time
+import datetime
+import pytz
+import pandas as pd
+
+from dateutil import rrule, parser
+
+
+def visualize_growth_clean(input_file, delta_value):
+  # create a date range:
+  dates = get_date_range('10-01-2010', '09-01-2015', 'weekly')
+  # localize:
+  dates = map(lambda x: pytz.UTC.localize(x), dates)
+
+  repos_at_date = {}
+  for date in dates:
+    repos_at_date[str(date)] = 0  
+  count = 0
+
+  delta = datetime.timedelta(days=delta_value)
+
+  with open(input_file) as data_file:    
+    data = json.load(data_file)
+
+  print 'loaded data.'
+
+  for repo in data:
+    count  += 1
+    if count % 200 == 0:
+      print '%s - %s' % (count, repo['name'])
+
+    # iterate dates:
+    if 'time' in repo:
+      for date in dates:
+        date_str = str(date)
+        latest_version_date = pytz.UTC.localize(datetime.datetime(2010, 1, 1))
+        latest_version = None
+
+        for key, version in enumerate(repo['time']):
+          version_date = parser.parse(repo['time'][version])
+          try:
+            if version_date < date and latest_version_date < version_date:
+              latest_version_date = version_date
+              latest_version = version
+          except TypeError:
+            pass
+        if latest_version is not None and (date - latest_version_date) < delta:
+          # print 'Latest version of "%s" (%s) is NEWER than %s at %s' % (repo['name'], latest_version, delta_value, date_str)
+          repos_at_date[date_str] += 1
+        else:
+          # print 'Latest version of "%s" (%s) is OLDER than %s at %s' % (repo['name'], latest_version, delta_value, date_str)
+          pass
+
[…]

### 2019-04-12 resources/original_scripts/src/graph/calc_rank_differences.py

@@ -1,0 +1,72 @@
+#!/usr/bin/env python
+
+#
+# Calculate the differences in rank of packages in the two given 
+# files and sort results correspondingly.
+# 
+# Input (examples):
+#   npm_graph_pr_top_1800000_weekly_10-01-2010_09-01-2015.csv
+#   npm_graph_downloads-ranks_2015-09-01.csv
+#   
+#
+import sys
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+def calc_rank_differences(input_file_1, input_file_2):
+  df = get_dfs(input_file_1, input_file_2)
+
+  col1 = df.ix[:,0]
+  name1 = ' '.join(col1.name.split('_')[:4])
+  col2 = df.ix[:,1]
+  name2 = ' '.join(col2.name.split('_')[:4])
+  sub = col1 - col2
+  subname = name1 + ' - ' + name2
+  sub.name = subname
+
+  df = pd.DataFrame(sub).sort_values(subname, ascending=False)
+
+  df = df.dropna()
+
+  print '\nDoing much better in "%s" than in "%s":' % (name1, name2)
+  for index, row in df.tail(10).sort_values(subname).abs().iterrows():
+    print '%30s: difference=%s %30s=%s %30s=%s' % (index, row[subname], name1, col1[index], name2, col2[index])
+  # print df.tail(10).sort_values(subname).abs()
+
+  print '\nDoing much better in "%s" than in "%s":' % (name2, name1)
+  for index, row in df.head(10).iterrows():
+    print '%30s: difference=%s %30s=%s %30s=%s' % (index, row[subname], name1, col1[index], name2, col2[index])
+
+  # print df
+
+
+def get_dfs(input_file_1, input_file_2):
+  frames = []
+
+  print '  read %s...' % (input_file_1)
+  name_1 = input_file_1.split('/')[-1]
+  df_1 = pd.read_csv(input_file_1, index_col=0)
+  df_1.columns = [name_1]
+  frames.append(df_1)
+
+  print '  read %s...' % (input_file_2)
+  name_2 = input_file_2.split('/')[-1]
+  df_2 = pd.read_csv(input_file_2, index_col=0)
+  print df_2
+  df_2.columns = [name_2]
+  frames.append(df_2)
+
+  print '  concatenate...'
[…]

### 2019-04-12 resources/original_scripts/src/graph/calc_rank_differences_complex.py

@@ -1,0 +1,55 @@
+#!/usr/bin/env python
+
+#
+# Calculate the differences in rank of packages in multiple given 
+# files and sort results correspondingly.
+#
+import sys
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+files = [
+  {
+    'name': 'GitHub',
+    'path': '../../data/pageranks/apps_graph_bipartite_pr_top_300000_daily_09-01-2015_09-01-2015.csv'
+  }
+  ,
+  {
+    'name': 'npm',
+    'path': '../../data/pageranks/npm_graph_pr_top_300000_daily_09-01-2015_09-01-2015.csv'
+  }
+  ,
+  {
+    'name': 'downloads',
+    'path': '../../data/downloads/npm_graph_download-ranks_2015-08-01_2015-09-01.csv'
+  }
+]
+
+
+frames = []
+for o in files:
+  df = pd.read_csv(o['path'], index_col=0)
+  df.columns = [o['name']]
+  frames.append(df)
+
+df = pd.concat(frames, axis=1)
+df = df.dropna()
+# df['min'] = pd.DataFrame([df['npm pagerank'], df['Bipartite pagerank']]).min()
+
+df = df.sort_values('downloads', ascending=False)
+
+df['diff'] = df['downloads'] - df['npm']
+
+df = df.sort_values('diff', ascending=False)
+
+print df
+
+# df = ((df + df.shift(-1)) / 300)[::300]
+# print df
+
+axes = df['diff'].plot()
+axes.set_xlabel('packages')
+axes.set_ylabel('difference between GitHub and npm pageranks')
+plt.show()

### 2019-04-12 resources/original_scripts/src/graph/calc_select_package_popularity.py

@@ -1,0 +1,78 @@
+#!/usr/bin/env python
+
+#
+# Prints the popularity of selected packages in different measures.
+#
+import sys
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+files = [
+  {
+    'name': 'GitHub',
+    'path': '../../data/pageranks/apps_graph_bipartite_in-deg_daily_09-01-2015_09-01-2015.csv'
+  }
+  ,
+  {
+    'name': 'npm',
+    'path': '../../data/pageranks/npm_graph_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
+  }
+  ,
+  {
+    'name': 'downloads',
+    'path': '../../data/downloads/npm_graph_download-ranks_2015-08-01_2015-09-01.csv'
+  }
+]
+
+def calc_popularity(package):
+  frames = []
+
+  # get filtered GitHub dependencies:
+  frames.append(get_filtered_github(files[0]['path']))
+
+  # get filtered pageranks:
+  frames.append(get_filtered_pageranks(files[1]['path']))
+
+  # get filtered downloads: (NO processing needed, all have downloads)
+  df_downloads = pd.read_csv(files[2]['path'], index_col=0)
+  df_downloads.columns = ['downloads']
+  frames.append(df_downloads)
+
+  # create overall dataframe:
+  df = pd.concat(frames, axis=1)
+
+  print df.ix[package]
+
+
+def get_filtered_pageranks(file_name):
+  df = pd.read_csv(file_name, index_col=0)
+  # filter min values:
+  min_pagerank_value = df.min()[0]
+  df_filtered = df[(df['2015-09-01'] != min_pagerank_value)]
+  
+  # create ranking:
+  df_filtered.sort_values('2015-09-01', ascending=False, inplace=True)
+  df_filtered['npm pagerank'] = range(1, len(df_filtered) + 1)
+
+  return pd.DataFrame(df_filtered['npm pagerank'])
+
+
+def get_filtered_github(file_name):
+  df = pd.read_csv(file_name, index_col=0)
+  # filter min values:
+  df_filtered = df[(df['2015-09-01'] != 0)]
+
+  # create ranking:
+  df_filtered.sort_values('2015-09-01', ascending=False, inplace=True)
[…]

### 2019-04-12 resources/original_scripts/src/graph/calc_updates_everymonth.py

@@ -1,0 +1,113 @@
+#!/usr/bin/env python
+
+#
+# Script to calculate packages that were updated in a month, binned by month
+## Multiple updates in the same month are not considered here
+# 
+# Input: 
+# - "npm_version_dates.json"
+#    (which is an array of JSON objects describing each package in the following way:
+#        {
+#          "name": "...",
+#          "time": {
+#            "created": "2013-05-18T14:04:50.640Z",
+#            "0.0.1": "2013-05-18T14:04:53.742Z",
+#            ...
+#          }
+#        }
+#    )
+#
+import sys
+import json
+import time
+import datetime
+import pytz
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+
+from dateutil import rrule, parser
+
+
+def visualize_updates(input_file):
+  # create a date range:
+  dates = get_date_range('10-01-2010', '04-01-2019', 'monthly')
+  # localize:
+  dates = map(lambda x: pytz.UTC.localize(x), dates)
+
+  start_date = dates[0]
+  end_date = dates[-1]
+  dates.pop()
+
+  repos_at_date = {}
+  for date in dates:
+    repos_at_date[date.strftime('%Y-%m-%d')] = 0
+  count = 0
+  errors = 0
+
+  with open(input_file) as data_file:    
+    data = json.load(data_file)
+
+  print 'loaded data.'
+
+  for repo in data:
+    count  += 1
+    if count % 200 == 0:
+      print '%s - %s' % (count, repo['name'])
+
+    updates = {}
+    # iterate dates:
+    if 'time' in repo:
+      for version in repo['time']:
+        if version.startswith('created'):
+          continue
+        try:
+          version_date = parser.parse(repo['time'][version])
+          if (version_date > start_date) and (version_date < end_date):
+            date_str = version_date.strftime('%Y-%m-01')
+            updates[date_str] = 1
+        except TypeError:
+          print(version_date)
+          errors += 1
+      for d in updates:
+        repos_at_date[d] += 1
+
+  print 'Had %d errors' % (errors)
+  print 'Total num repos in buckets is %d against total processed %d' % (sum(repos_at_date.values()), count)
+
+  df = pd.DataFrame(repos_at_date, index=[0]).T
+  df.columns = ['updatedrepos']
+  print df
+  df.to_csv('npm_updates_per_month.csv')
+
+
+#
[…]

### 2019-04-12 resources/original_scripts/src/graph/create-gt-graph.py

@@ -1,0 +1,127 @@
+#!/usr/bin/env python
+
+#
+# Creates a .gt graph (graph-tool) from given JSON graph.
+# The JSON graph is expected to be a JSON object of the following form:
+# 
+# {
+#   "package_a": {
+#     "creationDate": 1359595266159,
+#     "deps": {
+#       "package_b": [
+#         {
+#           "from": 1359595266159,
+#           "to": 1500000000000
+#         },
+#         ...
+#       ]
+#     },
+#     ...
+#   },
+#   ...
+# }
+#
+
+import json
+import sys
+import pytz
+import re
+import os
+
+from graph_tool.all import *
+
+
+def create_graph(input_file, do_bipartite):
+  print '--------------'
+  fake_graph = load_data(input_file)
+  print 'loaded graph with %s nodes' % (len(fake_graph))
+  graph = construct_graph(fake_graph, do_bipartite)
+  print 'created graph with %s nodes and %s edges' % (graph.num_vertices(), graph.num_edges())
+  save_graph(graph, input_file, do_bipartite)
+
+
+# loads the fake graph and returns it as dict:
+def load_data(input_file):
+  print 'read input data at %s...' % (input_file)
+  with open(input_file) as f:    
+    return json.load(f)
+
+
+def save_graph(graph, input_file, do_bipartite):
+  # save the graph:
+  output_file = '../../data/gt-graphs/' + os.path.splitext(input_file)[0].split('/')[-1] + '.gt'
+  if do_bipartite:
+    output_file = '../../data/gt-graphs/' + os.path.splitext(input_file)[0].split('/')[-1] + '_bipartite.gt'
+  graph.save(output_file, fmt='gt')
+  print 'done. graph saved to "%s"' % (output_file)
+
+
+def construct_graph(fake_graph, do_bipartite):
+  print 'start creating graph...'
+  # graph variables:
+  g = Graph()
+  vprop_name = g.new_vertex_property('string')
+  vprop_created = g.new_vertex_property('string')
+  eprop_from = g.new_edge_property('long')
+  eprop_to = g.new_edge_property('long')
+
+  # store properties to graph:
+  g.vertex_properties["name"] = vprop_name
+  g.vertex_properties["created"] = vprop_created
+  g.edge_properties["fromdate"] = eprop_from
+  g.edge_properties["todate"] = eprop_to
+
[…]

### 2019-04-12 resources/original_scripts/src/graph/create-json-graph.js

@@ -1,0 +1,325 @@
+
+/**
+ * Creates a JSON graph from input data, in which every line
+ * is a stringified JSON object describing an npm package,
+ * as available at http://registry.npmjs.org/<name>
+ */
+
+var fs = require('fs')
+var byline = require('byline')
+var moment = require('moment')
+var semver = require('semver')
+
+;(function () {
+  function createSnapshotFromSingleFile (inputPath, outputPath, callback) {
+    console.log('create FULL snapshot from file %s.', inputPath)
+
+    var graph = {}
+
+    var lineCount = 0
+    var numNodes = 0
+    var numDeps = 0
+    var numLostDeps = 0
+    var numReDeps = 0
+    var start = new Date().getTime()
+
+    console.log('read input data from file...')
+    var stream = fs.createReadStream(inputPath)
+    stream = byline.createStream(stream)
+
+    stream.on('data', function (line) {
+      lineCount++
+      if (lineCount % 10000 === 0) console.log('%s lines...', lineCount)
+      var repo = JSON.parse(line)
+      var formattedVersions = getFormattedVersions(repo, 15000000000000, true)
+      if (formattedVersions) {
+        numNodes++
+        graph[repo.name] = formattedVersions.deps
+        numDeps += formattedVersions.numDeps
+        numLostDeps += formattedVersions.numLostDeps
+        numReDeps += formattedVersions.numReDeps
+      }
+    })
+
+    stream.on('finish', function () {
+      var end = new Date().getTime()
+      var time = (end - start) / 1000
+      console.log('Created graph from %s lines', lineCount)
+      console.log(' - %s nodes', numNodes)
+      console.log(' - %s edges (%s lost deps, %s recreated deps)', numDeps, numLostDeps, numReDeps)
+      console.log(' - %s seconds to create nodes', time)
+      var results = {
+        numNodes: numNodes,
+        numDeps: numDeps,
+        numLostDeps: numLostDeps,
+        numReDeps: numReDeps
+      }
+      storeGraph(graph, outputPath, results, callback)
+    })
+  }
+
+  function createSnapshotFromMultipleFiles (inputPath, outputPath, callback) {
+    console.log('create FULL snapshot from folder %s.', inputPath)
+
+    // remove possibly existing file:
+    try {
+      if (fs.existsSync(outputPath)) {
+        fs.unlinkSync(outputPath)
+        console.log('removed file %s', outputPath)
+      } else {
[…]

### 2019-04-12 resources/original_scripts/src/graph/new_calc_growth_regression.py

@@ -1,0 +1,61 @@
+import sys
+import math
+import pandas as pd
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+
+def linear_regression(x, y):
+    A = np.vstack([ x, np.ones(len(x)) ]).T
+    m,c = np.linalg.lstsq(A, y)[0]
+    return m,c
+
+def scale_data(x):
+    """Returns (xs, a, b) such that x = a + xs*b."""
+    m = np.min(x)
+    x0 = x - m
+    M = np.max(x0)
+    x1 = x0 / M
+    return (x1, m, M)
+
+def f(x0, a, b, c):
+    return a * np.exp(b * x0) + c
+
+def fit_exp(x, y):
+    popt, pcov = curve_fit(f, x, y, maxfev=100000000)
+    print popt
+    print pcov
+    return (popt[0], popt[1], popt[2])
+
+def work(input_file):
+    df = pd.read_csv(input_file).T
+
+    df = df.ix[1:]
+
+    df.index = pd.to_datetime(df.index)
+
+    x = df.index.astype(np.int64).astype(np.float64) / 10000000000000.0
+    y = df[4].astype(np.float64).as_matrix()
+
+    (xs, xa, xb) = scale_data(x)
+    (ys, ya, yb) = scale_data(y)
+
+    (a,b,c) = fit_exp(xs, ys)
+
+    ys_approx = f(xs, a, b, c)
+    y_approx  = ya + yb * ys_approx
+
+    plt.plot(x, y, label="Number of packages")
+
+    plt.plot(x, y_approx, label="Approximation")
+
+    plt.show()
+
+if __name__ == "__main__":
+  if len(sys.argv) < 2:
+      sys.stderr.write("Usage: %s <input-data>\n" % sys.argv[0])
+      sys.exit(1)
+
+  input_file = sys.argv[1]
+  work(input_file)

### 2019-04-12 resources/original_scripts/src/graph/visualize_correlation_table.py

@@ -1,0 +1,77 @@
+#!/usr/bin/env python
+
+#
+# Visualizes a table including all Spearman rank correlation coefficients
+# between the popularity measures provided in the files list.
+# 
+
+import visualize_correlation
+
+top = 1000
+
+# pageranks:
+files = [
+  {
+    'name': 'npm downloads 1 month',
+    'path': '../../data/downloads/npm_graph_downloads_2015-08-01_2015-09-01.csv'
+  }
+  ,
+  {
+    'name': 'Bipartite pagerank values',
+    'path': '../../data/pageranks/apps_graph_bipartite_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
+  }
+  ,
+  # {
+  #   'name': 'Bipartite pagerank values DEPS only',
+  #   'path': '../../data/pageranks/apps_graph_deps_bipartite_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
+  # }
+  # ,
+  # {
+  #   'name': 'Bipartite pagerank values DEV only',
+  #   'path': '../../data/pageranks/apps_graph_dev_bipartite_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
+  # }
+  # ,
+  {
+    'name': 'npm pagerank values',
+    'path': '../../data/pageranks/npm_graph_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
+  }
+  ,
+  # {
+  #   'name': 'npm pagerank values DEPS only',
+  #   'path': '../../data/pageranks/npm_graph_deps_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
+  # }
+  # ,
+  # {
+  #   'name': 'npm pagerank values DEV only',
+  #   'path': '../../data/pageranks/npm_graph_dev_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
+  # }
+  # ,
+  # {
+  #   'name': 'npm downloads overall',
+  #   'path': '../../data/downloads/npm_graph_downloads_2010-01-01_2015-09-01.csv'
+  # }
+  # ,
+  # ,
+  # {
+  #   'name': 'npm downloads 1 week',
+  #   'path': '../../data/downloads/npm_graph_downloads_2015-08-26_2015-09-01.csv'
+  # }
+]
+
+results = []
+for idx in range(0, len(files)):
+  if idx < len(files):
+    for idx2 in range(idx+1, len(files)):
+      f1 = files[idx]['path']
[…]

### 2019-04-12 resources/original_scripts/src/graph/visualize_dependency_dist_evolution.py

@@ -1,0 +1,66 @@
+#!/usr/bin/env python
+
+#
+# Visualize the distribution of dependencies over time.
+# Input: a _hist_ csv, e.g., "npm_graph_hist_in_weekly_10-01-2010_09-01-2015.csv"
+# Outputfile: npm_deps_in_degree.pdf
+
+import sys
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+
+def visualize_deps_dist(input_file, pp):
+  
+  agg_min = 9
+
+  df = pd.read_csv(input_file, index_col=0, parse_dates=[0])
+  # df.columns = df.columns.to_datetime()
+  df.columns = pd.to_datetime(df.columns)
+
+  # replace entries with percent:
+  for colKey in df:
+    df[colKey] = 100 * df[colKey] / df[colKey].sum()
+
+  # merge columns:
+  num_rows = len(df)
+  print num_rows
+  # label = '> %d' % (agg_min - 1)
+  label = '%d or more' % agg_min
+  df.loc[label] = df.ix[agg_min:num_rows,:].sum(axis=0)
+  ##df.drop(df.iloc[[0:num_rows-2],:])
+
+  df = df.ix[:agg_min].append(df.loc[label])
+#  df = df.loc[:,['2015-08-28']]
+  plt.figure()
+  plt.clf()
+  width = 7.0
+  plt.rc("figure", figsize=(width, 3.0*width/4.0))
+
+  # plot as area:
+  axes = df.T.plot(kind='area')
+  axes.set_ylim(0,100)
+  axes.set_ylabel("Percentage of Packages in npm")
+  axes.set_yticks(range(0, 110, 10))
+  
+  # plt.gcf().autofmt_xdate()
+#  plt.show()
+  plt.tight_layout()
+  pp.savefig(plt.gcf())
+
+
+if __name__=='__main__':
+  if len(sys.argv) < 3:
+      print 'usage: %s <input-data> <output-file>' % (sys.argv[0])
+      exit(-1)
+  input_file = sys.argv[1]
+  output_file = sys.argv[2]
+
+  #npm_deps_out_degree.pdf
+  with PdfPages(output_file) as pp:
+    visualize_deps_dist(input_file, pp)

### 2019-04-12 resources/original_scripts/src/graph/visualize_devs_per_repo.py

@@ -1,0 +1,75 @@
+#!/usr/bin/env python
+
+#
+# Script to visualize growth of packages vs number of contributors on a
+# month by month basis
+# 
+# Input: 
+# - devs_and_versions_per_repo.csv
+
+#
+import sys
+import math
+import pandas as pd
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib.ticker import FuncFormatter
+
+
+def to_percent(y, position):
+  # Ignore the passed in position. This has the effect of scaling the default
+  # tick locations.
+  s = str(math.floor(100 * y))
+
+  # The percent symbol needs escaping in latex
+  if matplotlib.rcParams['text.usetex'] is True:
+    return s + r'$\%$'
+  else:
+    return s + '%'
+
+def last_x(x, position):
+  # Ignore the passed in position. This has the effect of scaling the default
+  # tick locations.
+  if (x < 10):
+    s = str(x)
+  else:
+    s = ">=10"
+  return s
+
+def visualize_growth(input_file, pp):
+  df = pd.read_csv(input_file, index_col=0).T
+  
+  plt.figure()
+  plt.clf()
+
+#  axes=df['Developers'].hist(bins=50,normed=1,alpha=0.5,cumulative=True,lw=1.5,histtype='step')
+  axes=df['Developers'].hist(bins=10,range=(1,10), density=1,cumulative=True,lw=1.75,histtype='step')
+  axes.set_ylabel("Percentage of Packages")
+  axes.set_xlabel("Number of Developers")
+  # axes.set_ylim(0,1.05)
+  # axes.set_xlim(0,11)
+  axes.set_xticks(range(0,11,1))
+  plt.gcf().subplots_adjust(left=0.15)
+
+  # Create the formatter using the function to_percent. This multiplies all the
+  # default labels by 100, making them all percentages
+  yformatter = FuncFormatter(to_percent)
+  ##trimming the bins to that it doesn't obscure patterns in the lower ends of X range
+  xformatter = FuncFormatter(last_x)
+  
+  # Set the formatter
+  plt.gca().yaxis.set_major_formatter(yformatter)
+  plt.gca().xaxis.set_major_formatter(xformatter)
+#  plt.show()
+
+  pp.savefig(plt.gcf())
+
+if __name__=='__main__':
+  if len(sys.argv) < 2:
[…]

### 2019-04-12 resources/original_scripts/src/graph/visualize_highest_ranked.py

@@ -1,0 +1,197 @@
+#!/usr/bin/env python
+
+#
+# Script to identify and visualize packages whose pagerank 
+# has been the highest over time.
+# 
+# Input: "npm_graph_pr_top_180000_weekly_10-01-2010_09-01-2015.csv"
+#
+import sys
+import math
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.dates as dates
+from matplotlib.backends.backend_pdf import PdfPages
+from scipy.stats import gmean
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+
+def visualize_highest_ranked(input_file):
+  
+  num_packages = 5
+
+  df = pd.read_csv(input_file, index_col=0, parse_dates=[0])
+  # df.columns = df.columns.to_datetime()
+  # df.columns = pd.to_datetime(df.columns)
+
+  # Reverse rank sum:
+  # visualize_reverse_rank(df, num_packages)
+
+  # Average rank:
+  # visualzie_avg_rank(df, num_packages)
+
+  # Geometric mean rank:
+  # visualize_geo_rank(df, num_packages)
+
+  # Relative rank (from 0 - 1):
+  # visualize_relative_rank(df, num_packages)
+
+  # Select packages:
+  # packages = ['underscore', 'lodash', 'lazy.js', 'sugar', 'valentine', 'babel', 'typescript']
+  # visualize_select_packages(df, packages)
+
+  # Average rank per year:
+  visualize_avg_rank_per_year(df, num_packages)
+
+
+def visualize_reverse_rank(df, num_packages):
+  df['overall_score'] = df.T.apply(lambda x: 300000 - x).sum()
+  df.sort_values('overall_score', ascending=True, inplace=True)
+  df.drop('overall_score', axis=1, inplace=True)
+  ax = df[:num_packages].plot()
+  plt.tight_layout()
+  plt.gca().invert_yaxis()
+  plt.savefig('reverse_rank.png')
+  #plt.show()
+
+
+def visualize_select_packages(df, packages):
+  df_select = df.ix[packages]
+  print(type(df_select.columns))
[…]

### 2019-04-12 resources/original_scripts/src/graph/visualize_popularity_relations.py

@@ -1,0 +1,171 @@
+#!/usr/bin/env python
+
+#
+# Visualizes the relationships (differences in ranks) of different popularity measures.
+# Considers only ranks that are NOT random. E.g., filters packages that have all the same
+# minimum pagerank value as they don't have any incoming relations.
+# 
+# It does also re-rank the packages after filtering:
+#   Consider two rankings A and B regarding a set of 150 entries.
+#   A contains 100 valid ranks, 1 - 100.
+#   B contains  50 valid ranks, 1 -  50.
+#   Not having a valid value means that the entry performs indistinguishably BAD.
+#   A comparison of A and B results in 40 comparisons where entries have valid values in A and B.
+#   Theory 1:
+#     Re-rank values regarding A and B from 1 - 40.
+#     This way, one compares the relative rankings between A and B.
+#     Neglects all the packages in either A or B that have no valid value in the other ranking.
+#   Theory 2:
+#     Compare values of A and B without re-ranking, resulting for example in A = 2, B = 125.
+#     This way, one compares the absolute ranks of A and B.
+#     The resulting distribution may be skewed, for example, ranks may be comparatively lower in A.
+#     But doesn't that account for the fact, that there are entries that rank higher in A and comparatively 
+#     low in B (= they don't even have a valid rank)?
+#
+import sys
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+
+files = [
+  {
+    'name': 'GitHub',
+    'path': '../../data/pageranks/apps_graph_bipartite_in-deg_daily_09-01-2015_09-01-2015.csv'
+  }
+  ,
+  {
+    'name': 'npm',
+    'path': '../../data/pageranks/npm_graph_pr-values_top_300000_daily_09-01-2015_09-01-2015.csv'
+  }
+  ,
+  {
+    'name': 'downloads',
[…]

### 2019-04-12 resources/original_scripts/src/graph/visualize_repos_and_devs_by_month.py

@@ -1,0 +1,41 @@
+#!/usr/bin/env python
+
+#
+# Script to visualize growth of packages vs number of contributors on a
+# month by month basis
+# 
+# Input: 
+# - repos_and_devs_by_month.csv
+
+#
+import sys
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+
+
+def visualize_growth(input_file, pp):
+  df = pd.read_csv(input_file, index_col=0, parse_dates = [0]).T
+  
+  plt.figure()
+  plt.clf()
+
+  axes = df.plot(style=['-','--'], lw=2.0)
+  axes.legend(loc='best')
+  
+  #  plt.tight_layout()
+  #  plt.show()
+  plt.gcf().autofmt_xdate()
+  axes.set_ylabel("Count")
+  axes.set_xlabel("Time")
+
+  pp.savefig(plt.gcf())
+
+if __name__=='__main__':
+  if len(sys.argv) < 2:
+      print 'usage: %s repos_and_devs_per_month.csv' % (sys.argv[0])
+      exit(-1)
+  input_file = sys.argv[1]
+  with PdfPages('repos_and_devs_per_month.pdf') as pp:
+    visualize_growth(input_file, pp)

### 2019-04-12 resources/original_scripts/src/graph/visualize_top_keywords.py

@@ -1,0 +1,55 @@
+#!/usr/bin/env python
+
+#
+# Determine and prints keywords of packages that are comparatively the
+# highest ranking in npm as compared to GitHub and vice versa.
+#
+import sys
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.ticker import ScalarFormatter, FormatStrFormatter
+
+
+def get_top_keyword_count_df(df, column_name, top, reverse):
+  df.sort_values(column_name, inplace=True, ascending=(not reverse))
+  keyword_counts = {}
+  for index, row in df[:top].iterrows():
+    keyword_list = str(row['keywords']).split(';')
+    for name in keyword_list:
+      if name not in keyword_counts:
+        keyword_counts[name] = 1
+      else:
+        keyword_counts[name] += 1
+  new_column_name = column_name
+  if reverse:
+    new_column_name = '%s - %s' % (column_name.split(' - ')[1], column_name.split(' - ')[0])
+  new_df = pd.DataFrame(keyword_counts, index=['count_' + new_column_name]).T
+  return new_df.sort_values('count_' + new_column_name, ascending=False)
+
+# read DataFrame with all popularity measures and their rank differences:
+df = pd.read_csv('../../data/popularity_measures.csv', index_col=0)
+
+# count the keywords in the 1000 packages the most better on npm than GitHub:
+print '\n\nKeyword count for packages better on npm than on GitHub:'
+better_npm_df = get_top_keyword_count_df(df, 'npm - GitHub', 1000, False)
+print better_npm_df[:20]
+
+# count the keywords in the 1000 packages the most better on GitHub than npm:
+print '\n\nKeyword count for packages better on GitHub than on npm:'
+better_github_df = get_top_keyword_count_df(df, 'npm - GitHub', 1000, True)
+print better_github_df[:20]
+
+# find keywords with the highest different count between npm- and GitHub-strong packages:
+new_df = pd.concat([better_npm_df, better_github_df], axis=1) 
+new_df['diff'] = new_df['count_npm - GitHub'] - new_df['count_GitHub - npm']
+
+# print keywords that predominantly appear in npm-strong packages:
+print '\n\nKeywords most unilaterally used by npm-strong pacakges:'
+new_df.sort_values('diff', ascending=False, inplace=True)
+print new_df[:15]
+
+# print keywords that predominantly appear in GitHub-strong packages:
[…]

### 2019-04-12 resources/original_scripts/src/graph/visualize_top_losers.py

@@ -1,0 +1,102 @@
+#!/usr/bin/env python
+
+#
+# Visualizes the top losing packages.
+#
+# Input: "npm_graph_pr_top_180000_weekly_10-01-2010_09-01-2015.csv"
+#
+import sys
+import math
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.stats import gmean
+
+def visualize_highest_lossers(input_file):
+  
+  num_packages = 5
+
+  df = pd.read_csv(input_file, index_col=0, parse_dates=0)
+  df.columns = df.columns.to_datetime()
+
+  visualize_loosers_top_1000(df, num_packages)
+
+def get_max_decline(df):
+  results = {}
+  for index, row in df.iterrows():
+    highest_rank = len(df)
+    lowest_subsequent_rank = 0
+    for rank in row:
+      if math.isnan(rank):
+        continue
+      if rank < highest_rank:
+        highest_rank = rank
+        lowest_subsequent_rank = 0
+      elif rank >= lowest_subsequent_rank and rank < len(df):
+        lowest_subsequent_rank = rank
+      else:
+        continue
+    max_decline = lowest_subsequent_rank - highest_rank
+    # print '%s: highest=%s, lowest=%s, max-decline=%s' % (index, highest_rank, lowest_subsequent_rank, max_decline)
+    results[index] = max_decline
+  return pd.DataFrame(results, index=['num_declines']).T
+
+
+def get_rank_declines(df):
+  results = {}
+  for index, row in df.iterrows():
+    last_rank = 0
+    num_declines = 0
+    for rank in row:
+      if math.isnan(rank):
+        continue
+      if rank < 1000:
+        if last_rank < rank: 
+          num_declines += rank - last_rank
+        last_rank = rank
+    results[index] = num_declines
+  return pd.DataFrame(results, index=['num_declines']).T
+
+
+def visualize_loosers_top_1000(df, num_packages):
+  # sort by geometric mean:
+  def geo_mean(x):
+    return gmean(list(x.dropna()))
+  df['overall_score'] = df.T.apply(geo_mean) # df.T.mean()
+  df.sort_values('overall_score', ascending=True, inplace=True)
+  df.drop('overall_score', axis=1, inplace=True)
+
+  # Consider top 1000 from hereon:
+  df = df[:1000]
+
[…]

### 2019-04-12 resources/original_scripts/src/graph/visualize_top_newcomers.py

@@ -1,0 +1,70 @@
+#!/usr/bin/env python
+
+#
+# Visualizes the number of packages entering the top N pageranks for the first time
+# over time.
+# 
+# Input: "npm_graph_pr_top_180000_weekly_10-01-2010_09-01-2015.csv"
+#
+import sys
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import rc
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+
+
+def visualize_top_newcomers(input_file):
+  # list of top values to consider:
+  top_list = [10, 100, 250]
+
+  # read CSV:
+  df = pd.read_csv(input_file, index_col=0, parse_dates=False)
+  df.columns = pd.to_datetime(df.columns)
+
+  # start at 2011-06-01:
+  # df = df.ix[:,35:]
+
+  frames = []
+  for top in top_list:
+    frame = get_newcomers(df, top)
+    frames.append(frame)
+
+  df_results = pd.concat(frames, axis=1)
+
+  # print absolute numbers of packages entering per year:
+  df_results.resample('A', how='sum').to_csv("top_newcomers_data.csv")
+  print "printed stuff"
+
+  width = 6.0
+  plt.rc("figure", figsize=(width, 3.0*width/4.0))
+
+  ax = df_results.resample('1M', how='mean').plot(style=['-', '-', '-'], lw=1.5) # resample('4M', how='mean')
+  ax.set_ylim(0, 10)
+  ax.set_ylabel('No. of Packages')
+  plt.tight_layout()
+  plt.grid()
+  plt.show()
+
+
+def get_newcomers(df, top):
+  seen = []
+  results = {}
+  for column in df:
+    ranks = df[column].sort_values()
+    new_packages = 0
+    for package_name, value in ranks[:top].iteritems():
+      if package_name not in seen:
+        new_packages += 1
+        seen.append(package_name)
+    results[column] = new_packages
+  return pd.DataFrame(results, index=['Entering top %s for the first time' % str(top)]).T
+
+
+if __name__=='__main__':
+  if len(sys.argv) < 1:
+      print 'usage: %s <input-data>' % (sys.argv[0])
+      exit(-1)
+  input_file = sys.argv[1]
+  visualize_top_newcomers(input_file)

### 2019-04-12 resources/original_scripts/src/graph/visualize_versions_per_repo.py

@@ -1,0 +1,74 @@
+#!/usr/bin/env python
+
+#
+# Script to visualize growth of packages vs number of contributors on a
+# month by month basis
+# 
+# Input: 
+# - devs_and_versions_per_repo.csv
+
+#
+import sys
+import math
+import pandas as pd
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.backends.backend_pdf import PdfPages
+from matplotlib.ticker import FuncFormatter
+
+
+def to_percent(y, position):
+  # Ignore the passed in position. This has the effect of scaling the default
+  # tick locations.
+  s = str(math.floor(100 * y))
+
+  # The percent symbol needs escaping in latex
+  if matplotlib.rcParams['text.usetex'] is True:
+    return s + r'$\%$'
+  else:
+    return s + '%'
+
+def last_x(x, position):
+  # Ignore the passed in position. This has the effect of scaling the default
+  # tick locations.
+  if (x < 100):
+    s = str(x)
+  else:
+    s = ">=100"
+  return s
+
+def visualize_growth(input_file, pp):
+  df = pd.read_csv(input_file, index_col=0).T
+  
+  plt.figure()
+  plt.clf()
+
+  axes=df['Versions'].hist(bins=100,range=(1,100), density=1,cumulative=True,lw=1.75,histtype='step')
+  axes.set_ylabel("Percentage of Packages")
+  axes.set_xlabel("Number of Versions")
+  # axes.set_ylim(0,1.05)
+  # axes.set_xlim(0,110)
+  axes.set_xticks(range(0,110,10))
+  plt.gcf().subplots_adjust(left=0.15)
+
+  # Create the formatter using the function to_percent. This multiplies all the
+  # default labels by 100, making them all percentages
+  yformatter = FuncFormatter(to_percent)
+  ##trimming the bins to that it doesn't obscure patterns in the lower ends of X range
+  xformatter = FuncFormatter(last_x)
+  
+  # Set the formatter
+  plt.gca().yaxis.set_major_formatter(yformatter)
+  plt.gca().xaxis.set_major_formatter(xformatter)
+#  plt.show()
+
+  pp.savefig(plt.gcf())
+
+if __name__=='__main__':
+  if len(sys.argv) < 2:
+      print 'usage: %s devs_versions_per_repo_hist.csv' % (sys.argv[0])
+      exit(-1)
+  input_file = sys.argv[1]
[…]

### 2019-04-12 resources/original_scripts/version-histories/data-express-adoption.py

@@ -1,0 +1,75 @@
+import re
+import sys
+import numpy
+
+from db import DB
+
+if __name__ == "__main__":
+    output_file = sys.argv[0].replace(".py", ".dat")
+
+    def semver(v):
+        m = re.match("""([0-9]*)\.([0-9]*)\.([0-9]*)""", v)
+        major = int(m.group(1))
+        minor = int(m.group(2))
+        patch = int(m.group(3))
+        return (major, minor, patch)
+
+    def triple_to_float(major, minor, patch):
+        K = 0.5
+        m = float(major)
+        M = float(minor)
+        p = float(patch)
+
+        M_p = M + 1.0 - (1.0 / (K*p + 1.0))
+        m_M_p = m + 1.0 - (1.0 / (K*M_p + 1.0))
+        
+        # THIS IS SPECIFIC TO EXPRESS
+        return m + M / 22.0 + p / (13.0 * 22.0)
+
+        return m_M_p
+
+    db = DB()
+
+    db.cursor.execute("""
+SELECT
+    `rd`.`version`,
+    `rd`.`released` AS `released`,
+    UNIX_TIMESTAMP(`rd`.`released`) AS `ts`,
+    `rd`.`resolvable_dependents` AS `resolvable`,
+    `ad`.`resolved_dependents` AS `resolved`,
+    `ad`.`resolved_dependents` / `rd`.`resolvable_dependents` AS `fraction`
+FROM
+    `resolvable_dependents` `rd`
+        LEFT OUTER JOIN 
+    `resolved_dependents` `ad`
+        ON
+    `rd`.`version` = `ad`.`version`
+WHERE
+    `rd`.`package_id` = `ad`.`package_id` AND
+    `rd`.`version` = `ad`.`version` AND
+    `rd`.`released` > "2012-10-15"
+ORDER BY
+    `released`
+;
+    """)
+
+    all_triples = []
+    all_major   = []
+    all_minor   = []
+    all_patch   = []
+
+    triple_counts = {}
+
+    print "Writing to %s..." % (output_file)
+    with open(output_file, "w") as fp:
+        fp.write("major,minor,patch,linearized,ts,frac\n")
+
+        for row in db.cursor.fetchall():
+            version = row[0]
+            ts      = row[2]
+            frac    = row[5]
+            triple  = semver(version)
+            (major,minor,patch) = triple
+            linearized = triple_to_float(major, minor, patch)
+
[…]

### 2019-04-12 resources/original_scripts/version-histories/data-time-to-version.py

@@ -1,0 +1,75 @@
+import re
+import sys
+
+from db import DB
+
+if __name__ == "__main__":
+    output_file = sys.argv[0].replace(".py", ".dat")
+
+    def semver(v):
+        m = re.match("""([0-9]*)\.([0-9]*)\.([0-9]*)""", v)
+        major = int(m.group(1))
+        minor = int(m.group(2))
+        patch = int(m.group(3))
+        return (major, minor, patch)
+
+    def triple_to_float(major, minor, patch):
+        K = 0.5
+        m = float(major)
+        M = float(minor)
+        p = float(patch)
+
+        M_p = M + 1.0 - (1.0 / (K*p + 1.0))
+        m_M_p = m + 1.0 - (1.0 / (K*M_p + 1.0))
+
+        return m_M_p
+
+    db = DB()
+
+    print "Running query..."
+    db.cursor.execute("""
+        SELECT
+            `version`,
+            COUNT(*) AS `count`,
+            AVG(`time_diff`) AS `avg_time_to_version`,
+            MIN(`time_diff`) AS `min_time_to_version`,
+            MAX(`time_diff`) AS `max_time_to_version`
+        FROM (
+            SELECT
+                `pv`.`package_id`,
+                `pv`.`version`,
+                `pv`.`released`,
+                `sub`.`first_released`,
+                TIMESTAMPDIFF(SECOND, `sub`.`first_released`, `pv`.`released`) AS `time_diff`
+            FROM
+                `package_versions` `pv`
+                INNER JOIN
+                (
+                    SELECT
+                        `package_id`,
+                        MIN(`released`) AS `first_released`
+                    FROM
+                        `package_versions`
+                    GROUP BY
+                        `package_id`
+                ) `sub`
+                ON `pv`.`package_id` = `sub`.`package_id`
+        ) `xxx`
+        WHERE
+            `version` REGEXP "^[0-9]+\\.[0-9]+\\.[0-9]+$"
+        GROUP BY
+            `version`;
+    """)
+
+    print "Writing to %s..." % (output_file)
+    with open(output_file, "w") as fp:
+        fp.write("major,minor,patch,linearized,count,avg_time,min_time,max_time\n")
+
+        for row in db.cursor.fetchall():
+            (version, count, avg_time, min_time, max_time) = row
+            (major,minor,patch) = semver(version)
+            linearized = triple_to_float(major,minor,patch)
+
[…]

### 2019-04-12 resources/original_scripts/version-histories/dbstats.py

@@ -1,0 +1,24 @@
+#!/usr/bin/env python
+from db import DB
+
+if __name__ == "__main__":
+    db = DB()
+
+    query = """
+        SELECT 
+            `table_name`,
+            ROUND(((data_length + index_length) / 1024 / 1024), 2)
+            FROM information_schema.TABLES where `table_schema`="npmversions"
+            ORDER BY (data_length + index_length) DESC;
+     """
+
+    db.cursor.execute(query)
+    print "%-40s %10s" % ("Table name", "Size")
+    print "%-40s-%10s" % ("-" * 40, "-" * 10)
+    for row in db.cursor.fetchall():
+        if row[1] is None:
+            size = "%10s" % "----"
+        else:
+            size = "%7.2f MB" % row[1]
+
+        print "%-40s %10s" % (row[0], size)

### 2019-04-12 resources/original_scripts/version-histories/multiresolver-pre.py

@@ -1,0 +1,141 @@
+import json
+import subprocess
+
+from loader import Loader
+
+# This script is designed to feed into version-resolver.js, then into *-post.py.
+class MultiResolverPre:
+    @classmethod
+    def resolve_all_queries(cls, db, package_name):
+        (intervals, latest_ts) = cls.query_intervals(db, package_name)
+
+        if latest_ts is None:
+            return
+
+        releases = cls.versions_earlier_than(db, package_name, latest_ts)
+
+        if releases:
+            (versions, release_dates) = zip(*releases)
+
+            for (qs, start_ts, end_ts) in intervals:
+                cls.resolve(package_name, qs, start_ts, end_ts, versions, release_dates)
+
+    @classmethod
+    def versions_earlier_than(cls, db, package_name, ts):
+        versions = []
+
+        db.cursor.execute("""
+            SELECT
+                `version`, `released`
+            FROM
+                `packages`,
+                `package_versions`
+            WHERE
+                `packages`.`id`=`package_versions`.`package_id` AND
+                `packages`.`name`=%s
+            ORDER BY
+                `released` ASC;""", package_name)
+
+        for (version, released) in db.cursor.fetchall():
+            versions.append((version, Loader.dt2ts(released)))
+
+        return versions
+
+    @classmethod
+    def query_intervals(cls, db, package_name):
+        
+        # This will get you all the query strings ever used for that package,
+        # together with first-seen and last-seen dates.
+        db.cursor.execute("""
+            SELECT
+                `packages`.`id` AS `package_id`,
+                `packages`.`name` AS `package_name`,
+                `deps`.`version_query`,
+                MIN(`deps`.`started`) AS `first_started`,
+                MAX(`deps`.`ended`) AS `last_ended`
+            FROM
+                `packages`,
+                `project_explicit_dependencies` AS `deps`
+            WHERE
+                `packages`.`id`=`deps`.`package_id` AND
+                `packages`.`name`=%s
+            GROUP BY
+                `packages`.`id`,
+                `deps`.`version_query`;""", package_name)
+
+        stored_rows = []
+        latest_ts = -1
+
+        # Each row is a specific query string
+        for row in db.cursor.fetchall():
+            (pkg_id, pkg_name, qs, first_started, last_ended) = row
+            first_ts = Loader.dt2ts(first_started)
+            last_ts  = Loader.dt2ts(last_ended)
[…]

### 2019-04-12 resources/original_scripts/version-histories/schema.py

@@ -1,0 +1,28 @@
+#!/usr/bin/env python
+import sys
+
+from db import DB
+
+if __name__ == "__main__":
+    if len(sys.argv) < 3 or (sys.argv[2] != "up" and sys.argv[2] != "down"):
+        print("Usage: %s id {up,down}" % sys.argv[0])
+        sys.exit(1)
+
+    which = sys.argv[1]
+
+    if sys.argv[2] == "down":
+        src = "./sql/%s-down.sql" % which
+    else:
+        src = "./sql/%s-up.sql" % which
+
+    print "Executing script: %s" % src
+
+    with open(src) as fp:
+        contents = fp.read()
+
+    print ""
+    print contents
+
+    db = DB()
+    db.cursor.execute(contents)
+

### 2019-04-13 paper/paper.tex
small typo fixes

@@
 We obtained the list of all \code{npm} package names from the \code{npm} registry skimdb\footnote{https://skimdb.npmjs.com/registry/\_all\_docs}, and then %TODO fix this footnote, underscores are cursed
-downloaded this metadata for all 797,940 packages on the \code{npm} registry, having found the names of all packages using the npm registry skimdb
+downloaded this metadata for all 797,940 packages on the \code{npm} registry, having found the names of all packages using the \code{npm} registry skimdb
 , which we then converted to a somewhat simplified form as in Listing \ref{sampleSimpleMetadata} with just version and dependency information as this is all
-we care about for this study. There are two kinds of dependencies in the metadata files, a list of runtime dependencies and $devDependencies$ used in testing and development.\\
+we care about for this study. There are two kinds of dependencies in the metadata files, a list of runtime dependencies and \code{devDependencies} used in testing and development.\\
 
-We gathered some information on download counts for \code{npm} packages from the npmjs API\footnote{https://api.npmjs.org/downloads/range/2010-01-01:2019-04-01/packageName} 
+We gathered some information on download counts for \code{npm} packages from the \code{npm} API\footnote{https://api.npmjs.org/downloads/range/2010-01-01:2019-04-01/packageName} 
 however we found that the npmjs API seems to no longer have any data on download counts before October 1 2017, and so were unable to collect
@@
     and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
-    \code{npm} rank, an relative ranking of packge popularity with 1 being the most popular.
+    \code{npm} rank, an relative ranking of package popularity with 1 being the most popular.
   \item \textbf{download rank}

### 2019-04-13 paper/paper.tex
edited and reformatted the npm metadata section

@@
 \begin{lstlisting}[caption={A mock simplified \code{npm} metadata file.},captionpos=b,
-  label=sampleSimpleMetadata, frame=single, firstline=1][t]
+  label=sampleSimpleMetadata, frame=single, firstline=1]
 {
@@
 
-Metadata for every package is available on the \code{npm} registry\footnote{https://registry.npmjs.org/packageName}. 
-This metadata is a JSON file containing some info on licensing, documentation links, maintainers, and crucially for 
-our purposes a log of each version of the package since it's creation, labelled using semantic versioning \cite{preston-werner},
-and a time field containing the timestamp for each version. Each version in the version field contains various bits of 
-version specific information such as authors, maintainers, license used, bugs, and a list of dependencies for that specific
-version.\\
+Metadata for every package is available on the \code{npm}
+registry\footnote{https://registry.npmjs.org/packageName}. 
+This metadata is a \code{JSON} file containing info 
+on licensing, documentation links, and maintainers, as well as
+a log of each version of the package since its creation, which 
+for our purposes is the most crucial element.
+The version data is labelled using semantic 
+versioning \cite{preston-werner} and includes a time field containing 
+the timestamp of creation for each version. Each version in the version 
+field contains various version specific information such as authors, 
+maintainers, the license used, bugs, and a list of dependencies for that specific
+version.
 
-We obtained the list of all \code{npm} package names from the \code{npm} registry skimdb\footnote{https://skimdb.npmjs.com/registry/\_all\_docs}, and then %TODO fix this footnote, underscores are cursed
-downloaded this metadata for all 797,940 packages on the \code{npm} registry, having found the names of all packages using the \code{npm} registry skimdb
-, which we then converted to a somewhat simplified form as in Listing \ref{sampleSimpleMetadata} with just version and dependency information as this is all
-we care about for this study. There are two kinds of dependencies in the metadata files, a list of runtime dependencies and \code{devDependencies} used in testing and development.\\
+We obtained the list of all \code{npm} package names from 
+the \code{npm} registry \code{skimdb}\footnote{https://skimdb.npmjs.com/registry/\_all\_docs}. Using these names,
+we then downloaded the metadata for each of the 797,940 packages hosted by the
+\code{npm} registry and then converted this metadata into a somewhat simplified form 
+with just version and dependency information, as seen
+in Listing \ref{sampleSimpleMetadata}. There are two kinds of dependencies in the metadata
+files: runtime dependencies and \code{devDependencies} used in testing and development.
 
-We gathered some information on download counts for \code{npm} packages from the \code{npm} API\footnote{https://api.npmjs.org/downloads/range/2010-01-01:2019-04-01/packageName} 
-however we found that the npmjs API seems to no longer have any data on download counts before October 1 2017, and so were unable to collect
-historic download counts for \code{npm} as a whole or any specific packages.\\
+% We gathered information on download counts for \code{npm} packages from the
+% \code{npm} API\footnote{https://api.npmjs.org/downloads/range/2010-01-01:2019-04-01/packageName} 
+% however we found that the npm.js API seems to no longer have any data on download counts before October 1 2017, and so were unable to collect
+% historic download counts for \code{npm} as a whole or any specific packages.\\
 

### 2019-04-15 resources/original_scripts/src/graph/visualize_package_growth.py
added packages vs dependencies figure

@@ -14,21 +14,24 @@ import sys
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
+import matplotlib.dates as mdates
 from matplotlib import rc
 rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
 rc('text', usetex=True)
 
 def visualize_growth(input_file, input_clean):
-  df = pd.read_csv(input_file, index_col=0, parse_dates=0).T
+  df = pd.read_csv(input_file, index_col=0, parse_dates=False).T
 
   df.rename(columns={'num_vertices': 'Packages', 'num_edges': 'Dependencies'}, inplace=True)
 
-  df_clean = pd.read_csv(input_clean, index_col=0, parse_dates=0)
+  df_clean = pd.read_csv(input_clean, index_col=0, parse_dates=False)
   df_clean.columns = ['Packages newer than 180 days']
 
   df = df[['Packages', 'Dependencies']].join(df_clean)
 
   df['Dependencies per Package'] = pd.DataFrame(df['Dependencies'] / df['Packages'])
+
+  # print(df['Dependencies per Package'])
 
   width = 5.0
   plt.rc("figure", figsize=(width, 3.0*width/4.0))
@@ -36,15 +39,20 @@ def visualize_growth(input_file, input_clean):
   # plot left:
   ax = df[['Packages', 'Dependencies']].plot(lw=2.0, legend=False)
   ax.set_ylabel('No. of Packages / Dependencies')
+  ax.set_ylim(0, 7500000)
+  # ax.xaxis.set_major_locator(mdates.MonthLocator())
+  # ax.xaxis.set_major_formatter(mdates.DateFormatter('%Y'))
   ax.xaxis.grid(True)
-
 
   # plot rights:
   ax2 = df['Dependencies per Package'].plot(secondary_y=True, lw=2.0, legend=False)
   ax2.set_ylim(0,10)
   ax2.set_ylabel('Dependencies per Package')
+  # ax2.xaxis.set_major_locator(mdates.MonthLocator(interval=1))
+  # ax2.xaxis.set_major_formatter(mdates.DateFormatter('%Y'))
 
   plt.tight_layout()
+  plt.gcf().autofmt_xdate()
   plt.grid()
   plt.show()
 

### 2019-04-15 paper/paper.tex
added description for package vs dependency graph

--- 2019-04-11 paper/paper.tex
@@
 Additionally, the major frameworks used in JavaScript development have undergone a 
-rapid transformation as packages such as Angular and React are adopted\footnotemark[\ref{adoption}].
+rapid transformation as packages such as Angular and React are adopted\footnotemark{\ref{adoption}}.
 The core contributions we make are as follows:
@@
 \begin{figure}
+  \includegraphics[width=1\linewidth]{figures/packages_vs_dependencies.png}
+  \caption{axis \textbf{y1} shows growth in number of packages in npm (blue line), and the number of dependencies (orange line), 
+  with axis \textbf{y2} showing average number of dependencies per package (green line)}
+  \label{packVSDependencies}
+\end{figure}
+
+\begin{figure}
   % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS

### 2019-04-15 resources/original_scripts/src/graph/visualize_package_growth.py

@@ -54,7 +54,8 @@ def visualize_growth(input_file, input_clean):
   plt.tight_layout()
   plt.gcf().autofmt_xdate()
   plt.grid()
-  plt.show()
+  plt.savefig("packages_vs_dependencies.png", dpi=300)
+  # plt.show(
 
 
 if __name__=='__main__':

### 2019-04-15 paper/paper.tex
some formatting

@@
 we investigate the number of packages created and updated over time, as well
-as system-wide trends of dependencies within packages. In Figure \ref{npmGrowth},
+as system-wide trends of dependencies within packages. 
+In Figure \ref{npmGrowth},
 we can observe that while \code{npm} is still growing, the speed at which new packages
@@
 by some source currently unknown to the authors [TRY TO FIGURE THIS ONE OUT].
-[ADD CONCAVITY DATA]. Figure 2 [CURRENTLY MISSING][MORE DATA COMMENTARY].
+[ADD CONCAVITY DATA].
+
+\begin{figure}
+  \includegraphics[width=1\linewidth]{figures/packages_vs_dependencies.png}
+  \caption{Axis \code{y1} shows growth in number of \code{npm} packages (blue line), and the number of package dependencies (orange line) over time. 
+  Axis \code{y2} shows the average number of dependencies per package (green line).}
+  \label{packVSDependencies}
+\end{figure}
+
+Figure 2 [CURRENTLY MISSING][MORE DATA COMMENTARY].
 
@@
   \includegraphics[width=0.5\textwidth]{figures/npm_deps_monthly_out_degree.pdf}
-  \caption{\code{npm} packages by their number of dependencies on other packages}
+  \caption{\code{npm} packages by their number of dependencies on other packages.}
   \label{outDegree}
@@
   \includegraphics[width=0.5\textwidth]{figures/npm_deps_monthly_in_degree.pdf}
-  \caption{\code{npm} packages by the number of other packages depending on them}
+  \caption{\code{npm} packages by the number of other packages depending on them.}
   \label{inDegree}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=1\linewidth]{figures/packages_vs_dependencies.png}
-  \caption{axis \textbf{y1} shows growth in number of packages in npm (blue line), and the number of dependencies (orange line), 
-  with axis \textbf{y2} showing average number of dependencies per package (green line)}
-  \label{packVSDependencies}
 \end{figure}

### 2019-04-15 paper/paper.tex
more content

@@
 
-\subsection{Package Metadata}
+\subsection{Package Metadata} \label{PackageMetadata}
 
@@
 
-Figure 2 [CURRENTLY MISSING][MORE DATA COMMENTARY].
+Figure \ref{packVSDependencies} presents the total number of \code{npm} packages over time, 
+as well as the total number of package dependencies. Additionally, we have plotted
+the average number of dependencies per \code{npm} package. Curiously, though total dependencies
+continues to grow faster than the creation of new packages, the number of dependencies 
+for the average package appears to be plateauing. If this trend continues, it could suggest
+that the \code{npm} ecosystem is reaching some sort of equilibrium with regards to the number
+of package dependencies.
 
@@
 a directed dependency graph using dependants as out-degrees and
-dependencies as in-degrees. Based on this graph, Figure \ref{outDegree}
+dependencies as in-degrees. Based on this data, Figure \ref{outDegree}
 displays the percentage of packages with various amounts of dependencies. 
-[MIGHT NEED TO CHANGE BASED ON DATA: While the average number of dependencies 
+This confirms some of our earlier suspicious: while the average number of dependencies 
 of packages continues to increase, the percentage of packages with zero 
 to three dependencies has actually increased since the end of the original paper's
-reporting period \cite{Wittern:2016}. This suggests some changes to developer 
-behaviour, likely either as a deliberate effort by programmers seeking to avoid the perils of 
+reporting period \cite{Wittern:2016}. This supports the hypothesis that developer 
+behaviour is changing, likely either as a deliberate effort by programmers seeking to avoid the perils of 
 complicated dependency trees \cite{Kikas:2017}, or as a natural result of the ever-changing
@@
   \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within a dependency graph that we built using the
-    package metadata as described in Section \ref{Package Metadata}. PageRank is calculated for every package using a damping factor of 0.85 
+    package metadata as described in Section \ref{PackageMetadata}. PageRank is calculated for every package using a damping factor of 0.85 
     and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
     \code{npm} rank, an relative ranking of package popularity with 1 being the most popular.
-  \item \textbf{download rank}
+  \item The \textbf{download rank} is based on the the gross volume of package downloads from the \code{npm}
+    registry, then ordered relatively with 1 being the most downloaded.
+  \item \textbf{\code{GitHub} rank} is a measure of the popularity of package use in public \code{GitHub} projects.
+    This rank is created from a list of \code{npm} dependency occurrences found in \code{package.json} files, with rank 1
+    meaning that the package was the most common dependency among analyzed \code{GitHub} repositories.  
 \end{enumerate}

### 2019-04-15 paper/paper.tex
updated bibs, more ecosystem content

@@
 
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{figures/npm_deps_monthly_out_degree.pdf}
+  \caption{\code{npm} packages by their number of dependencies on other packages.}
+  \label{outDegree}
+\end{figure}
+
 To better visualize the status of inter-package dependencies, we constructed
@@
 
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{figures/npm_deps_monthly_in_degree.pdf}
+  \caption{\code{npm} packages by the number of other packages depending on them.}
+  \label{inDegree}
+\end{figure}
+
 In addition to the number of external dependencies per package, 
@@
 that the current trend of increasing concentration appears to have begun shortly after the end of window in the original
-paper \cite{Wittern:2016}.
+paper.
 
-\begin{figure}
-  \includegraphics[width=0.5\textwidth]{figures/npm_deps_monthly_out_degree.pdf}
-  \caption{\code{npm} packages by their number of dependencies on other packages.}
-  \label{outDegree}
-\end{figure}
+In section \ref{popularity}, we revisit the popularity measures
+investigated in the original paper \cite{Wittern:2016} to discover
+changes in the relationships between package rankings
+both inside and outside of the \code{npm} ecosystem,
+gaining insight into the dynamics of \code{npm} package popularity.
 
-\begin{figure}
-  \includegraphics[width=0.5\textwidth]{figures/npm_deps_monthly_in_degree.pdf}
-  \caption{\code{npm} packages by the number of other packages depending on them.}
-  \label{inDegree}
-\end{figure}
+\textbf{Takeaways.} We find that while the \code{npm} ecosystem
+continues to grow, the rate of growth is no longer superlinear, 
+a possible sign of the ecosystem beginning to reach some form of maturity.
+In the relationships between packages, we find that though the average number
+of dependencies continues to grow, there has been a recent decline in the
+rate of this growth. Accordingly, we have found that the number of packages with
+zero dependencies has increased from 28.7\% in September 2015 to [DATA REQUIRED]\%
+as of April 2019. The percentage of packages that are depended on has
+also declined, albeit still exhibiting a power law relationship as observed
+in prior software ecosystem research \cite{Wittern:2016, Myers:2003, Louridas:2008}.
 
-\begin{figure}
+\section{Package Popularity}\label{popularity}
+
+As per the original paper we analyzed popularity of \code{npm} packages using three major measures \cite{Wittern:2016}:
+\begin{enumerate}
+  \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within a dependency graph that we built using the
+    package metadata as described in Section \ref{PackageMetadata}. PageRank is calculated for every package using a damping factor of 0.85 
+    and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
+    \code{npm} rank, an relative ranking of package popularity with 1 being the most popular.
+  \item The \textbf{download rank} of a package is based on the the gross volume of package downloads from the \code{npm}
+    registry, then ordered relatively with 1 being the most downloaded.
+  \item \textbf{\code{GitHub} rank} is a measure of the popularity of a package among public \code{GitHub} projects.
+    This rank is created from a list of \code{npm} dependency occurrences found in \code{package.json} files, with rank 1
+    meaning that the package was the most common dependency among analyzed \code{GitHub} repositories.  
+\end{enumerate}
+
+\subsection{Relationships between Measures}
+[NEEDS MORE DATA]
+
+\subsection{Distinct Package Types}
+[NEEDS MORE DATA]
+
+\subsection{Popularity Over Time}
+
+\begin{table}
+  \centering
   % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
@@
   \label{numEnteringTop}
-\end{figure}
+\end{table}
 
-\section{Package Popularity}
-
-As in the original paper we analyzed popularity of \code{npm} packages using three major measures
-\begin{enumerate}
-  \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within a dependency graph that we built using the
-    package metadata as described in Section \ref{PackageMetadata}. PageRank is calculated for every package using a damping factor of 0.85 
-    and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
-    \code{npm} rank, an relative ranking of package popularity with 1 being the most popular.
-  \item The \textbf{download rank} is based on the the gross volume of package downloads from the \code{npm}
-    registry, then ordered relatively with 1 being the most downloaded.
-  \item \textbf{\code{GitHub} rank} is a measure of the popularity of package use in public \code{GitHub} projects.
-    This rank is created from a list of \code{npm} dependency occurrences found in \code{package.json} files, with rank 1
-    meaning that the package was the most common dependency among analyzed \code{GitHub} repositories.  
-\end{enumerate}
-
-\subsection{Relationships between Measures}
-[NEEDS MORE DATA]
-
-\subsection{Distinct Package Types}
-[NEEDS MORE DATA]
-
-\subsection{Popularity Over Time}
 [NEEDS MORE DATA]
@@
 
+  \bibitem{Louridas:2008}
+  Panagiotis Louridas, Diomidis Spinellis, and Vasileios Vlachos.
+  \newblock Power laws in software.
+  \newblock {\em ACM Trans. Softw. Eng. Methodol.}, 18(1):2:1--2:26, October
+    2008.
+
   \bibitem{LUNGU2010264}

### 2019-04-15 paper/paper.tex
added related works section (could be expanded)

@@
 continues to grow, the rate of growth is no longer superlinear, 
-a possible sign of the ecosystem beginning to reach some form of maturity.
+a possible sign of the ecosystem beginning to reach some form of maturity \cite{Alves:2011}.
 In the relationships between packages, we find that though the average number
@@
 \subsection{Attribution of Version Numbers}
-[NEEDS MORE DATA]
+[NEEDS MORE DATA
 
@@
 \section{Related Work}
-[IN PROGRESS]
+
+Related research can be generally described as one of two types
+of work: meta-analyses of the behaviour and importance
+of software ecosystems, and empirical investigations into the
+specifics of a particular ecosystem. Some topics 
+for meta-analyses include ecosystem visualization \cite{LUNGU2010264},
+ecosystem maturity \cite{Alves:2011}, quality metric aggregation \cite{Mordal:2013},
+and literature reviews \cite{Manikas:2013, Manikas:2017}. Specific ecosystem analysis include works such
+paper and the original research by Wittern, Suter and Rajagopalan \cite{Wittern:2016} on \code{npm}.
+Others have performed evaluations of specific ecosystems such as Raemaekers et al. \cite{Raemaekers:2013},
+who present a dataset with basic metrics, dependencies and changes within the popular 
+Java-based Maven ecosystem. Another work investigates the
+result of changing project interdependencies in Apache \cite{Bavota:2013}, 
+and still others evaluate evolution over time in ecosystems such as
+Gentoo \cite{Bloemen:2014}, Ruby, \cite{Kabbedijk:2011}, and R \cite{Plakidas:2017}.
 
@@
 \begin{thebibliography}{10}
+
+  \bibitem{Alves:2011}
+  Salviano~C.F Alves~A.M., Pessoa~M.
+  \newblock {\em Towards a Systemic Maturity Model for Public Software
+    Ecosystems}, volume 155.
+  \newblock Springer, Berlin, Heidelberg, 2011.
+
+  \bibitem{Bavota:2013}
+  Gabriele Bavota, Gerardo Canfora, Massimiliano~Di Penta, Rocco Oliveto, and
+    Sebastiano Panichella.
+  \newblock The evolution of project inter-dependencies in a software ecosystem:
+    The case of apache.
+  \newblock In {\em Proceedings of the 2013 IEEE International Conference on
+    Software Maintenance}, ICSM '13, pages 280--289, Washington, DC, USA, 2013.
+    IEEE Computer Society.
 
@@
     Press.
+
+  \bibitem{Bloemen:2014}
+  Remco Bloemen, Chintan Amrit, Stefan Kuhlmann, and Gonzalo Ordonez-Matamoros.
+  \newblock Gentoo package dependencies over time.
+  \newblock pages 404--407, 05 2014.
 
@@
     Press.
+
+  \bibitem{Kabbedijk:2011}
+  Jaap Kabbedijk and Slinger Jansen.
+  \newblock Steering insight: An exploration of the ruby software ecosystem.
+  \newblock volume~80, pages 44--55, 06 2011.
 
@@
 
+  \bibitem{Mordal:2013}
+  Karine Mordal-Manet, Nicolas Anquetil, Jannik Laval, Alexander Serebrenik,
+    Bogdan Vasilescu, and Stéphane Ducasse.
+  \newblock Software quality metrics aggregation in industry.
+  \newblock {\em Journal of Software: Evolution and Process}, 25:1117--1135, 10
+    2013.
+
   \bibitem{Myers:2003}
@@
 
+  \bibitem{Plakidas:2017}
+  Konstantinos Plakidas, Daniel Schall, and Uwe Zdun.
+  \newblock Evolution of the r software ecosystem.
+  \newblock {\em J. Syst. Softw.}, 132(C):119--146, October 2017.
+
   \bibitem{preston-werner}
@@
   \newblock Semantic versioning 2.0.0.
+
+  \bibitem{Raemaekers:2013}
+  Steven Raemaekers, Arie van Deursen, and Joost Visser.
+  \newblock The maven repository dataset of metrics, changes, and dependencies.
+  \newblock pages 221--224, 05 2013.
 

### 2019-04-15 paper/paper.tex

@@
 
+With the differences and changes in the relationships between
+popularity measures explored, we can now focus on \code{npm}
+rankings in particular, as it is most representative of the 
+importance of a package to the \code{npm} ecosystem as a whole.
+To obtain \code{npm} ranks over time, we first begin with the
+complete dependency graph as of April 2019. We then examine
+the date references on the edges of the graph to produce \code{PageRanks}
+for each and every package on a monthly basis for the period of October 2010
+to April 2019. From the list of \code{PageRanks} in each month, we then
+produce the relative rank for every package present in the \code{npm}
+ecosystem at that time.
+
+\subsubsection{Identifying Top Packages}
+
+\begin{figure}
+  \includegraphics[width=0.5\textwidth]{figures/geo_mean_highest_pagerank.pdf}
+  \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean}
+  \label{topFive}
+\end{figure}
+
+One of the most obvious things to investigate is which packages
+have historically performed best throughout the entirety of 
+\code{npm}'s existence. To determine overall package popularity,
+we use the geometric mean \code{npm} rank of a package over the full 
+window of analysis, and order them from lowest to highest (i.e,
+highly ranked to lowly ranked). Geometric mean is used in this instance
+instead of arithmetic mean in order to limit the effect of outliers \cite{Wittern:2016}.
+With popularity calculated in this manner, Figure \ref{topFive} presents 
+the top five \code{npm} packages of all time.
+
+The first thing to notice about these five packages is that the rankings
+have changed since the time of the original paper. Gone are the packages
+\code{uglify-js} and \code{coffee-script}, and newcomers \code{tape} and \code{mkdirp}
+have appeared. Additionally, though the package \code{should} remains on the list,
+it has fallen from the \#2 to the \#4 position.
+
+Four of the five current champions are testing utilities---\code{mkdirp} is the sole exception, instead providing the ability to dynamically
+create directories from within \code{node.js}. Curiously, the testing packages
+are essentially all direct competitors of one another, providing a powerful 
+demonstration of both the widespread importance of testing utilities as well as
+the ability for the \code{npm} software ecosystem to support multiple core packages with
+similar yet distinct functionality.
+
+\begin{figure*}
+  \includegraphics[width=1\textwidth]{figures/highest_ranked.pdf}
+  \caption{\code{npm} rank (PageRank) of the five packages each year with the lowest geometric}
+  \label{ranksByYear}
+\end{figure*}
+
+While these packages represent the most consistently popular
+members of \code{npm}, we also evaluate the most popular packages
+on a yearly basis. Figure \ref{ranksByYear} presents the top five packages
+for each individual year from 2011 to 2019. As noted in the original paper,
+the top packages per year are relatively stable from 2013 on \cite{Wittern:2016}.
+One notable exception to this rule is the 2016 rise in popularity of \code{eslint},
+a tool for improving the quality of \code{JavaScript} code\footnote{https://www.npmjs.com/package/eslint}.
+
+\subsubsection{Popular Package Dynamics}
+
 \begin{table}
@@
 
-[NEEDS MORE DATA]
-
-\subsubsection{Identifying Top Packages}
-[NEEDS MORE DATA]
-
-\begin{figure}
-  \includegraphics[width=0.5\textwidth]{figures/geo_mean_highest_pagerank.pdf}
-  \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean}
-  \label{topFive}
-\end{figure}
-
-\subsubsection{Popular Package Dynamics}
-[NEEDS MORE DATA]
-
-\begin{figure*}
-  \includegraphics[width=1\textwidth]{figures/highest_ranked.pdf}
-  \caption{\code{npm} rank (PageRank) of the five packages each year with the lowest geometric}
-  \label{ranksByYear}
-\end{figure*}
+To better understand the evolution of package popularity,
+we investigate the dynamics of the top rankings over time.
+While figure \ref{ranksByYear} demonstrate that package popularity
+appears to be relatively stable, we can examine the number of packages
+entering (and therefore exiting) the top \code{n} packages per year in
+order to obtain a better view of the ecosystem as a whole.
+Table \ref{numEnteringTop} depicts amount of newcomers to the top
+\code{npm} ranks each year, further supporting the observation that
+core \code{npm} package popularity is becoming more stable as the 
+ecosystem matures.
 

### 2019-04-15 paper/paper.tex
comparing similar packages

@@
 
+To better understand the evolution of package popularity,
+we investigate the dynamics of the top rankings over time.
+While figure \ref{ranksByYear} demonstrate that package popularity
+appears to be relatively stable, we can examine the number of packages
+entering (and therefore exiting) the top \code{n} packages per year in
+order to obtain a better view of the ecosystem as a whole.
+Table \ref{numEnteringTop} depicts the amount of newcomers to the top
+\code{npm} ranks each year, further supporting the observation that
+core \code{npm} package popularity is becoming more stable as the 
+ecosystem matures.
+
 \begin{table}
@@
 
-To better understand the evolution of package popularity,
-we investigate the dynamics of the top rankings over time.
-While figure \ref{ranksByYear} demonstrate that package popularity
-appears to be relatively stable, we can examine the number of packages
-entering (and therefore exiting) the top \code{n} packages per year in
-order to obtain a better view of the ecosystem as a whole.
-Table \ref{numEnteringTop} depicts amount of newcomers to the top
-\code{npm} ranks each year, further supporting the observation that
-core \code{npm} package popularity is becoming more stable as the 
-ecosystem matures.
-
-\subsubsection{Comparing Popularities}
-[NEEDS MORE DATA]
+\subsubsection{Comparing the Popularity of Similar Packages}
 
@@
 \end{figure}
+
+One of the significant benefits of being able to determine
+\code{npm} ranks over time is that it allows for the comparison
+of similar packages against each other at an objective level.
+Figure \ref{selectPackages} shows the npm ranks of selected 
+utility packages, as chosen in the original paper \cite{Wittern:2016}.
+One of these packages, \code{underscore}, is among the oldest \code{npm} 
+utility packages, and the rest have been selected for being
+typical alternatives to the \code{underscore} package. Some of these packages,
+such as \code{lodash}, are directly or indirectly results of forks from the
+\code{underscore} repository. While \code{lodash} has kept up and even surpassed
+\code{underscore} in popularity, the majority of newer alternatives are unable
+to consistently compete. Calculating ranks for similar groups of packages such as
+this allow us to isolate notable, successful packages across the entire span of
+the ecosystem's history, as well as evaluate the persistence of the most popular
+core packages over time. In the example group of packages presented in Figure \ref{selectPackages},
+we can observe that the package established early in the ecosystem's life-cycle
+is well-positioned to maintain a significant level of popularity, while the majority of
+other packages tend to eventually decline unless they provide something exceptional,
+such as \code{lodash} providing API compatibility with \code{underscore}\footnote{https://lodash.com/}.
 

### 2019-04-15 paper/paper.tex
added conclusion

@@
     ecosystem has affected the relationships between various measures of package popularity.
-  \item We determine if the ongoing maturation of the \code{npm} ecosystem has 
-    resulted in tangible changes to version numbering or adoption practices.
+  % \item We determine if the ongoing maturation of the \code{npm} ecosystem has 
+  %   resulted in tangible changes to version numbering or adoption practices.
 \end{itemize}
@@
 
-\section{Version Numbering and Package Adoption}
-[NEEDS MORE DATA]
+% \section{Version Numbering and Package Adoption}
+% [NEEDS MORE DATA]
 
-\subsection{Attribution of Version Numbers}
-[NEEDS MORE DATA
+% \subsection{Attribution of Version Numbers}
+% [NEEDS MORE DATA
 
-\subsection{Adoption by Version Number}
-[NEEDS MORE DATA]
+% \subsection{Adoption by Version Number}
+% [NEEDS MORE DATA]
 
@@
 ecosystem maturity \cite{Alves:2011}, quality metric aggregation \cite{Mordal:2013},
-and literature reviews \cite{Manikas:2013, Manikas:2017}. Specific ecosystem analysis include works such
-paper and the original research by Wittern, Suter and Rajagopalan \cite{Wittern:2016} on \code{npm}.
+and literature reviews \cite{Manikas:2013, Manikas:2017}. Specific ecosystem analysis include works such as this
+paper as well as the original research by Wittern, Suter and Rajagopalan \cite{Wittern:2016} on \code{npm}.
 Others have performed evaluations of specific ecosystems such as Raemaekers et al. \cite{Raemaekers:2013},
@@
 result of changing project interdependencies in Apache \cite{Bavota:2013}, 
-and still others evaluate evolution over time in ecosystems such as
+and still others evaluate evolution over time in ecosystems like
 Gentoo \cite{Bloemen:2014}, Ruby, \cite{Kabbedijk:2011}, and R \cite{Plakidas:2017}.
@@
 \section{Conclusion}
-[NEEDS MORE DATA]
+
+In this paper, we take a second look at the \code{npm} ecosystem,
+replicating and extending the results of previous research by 
+Wittern, Suter and Rajagopalan \cite{Wittern:2016}. Though
+we observe that the growth of \code{npm} has slowed down, the ecosystem
+continues to thrive, demonstrating signs of maturity rather than decline.
+
+Contrary to the trend observed in the original paper, there appears to be
+some effort to reduce the number of inter-package dependencies, and therefore the risks
+associated with complex dependency trees. The core set of packages upon which
+multiple other projects rely on has remained relatively constant in size, and
+demonstrates a trend towards even further concentration. Accordingly, the set of packages
+most depended on in the \code{npm} ecosystem is also trending towards stability, with
+fewer and fewer packages entering the top ranks each year.
+
+Our results regarding relationships between popularity metrics support the discoveries of the
+original paper, further reinforcing the theory that packages can be generally divided into the categories
+of end user and core utility packages, and improving our understanding of how package popularity evolves.
+Ultimately, our second evaluation of the \code{JavaScript} package environment can help developers evaluate
+the state of the \code{npm} ecosystem, and continue to make informed decisions when selecting frameworks
+to use in their applications.
 

### 2019-04-15 paper/paper.tex
expanded related works

@@
 Gentoo \cite{Bloemen:2014}, Ruby, \cite{Kabbedijk:2011}, and R \cite{Plakidas:2017}.
+Some works have looked empirically at the results of changing versions
+within software ecosystems (including \code{npm}), finding that
+developers often encounter difficulties when attempting to avoid
+breaking dependencies \cite{Bogart:2015}.
+
+Finally, \code{npm} has been investigated informally. In
+the \code{pagerank} package, web-based \code{PageRanks} are used to evaluate
+package popularity\footnote{https://www.npmjs.com/package/pagerank}.
+The project code{npm-by-the-numbers} also provides various statistics
+about the state of \code{npm}, but is significantly out of date and 
+in contrast to this work does not provide an evaluation of the ecosystem over time
+or give any insight into application usage\footnote{https://github.com/ashleygwilliams/npm-by-the-numbers}.
 
@@
   \newblock pages 404--407, 05 2014.
+
+  \bibitem{Bogart:2015}
+  Christopher Bogart, Christian K{\"a}stner, and James Herbsleb.
+  \newblock When it breaks, it breaks: How ecosystem developers reason about the
+    stability of dependencies.
+  \newblock In {\em Proceedings of the ASE Workshop on Software Support for
+    Collaborative and Global Software Engineering (SCGSE)}, pages 86--89, 11
+    2015.
 

### 2019-04-15 paper/paper.tex
added values

@@
 we can observe that while \code{npm} is still growing, the speed at which new packages
-are created has slowed from an exponential to a linear rate. Some other things of note 
-include an observable spike in package creation and updates around March 2016, the month 
+are created has slowed from an exponential to a linear rate. Packages added and updated 
+per month have gone from 10087 and 23100 respectively in September 2015 to 17354 and 48140 respectively in April 2019.
+Some other things of note include an observable spike in package creation and updates around March 2016, the month 
 when developer Azer Ko\c{c}ulu removed his 273 packages (including the popular package 
@@
 complicated dependency trees \cite{Kikas:2017}, or as a natural result of the ever-changing
-ways in which JavaScript is used for project development. [ADD EXACT VALUES]
+ways in which JavaScript is used for project development. In particular, the number of packages with zero dependencies
+has increased from 19.5\% in September 2015 to 23.8\% as of April 2019.
 
@@
 that not only have these aspects held true, but the concentration of 
-dependencies has actually increased. As of April 1\textsuperscript{st} 2019, [NUMBER]\% of packages
-had zero dependants, up from [NUMBER]\% in 2015. Meanwhile, only \%[NUMBER] of packages
+dependencies has actually increased. As of April 1\textsuperscript{st} 2019, 79.2\% of packages
+had zero dependants, up from 72.8\% in September 2015. Meanwhile, only \%[NUMBER] of packages
 had 6 or more dependants, down from \%[NUMBER] in September 2015. It is again interesting to note

### 2019-04-15 paper/paper.tex
more data and formatting

@@
 Additionally, the major frameworks used in JavaScript development have undergone a 
-rapid transformation as packages such as Angular and React are adopted\footnotemark{\ref{adoption}}.
+rapid transformation as packages such as Angular and React are adopted\footnotemark[\ref{adoption}].
 The core contributions we make are as follows:
@@
 By using this set we are able to analyze \code{GitHub} data without being constrained to the currently available window provided by the GHTorrent project\cite{Gousi13}.
-The final data set encompasses 797,940 packages and \textbf{\#VALUE} applications.
+The final data set encompasses 797,940 packages and 40,000 applications.
 
@@
 at any given time in the project's history. The results showed that on average a repository 
-had 37.9 commits as well as [STATS HERE]. Ultimately, of the 9,017,221 
-public \code{GitHub} projects written in JavaScript and the [NUMBER] of repositories
-using \code{npm} packages, we randomly selected [NUMBER] repositories as
+had 37.9 commits. Ultimately, of the 9,017,221 
+public \code{GitHub} projects written in JavaScript and out of all of the repositories
+using \code{npm} packages, we randomly selected 40,000 repositories as
 a representative data set for the analysis.
@@
 are created has slowed from an exponential to a linear rate. Packages added and updated 
-per month have gone from 10087 and 23100 respectively in September 2015 to 17354 and 48140 respectively in April 2019.
+per month have gone from 10,087 and 23,100 respectively in September 2015 to 17,354 and 48,140 respectively as of April 2019.
 Some other things of note include an observable spike in package creation and updates around March 2016, the month 
@@
 There is also a significant spike in package updates observed in the month of January 2019, caused 
-by some source currently unknown to the authors [TRY TO FIGURE THIS ONE OUT].
+by some source currently unknown to the authors.
 [ADD CONCAVITY DATA].

### 2019-04-15 paper/paper.tex
added number for out degrees
added takeaway blurb for popularity

@@
 dependencies has actually increased. As of April 1\textsuperscript{st} 2019, 79.2\% of packages
-had zero dependants, up from 72.8\% in September 2015. Meanwhile, only \%[NUMBER] of packages
-had 6 or more dependants, down from \%[NUMBER] in September 2015. It is again interesting to note
+had zero dependants, up from 72.8\% in September 2015. Meanwhile, only 3.2\% of packages
+had 6 or more dependants, down from 3.8\% in September 2015. It is again interesting to note
 that the current trend of increasing concentration appears to have begun shortly after the end of window in the original
@@
 
+\textbf{Takeaways.} Using \code{npm} ranks, we are able to identify successful packages 
+at any point in the life-cycle of the ecosystem. We can also use these
+ranks to obtain a measure of package popularity stability over time. In 
+the \code{npm} ecosystem, the amount of change in the highest ranked packages
+has decreased significantly since the inception of the service, with many
+more recent utilities falling out of favour relative to the oldest and most
+historically successful equivalents. However, there are still some relatively newer 
+packages such as \code{lodash} that have managed to compete with the oldest core packages
+such as \code{underscore}.
 % \section{Version Numbering and Package Adoption}

### 2019-04-15 paper/paper.tex
various edits

@@
 standard, we are able to confidently say that any remaining packages are 
-using \code{npm} packages. With this criteria, we then compiled a list 
-of [100,000 for now] project 
-repositories from GitHub, a volume that we felt is likely to be an 
-appropriate representation of all such public projects.
+using \code{npm} packages. From this criteria, we compiled a list 
+of applicable project 
+repositories from GitHub.
 Using the \code{GitHub} platform API and the list of valid repository names 
-from before, we cloned the GitHub repository for each project. With
+from before, we cloned the GitHub repository for a random subset of all projects. With
 this, we were then able to determine the date and time of every 
-commit of the project, as well as the list of included \code{npm} packages
-at the time of commit, as listed in every historic version of 
+commit of these projects, as well as the list of included \code{npm} packages
+at the time of every commit, as listed in every historic version of 
 \code{package.json}, providing us with the \code{npm} packages used by that repository
 at any given time in the project's history. The results showed that on average a repository 
-had 37.9 commits. Ultimately, of the 9,017,221 
+had 37.9 commits to its \code{package.json}. Ultimately, of the 9,017,221 
 public \code{GitHub} projects written in JavaScript and out of all of the repositories
-using \code{npm} packages, we randomly selected 40,000 repositories as
+using \code{npm} packages, we selected 40,000 repositories as
 a representative data set for the analysis.
@@
 by some source currently unknown to the authors.
-[ADD CONCAVITY DATA].
+% [ADD CONCAVITY DATA].
 
@@
 of dependencies continues to grow, there has been a recent decline in the
-rate of this growth. Accordingly, we have found that the number of packages with
-zero dependencies has increased from 28.7\% in September 2015 to [DATA REQUIRED]\%
-as of April 2019. The percentage of packages that are depended on has
-also declined, albeit still exhibiting a power law relationship as observed
+rate of this growth. Accordingly, we have found that the the percentage of packages with zero dependencies has 
+increased from 19.5\% in September 2015 to 23.8\% as of April 2019. The ratio of packages that are depended on has
+also declined, with the percentage of packages with
+one or more dependants decreasing from 27.2\% in September 2015 to 20.8\%
+as of April 2019. However, this still exhibits a power law relationship as observed
 in prior software ecosystem research \cite{Wittern:2016, Myers:2003, Louridas:2008}.
@@
 for each individual year from 2011 to 2019. As noted in the original paper,
-the top packages per year are relatively stable from 2013 on \cite{Wittern:2016}.
+the top packages per year are relatively stable from 2013 onwards \cite{Wittern:2016}.
 One notable exception to this rule is the 2016 rise in popularity of \code{eslint},
@@
 we investigate the dynamics of the top rankings over time.
-While figure \ref{ranksByYear} demonstrate that package popularity
+While Figure \ref{ranksByYear} demonstrates that package popularity
 appears to be relatively stable, we can examine the number of packages
@@
 Finally, \code{npm} has been investigated informally. In
-the \code{pagerank} package, web-based \code{PageRanks} are used to evaluate
+the \code{pagerank} package, web-based PageRanks are used to evaluate
 package popularity\footnote{https://www.npmjs.com/package/pagerank}.
-The project code{npm-by-the-numbers} also provides various statistics
+The project \code{npm-by-the-numbers} also provides various statistics
 about the state of \code{npm}, but is significantly out of date and 
@@
 we observe that the growth of \code{npm} has slowed down, the ecosystem
-continues to thrive, demonstrating signs of maturity rather than decline.
+continues to thrive, demonstrating signs of maturity rather than stagnation.
 
-Contrary to the trend observed in the original paper, there appears to be
+Contrary to the trend observed in the original paper, there now appears to be
 some effort to reduce the number of inter-package dependencies, and therefore the risks
@@
 demonstrates a trend towards even further concentration. Accordingly, the set of packages
-most depended on in the \code{npm} ecosystem is also trending towards stability, with
+most depended on in the \code{npm} ecosystem is also trending towards increasing stability, with
 fewer and fewer packages entering the top ranks each year.

### 2019-04-15 paper/paper.tex
literally only need one graph and three tables

@@
 
-\subsection{Relationships between Measures}
-[NEEDS MORE DATA]
+\subsection{Relationships between Measures}\label{metricDiff}
+
+In order to evaluate how different popularity metrics
+relate to each other and for what purposes they can be used,
+we investigate the relationships between our three chosen metrics.
+By calculating the Spearman rank correlation coefficients between
+the metrics, we are able to support the findings of the original 
+paper for the subset of packages for which this correlation is applicable,
+i.e., only those packages which have assigned ranks for each measure used
+in calculating the correlation coefficient. The coefficients presented 
+in Table \ref{corr} are similar to those found in the original paper, 
+supporting the idea that each measure of popularity does not always
+represent the same kind of intrinsic properties of a package, and
+thus cannot necessarily be used interchangeably.
+
+To inspect these relationships in greater detail, Figure \ref{corrGraph}
+plots the differences between ranks of each metric. It may be observed
+that our data presents a relatively normal distribution of differences
+between popularity ranks, again matching the findings of the original paper \cite{Wittern:2016}.
+From these results, we can conclude that our three metrics of popularity
+are measures of different package attributes, and that packages
+with a high rank in one metric can be ranked much lower by another metric.
 
 \subsection{Distinct Package Types}
-[NEEDS MORE DATA]
+
+As we demonstrated in section \ref{metricDiff}, packages that perform well
+by one measure of popularity often perform poorly by others. The original paper
+proposes that one major source of this differential is in the way that packages
+are used \cite{Wittern:2016}. It is surmised that packages ranked highly by the
+\code{npm} PageRank system are primarily packages that are used often within the
+\code{npm} ecosystem, and tend to be \textbf{core utility} packages that are used
+as dependencies for other \code{npm} packages, and rarely used outside of the
+\code{npm} package environment. Conversely, packages that exhibit
+significant popularity by the \code{GitHub} rank tend to be \textbf{end user} packages more
+commonly used in application development as opposed to package construction. 
+In order to confirm this hypothesis, we examine keywords associated with each
+ranking system, as is done in the original paper.
+Tables \ref{npmStrong} and \ref{githubStrong} display keywords most associated with
+each popularity ranking. As the keywords in Table \ref{npmStrong} are closely linked to 
+low level utilities, and the keywords of Table \ref{githubStrong} are strongly related to
+application frameworks, we feel confident confirming the hypothesis of the original authors.
 

### 2019-04-15 paper/paper.tex
small typo fixes

@@
     Edmonton, Canada\\
-  Email: \{kdehaan,neagu,rsauveho,abram.hindle\}@ualberta.ca}
+  Email: \{kdehaan,rsauveho,neagu,abram.hindle\}@ualberta.ca}
 }
@@
 \begin{enumerate}
-  \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within a dependency graph that we built using the
-    package metadata as described in Section \ref{PackageMetadata}. PageRank is calculated for every package using a damping factor of 0.85 
-    and stopping iterations once the cumulative change in values of vertices went below $10^{-6}$. We then order all packages by their PageRank to determine the
+  \item The \textbf{\code{npm} rank} is calculated using the PageRank\cite{brin1998anatomy} of an \code{npm} package within the dependency graph that we built using
+    package metadata as described in Section \ref{PackageMetadata}. PageRank is calculated for every package using a damping factor of 0.85,
+    and stopping iterations once the cumulative change in values of vertices fell below $10^{-6}$. We then order all packages by their PageRank to determine the
     \code{npm} rank, an relative ranking of package popularity with 1 being the most popular.
@@
 other packages tend to eventually decline unless they provide something exceptional,
-such as \code{lodash} providing API compatibility with \code{underscore}\footnote{https://lodash.com/}.
+such as \code{lodash}\footnote{https://lodash.com/} providing API compatibility with \code{underscore}\footnote{https://underscorejs.org/}.
 

### 2019-04-15 paper/paper.tex
added correlation table

@@
 
+\begin{table}
+  \centering
+  % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
+  \begin{tabular}{c|c c c}
+     & \code{npm} PageRank & Downloads & \code{GitHub} \\
+    \hline
+    \code{npm} PageRank & - & 0.389 & 0.405\\
+    Downloads & 0.389 & - & 0.576\\
+    \code{GitHub} & 0.405 & 0.576 & -\\
+
+  \end{tabular}
+  \caption{Spearman rank correlation coefficients between selected measures of popularity.}
+  \label{corr}
+\end{table}
+
 In order to evaluate how different popularity metrics
@@
   \includegraphics[width=0.5\textwidth]{figures/geo_mean_highest_pagerank.pdf}
-  \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean}
+  \caption{\code{npm} rank (PageRank) of the five packages with the lowest overall geometric mean.}
   \label{topFive}
@@
   \includegraphics[width=1\textwidth]{figures/highest_ranked.pdf}
-  \caption{\code{npm} rank (PageRank) of the five packages each year with the lowest geometric}
+  \caption{\code{npm} rank (PageRank) of the five packages each year with the lowest geometric mean.}
   \label{ranksByYear}
@@
 for each individual year from 2011 to 2019. As noted in the original paper,
-the top packages per year are relatively stable from 2013 onwards \cite{Wittern:2016}.
+the top packages per year are relatively stable from 2013 onward \cite{Wittern:2016}.
 One notable exception to this rule is the 2016 rise in popularity of \code{eslint},
@@
   \end{tabular}
-  \caption{Number of packages entering top \code{npm} ranks for the first time}
+  \caption{Number of packages entering top \code{npm} ranks for the first time.}
   \label{numEnteringTop}

### 2019-04-15 paper/paper.tex
updated spearman table
removed reference to the graph

@@
 at any given time in the project's history. The results showed that on average a repository 
-had 37.9 commits to its \code{package.json}. Ultimately, of the 9,017,221 
+had 37.9 commits to its \code{package.json}, and had 8.85 \code{npm} dependencies as well as 
+13.6 \code{devDependencies}. Ultimately, of the 9,017,221 
 public \code{GitHub} projects written in JavaScript and out of all of the repositories
@@
     \hline
-    \code{npm} PageRank & - & 0.389 & 0.405\\
-    Downloads & 0.389 & - & 0.576\\
-    \code{GitHub} & 0.405 & 0.576 & -\\
+    \code{npm} PageRank & - & 0.550 & 0.345\\
+    Downloads & 0.550 & - & 0.444\\
+    \code{GitHub} & 0.345 & 0.444 & -\\
 
@@
 
-To inspect these relationships in greater detail, Figure \ref{corrGraph}
-plots the differences between ranks of each metric. It may be observed
-that our data presents a relatively normal distribution of differences
-between popularity ranks, again matching the findings of the original paper \cite{Wittern:2016}.
-From these results, we can conclude that our three metrics of popularity
-are measures of different package attributes, and that packages
+% To inspect these relationships in greater detail, Figure \ref{corrGraph}
+% plots the differences between ranks of each metric. It may be observed
+% that our data presents a relatively normal distribution of differences
+% between popularity ranks, again matching the findings of the original paper \cite{Wittern:2016}.
+
+From these results, we can say that our data supports the findings of the original paper, and
+that our three metrics of popularity
+are measures of different package attributes. Functionally, this means that packages
 with a high rank in one metric can be ranked much lower by another metric.
@@
 As we demonstrated in section \ref{metricDiff}, packages that perform well
-by one measure of popularity often perform poorly by others. The original paper
+by one measure of popularity can perform poorly by others. The original paper
 proposes that one major source of this differential is in the way that packages

### 2019-04-15 paper/paper.tex
prepping keyword tables

@@
 ranking system, as is done in the original paper.
+
+\begin{table}
+  \centering
+  % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
+  \begin{tabular}{c|c|c|c}
+    Keyword & "\code{npm} strong" & "\code{GitHub} strong" & Diff. \\
+    \hline
+     & - & 0.550 & 0.345\\
+     & 0.550 & - & 0.444\\
+     & 0.345 & 0.444 & -\\
+
+  \end{tabular}
+  \caption{"\code{npm} strong" keywords ordered by difference in occurrence between correlated measures.}
+  \label{npmStrong}
+\end{table}
+
+\begin{table}
+  \centering
+  % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
+  \begin{tabular}{c|c|c|c}
+    Keyword  & "\code{GitHub} strong" & "\code{npm} strong" & Diff. \\
+    \hline
+     & - & 0.550 & 0.345\\
+     & 0.550 & - & 0.444\\
+     & 0.345 & 0.444 & -\\
+
+  \end{tabular}
+  \caption{"\code{GitHub} strong" keywords ordered by difference in occurrence between correlated measures.}
+  \label{githubStrong}
+\end{table}
+
 Tables \ref{npmStrong} and \ref{githubStrong} display keywords most associated with

### 2019-04-15 paper/paper.tex
phrasing
pandas sux

--- 2019-04-15 paper/paper.tex
@@
 commonly used in application development as opposed to package construction. 
-In order to confirm this hypothesis, we examine keywords associated with each
-ranking system, as is done in the original paper.
-Tables \ref{npmStrong} and \ref{githubStrong} display keywords most associated with
-each popularity ranking. As the keywords in Table \ref{npmStrong} are closely linked to 
-low level utilities, and the keywords of Table \ref{githubStrong} are strongly related to
-application frameworks, we feel confident confirming the hypothesis of the original authors.
+% In order to confirm this hypothesis, we examine keywords associated with each
+% ranking system, as is done in the original paper.
+
+% \begin{table}
+%   \centering
+%   % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
+%   \begin{tabular}{c|c}
+%     Keyword & "\code{npm} strong" \\
+%     \hline
+%     \code{test} & 32 \\
+%     \code & 0.550\\
+%      & 0.345\\
+
+%   \end{tabular}
+%   \caption{Sample "\code{npm} strong" keywords accociated most significantly with high \code{npm} rankings.}
+%   \label{npmStrong}
+% \end{table}
+
+% \begin{table}
+%   \centering
+%   % TODO NOTE THAT THIS HAS LOWER NUMBERS THAN THE ORIGINAL PAPER DUE TO MONTHLY PAGERANKS
+%   \begin{tabular}{c|c|c|c}
+%     Keyword & "\code{GitHub} strong" \\
+%     \hline
+%     \code{ember-addon} & 31 \\
+%     \code{css} & 27\\
+%     \code{react} & 26\\
+%     \code{json} & 20\\
+%     \code{http} & 20\\
+%   \end{tabular}
+%   \caption{"\code{GitHub} strong" keywords ordered by difference in occurrence between correlated measures.}
+%   \label{githubStrong}
+% \end{table}
+
+% Tables \ref{npmStrong} and \ref{githubStrong} display keywords most strongly associated with
+% a single popularity ranking. As the keywords in Table \ref{npmStrong} are closely linked to 
+% low level utilities, and the keywords of Table \ref{githubStrong} are strongly related to
+% application frameworks, we feel confident confirming the hypothesis of the original authors.
 
